### 2024-05-31 docs/paper/paper.tex
submission to JuliaCon2023 proceedings

% JuliaCon proceedings template
\documentclass{juliacon}[12pt]
\setcounter{page}{1}

%\newcommand{\pkg}[1]{{\it #1}}
\newcommand{\pkg}[1]{{\small \textsc{#1}}}
\newcommand{\struct}[1]{{\it {#1}}}
\newcommand{\tbd}{}

\begin{document}

\title{Digital Twins for Ocean Robots}

\author[1]{Gaël.Forget}
\affil[1]{Earth, Atmospheric and Planetary Sciences, Massachusetts Institute of Technology, \newline
77 Massachusetts Avenue, Cambridge, 02139, MA, USA}

\keywords{Julia, Ocean, Climate, Robot, Observation, Platform, Sensor, Drifter, Buoy, Profiler, Satellite, Modeling, Artificial Intelligence, Data Assimilation, Parameter Inference, Climatology, Geospatial, Statistics}

\hypersetup{
pdftitle = {Digital Twins for Ocean Robot},
pdfsubject = {JuliaCon 2023 Proceedings},
pdfauthor = {Gaël.Forget},
pdfkeywords = {Julia, Ocean, Robots, Observation, In Situ, Model},
}

\maketitle

\begin{abstract}

DTOR is a framework to access and simulate the global fleet of ocean observing devices (or {\it ocean robots}) that monitor climate change. It brings these observations to Julia and let's us pair ocean robots with virtual counterparts (or {\it twins}). Digital twins provide a bridge to predictive models that enables machine learning. In turn, simulating observations in a virtual environment can help evaluate observational strategies a priori, during deployment, or afterwards. In this paper we present the framework, review simulated ocean robots, and discuss envisioned applications.

%A fleet of ocean robots is collecting data that are crucial to monitor, understand, and predict climate change. Our {\it digital twins for ocean robots} framework brings these data to Julia and provides the ability to pair them with a virtual counterpart. The simulated ocean robots provide a bridge to numerical models and enable machine learning. In turn, the simulated observation of a virtual Earth can be used to evaluate observing system strategies ahead a priori, and once they are in operation. Our frameworks can readily simulates complex data sets being collected at sea. It leverages multiple Julia packages developed by the author and the community. The 2023 JuliaCon talk focused on the global observing system being simulated, as well as the expected scientific, societal, and commercial applications.

\end{abstract}

\section{Introduction}

The DTOR framework was introduced at the Symposium on Advances in Ocean Observation in 2022, and later presented to US-CLIVAR and JuliaCon in 2023. The primary goal of DTOR is to associate ocean observing systems (or {\it ocean robots}) with virtual counterparts (or {\it twins}), and do it for the whole fleet of ocean robots that are currently at sea or have observed the Ocean in the past (Fig.~\ref{fig:ocean-ops}). The virtual twins are to be created through numerical model simulations, which can come in different flavors and languages. The simulation of observing systems in the future, as climate change progresses, is also part of the scope of the DTOR project. At JuliaCon 2023, we presented a solution to (1) access and manipulate the data collected by ocean robots (inc. \pkg{OceanRobots.jl} and \pkg{ArgoData.jl}), and (2) simulate such observations in a virtual environment using a hierarchy of models (incl. \pkg{ClimateModels.jl} and \pkg{MITgcm.jl}).

The model hierarchy includes fast climate model emulators, global model output, ocean reanalyses, high-resolution models, and several ways to represent marine ecosystems. Through a streamlined workflow, \pkg{ClimateModels.jl} (JuliaCon 2021, 2023) makes it easy to operate these models that can provide a virtual environment for the virtual ocean robot fleet to observe and navigate. \pkg{IndividualDisplacements.jl} \cite{Forget2021} can be use to predict pathways of ocean robots that tend to follow ocean currents. \pkg{MeshArrays.jl} adds basic geospatial support for global climate model grids, providing capabilities such as interpolation and geolocation on a grid. The framework leverages and links to a variety of highly capable Julia packages from the community. It notably provides extension for visualization with \pkg{Makie.jl}, and tutorial examples in the form of \pkg{Pluto.jl} notebooks.

\begin{figure}[t]
\centerline{\includegraphics[width=\columnwidth]{figs/20240528_OceanOPS.png}}
\caption{Locations of ocean robots collecting data on {\it 2024/05/27}. Data source : https://www.ocean-ops.org}
\label{fig:ocean-ops}
\end{figure}

\section{Robots Observing the Ocean}

Part of the fleet of ocean robots currently at sea is depicted in Fig.~\ref{fig:ocean-ops}, focusing on some of the most common observing platforms. To create this map, \pkg{OceanRobots.jl} queries the meta-data-base from Ocean-OPS.org, which keeps track of the whole ocean fleet of scientific observation platforms in real time, and provides a restful API. \pkg{OceanRobots.jl} provides a simple interface to this API via the `OceanOPS` module. It then provides dedicated data structures to access and utilize data from common ocean robot types such as  `SurfaceDrifter` and `ArgoFloat` (shown in Fig.~\ref{fig:ocean-ops}). A non-exhaustive list of ocean observing platform categories within the scope of \pkg{OceanRobots.jl} is provided in Tab.~\ref{tab:robots}.

\begin{figure}[t]
\centerline{\includegraphics[width=\columnwidth]{figs/20240528_drifters_5percent.png}}
\caption{A few of the ocean drifters (5\% of 19396) that have been deployed to follow near surface ocean currents.}
\label{fig:drifters}
\end{figure}

A small fraction of the geospatial data obtained in the past using surface ocean drifters (green dots in Fig.~\ref{fig:ocean-ops}) is depicted in Fig.~\ref{fig:drifters} (using \pkg{OceanRobots.jl} and \pkg{Makie.jl}). These drifting buoys tend to follow near-surface ocean currents (at approximately 15 depth). They can measure sea surface temperature and sea level pressure along their trajectories. The data archive currently holds 19396 drifter trajectories, collected over the past 50 years, which allow us to create climatologies such as the one shown in Fig.~\ref{fig:drifters_ve}.

\begin{table}
\tbl{Ocean observing platforms targeted by \pkg{OceanRobots.jl}, and associated data structures (or blank if not yet implemented).}{
\begin{tabular}{|l||r|}\hline
Platform Type & Data Structure\\\hline\hline
surface drifters & \struct{SurfaceDrifter}, \struct{CloudDrift} \\
drifting profilers & \struct{ArgoFloat} \\
moored buoys & \struct{OceanSite}, \struct{NOAAbuoy} \\
sea gliders & \struct{Gliders} \\
sail drones & \tbd \\
research vessels & \tbd \\
ships of opportunity & \tbd \\
orbiting satellites & \struct{SeaLevelAnomaly} \\
suborbital flights & \tbd \\
marine mammals & \tbd \\\hline
\end{tabular}}
\label{tab:robots}
\end{table}

Argo profiling floats (blue dots in Fig.~\ref{fig:ocean-ops}; Code~\ref{lst:ArgoCode}) are one of our main tools to monitor global warming below the sea surface. These devices provide a less detailed view of oceanic pathways (Fig.~\ref{fig:Argo_Float}, top panels) than surface drifters do (e.g., Fig.~\ref{fig:drifters}) with just one location being recorded every ten days. However, Argo floats have a crucial diving capability that surface drifters don't have -- they go up and down the water column to measure temperature and salinity (T,S; bottom panels of Fig.~\ref{fig:Argo_Float}). As a result, the advent of Argo in the early 2000s \cite{Roemmich2019} opened up a whole new era of geospatial analysis, state estimation, and parameter inference over the global Ocean  \cite{Forget2007,Forget2010,MFF14,Forget2015a,FFL15,FP15,Forget2024a}. There were 3837 Argo floats at sea on `2024/05/27`, and a total of 18730 in the Argo data base. Since the Argo array is such an important and somewhat complex observing system, a dedicated package called \pkg{ArgoData.jl} was created that \pkg{OceanRobots.jl} uses under the hood.

\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:ArgoCode},
    caption={Download and visualize one Argo float data as in Fig.~\ref{fig:Argo_Float}.}
]
using OceanRobots, ArgoData, CairoMakie

files_list=GDAC.files_list(); wmo=6900900
argo=read(ArgoFloat(),wmo=wmo,files_list=lst)

fig=plot(argo,option=:standard,pol=pol)
\end{lstlisting}

\pkg{OceanRobots.jl} brings these key climate data sets to the Julia community. It provides a bridge to climate scientists working on observations and models, who are interested in leveraging the powerful Julia software ecosystem (e.g., for numerical modeling, machine learning, and statistical analysis), and have much expertise to contribute. The development of \pkg{OceanRobots.jl} aims to help advance (1) how we understand and simulate observations of climate change, and (2) climate literacy and education by providing simple apps that anyone should be able to use.

\begin{figure}[t]
\centerline{\includegraphics[width=\columnwidth]{figs/20240528_ve_mean.png}}
\caption{Sample mean eastward velocity estimated from drifter data, with a grid resolution of 1/2 degree.}
\label{fig:drifters_ve}
\end{figure}

\section{Simulating Ocean Robots}

Our ability to simulate the data produced by ocean robots is directly linked to our ability, or lack thereof, to explain observed variations and decipher mechanisms from data. Numerical modeling is thus often motivated and driven by observations. Many research activities involve combining ocean models and observations, with the typical goal of learning model parameters and dynamics from data \cite{Forget2010,Forget2015a,FFL15,FP15,Forget2024a}. Observing system simulations in a virtual environment (using models) enable a wide range of applications -- to test out innovative platform or sensor designs ahead of deployment, to optimize global monitoring strategies, or to guide deployed assets in real time for example.

The two simple examples presented below illustrate the simulation of (1) environmental sensors and (2) observing platforms. First, in Fig.~\ref{fig:Argo_Float_simu} we simulate an Argo data collection for temperature (T) and salinity (S) by sampling an ocean climatology along the track of the Argo float (the one from Fig.~\ref{fig:Argo_Float}). This calculation requires (1) a model prediction of $T,S(x,y,z,t)$, which can be based on statistical or mechanistic models, e.g. on a discrete grid, and (2) tools that deal with the Earth geography, can localize observations on a grid, and perform interpolation tasks.

Here we used the OCCA climatology \cite{Forget2010} to provide $T,S(x,y,z,t)$ and create Fig.~\ref{fig:Argo_Float_simu}, with \pkg{MeshArrays.jl} providing the geospatial tools. OCCA is essentially a previously trained model that consists of 12 monthly three-dimensional fields of $T,S$ (one per calendar month). Let's note that Figs.~\ref{fig:Argo_Float} and~\ref{fig:Argo_Float_simu} show broadly similar patterns -- this reflects that the predictive model for $T,S$ is skillful and that $T,S$ contrasts see in Fig.~\ref{fig:Argo_Float} largely reflect the $T,S$ sensor moving with the Argo float across the Ocean's geography. Differences between Figs.~\ref{fig:Argo_Float} and~\ref{fig:Argo_Float_simu} can in turn provide a basis for improving the predictive model, for example by including time variability beyond the seasonal cycle, or through various methods for data assimilation, artificial intelligence, or parameter inference \cite{Forget2010,Forget2015a,FFL15,FP15,Forget2024b}.

\begin{figure}[t]
\centerline{\includegraphics[width=\columnwidth]{figs/20240528_Argo_6900900.png}}
\caption{Data collected by a profiling float from the Argo array. Temperature and salinity profiles, taken every ten days, extend to 2000m depth.}
\label{fig:Argo_Float}
\end{figure}

\begin{figure}[t]
\centerline{\includegraphics[width=\columnwidth]{figs/20240529_MITprof_OCCA.png}}
\caption{Virtual Argo profiles predicted using the OCCA climatology, interpolated to the positions of the float shown in Fig.~\ref{fig:Argo_Float}.}
\label{fig:Argo_Float_simu}
\end{figure}

Our second example focuses on the simulation of observing platforms moving with ocean currents. This basic simulation of surface drifter pathways uses the geostatistical average of velocities calculated in Fig.~\ref{fig:drifters_ve} as a predictive model for the $U,V(x,y,t)$ velocity fields. This gridded data set is simply provided as input to \pkg{IndividualDisplacements.jl}, which then releases virtual drifters and calculates their trajectories following the flow field (code~\ref{lst:IndDispCode}). The combination of these two model elements represents a previously trained model to predict surface drifter trajectories. While it neglects time-variability and small scales in ocean currents altogether, this model is sufficient to capture the mean pathway of sea water through this region -- the well-known loop current feeding the Gulf Stream via Florida Strait (Fig.~\ref{fig:drifters_speed_simu}).

Much more could be done to improve the details and skill of the simple models used here. Higher-order and higher-resolution model output are available to represent important aspects of what is being observed, but neglected in Figs.~\ref{fig:Argo_Float_simu} and~\ref{fig:drifters_speed_simu}, such as the turbulent dispersion seen in Fig.~\ref{fig:drifters_speed} or the small-scale variations visible in Fig.~\ref{fig:Argo_Float}. Small scale temperature fronts and currents are present everywhere in the ocean, with a lot of heterogeneity across regions, as illustrated in Fig.~\ref{fig:km_scale}. Hence it is important to include global km-scale ocean simulations in our model hierarchy (see section~\ref{sec:DT}).

\begin{figure}[t]
\centerline{\includegraphics[width=\columnwidth]{figs/20240528_speed_subset.png}}
\caption{Drifter trajectories in the Gulf of Mexico region. Large velocities highlight the path of the Gulf Stream, being fed by the loop current.}
\label{fig:drifters_speed}
\end{figure}

\begin{figure}[t]
\centerline{\includegraphics[width=\columnwidth]{figs/20240529_speed_subset_IndDisp.png}}
\caption{Virtual drifter trajectories predicted using (1) just the climatological mean flow field estimated from drifters (Fig.~\ref{fig:drifters_ve}, and the northward component) and (2) \pkg{IndividualDisplacements.jl} to calculate trajectories.}
\label{fig:drifters_speed_simu}
\end{figure}

\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:IndDispCode},
    caption={Simulate surface drifter pathways in the Gulf of Mexico (Fig.~\ref{fig:drifters_speed}) from flow fields $u,v$ and initial positions $x,y$. The repetition of `u` and `v` in `FlowFields` reflects that flow fields are treated as time invariant in this example.}
]
using IndividualDisplacements, DataFrames

dT=6*3600 #6 hours
nt=120*86400/dT #120 days

T=(0.,dT)
F=FlowFields(u,u,v,v,T)
I=Individuals(F,x,y)

[solve(I,T.+dT*(n-1)) for n in 1:nt]
trajectories=groupby(record(I),:ID)
\end{lstlisting}

\section{Digital Twin Framework} \label{sec:DT}

Let's define digital twins as agreed upon by the U.S. Committee on Foundational Research Gaps and Future Directions for Digital Twins \cite{DT2024} :

\begin{defi}
A digital twin is a set of virtual information constructs that mimics the structure, context, and behavior of a natural, engineered, or social system (or system-of-systems), is dynamically updated with data from its physical twin, has a predictive capability, and informs decisions that realize value. The bidirectional interaction between the virtual and the physical is central to the digital twin.
\end{defi}

In the {\it digital twins for ocean robots} framework (DTOR), interactivity is facilitated by Julia and its large ecosystem of software packages. In particular, \pkg{Makie.jl} \cite{Makie} and \pkg{Pluto.jl} \cite{Pluto} let us operate even complex modeling workflows from notebooks and apps. The tutorial examples in \pkg{OceanRobots.jl}, \pkg{ArgoData.jl}, \pkg{ClimateModels.jl}, and \pkg{MITgcm.jl} \cite{Forget2024b} are notably available as Pluto notebooks. Interaction between model and data is further enabled by the rich Julia ecosystem for machine learning, data assimilation, parameter inference, and so on. Fig.~\ref{fig:MLP} provides an example where we used \pkg{Flux.jl} \cite{Innes2018} to train a neural network to predict chlorophyll concentration (linked to marine microbe abundance) from environmental parameters as done in the CANYON model \cite{Sauzède2017,Bittig2018}.

The core of DTOR is formed by \pkg{OceanRobots.jl}, \pkg{ArgoData.jl}, and \pkg{MeshArrays.jl} for the physical twins, along with \pkg{ClimateModels.jl}, \pkg{MITgcm.jl}, and \pkg{IndividualDisplacements.jl} for the virtual twins (i.e., predictive modeling). The \pkg{ClimateModels.jl} interface streamlines the use of models implemented in various languages. Our current model hierarchy supported via \pkg{ClimateModels.jl} includes, but is not limited to, the models used in this paper. DTOR can notably simulate observations in the future based on climate model predictions using \pkg{ClimateModels.jl}, which provides two options for this kind of applications -- either querying the CMIP6 archive of model output \cite{CMIP6} or using a fast emulator such as Hector \cite{Hector2015} (Fig.~\ref{fig:globalwarming}).

Within our model hierarchy, future climate scenarios like Fig.~\ref{fig:globalwarming} can be downscaled using gridded climatologies and reanalyses \cite{Forget2010,Forget2015a,Forget2024a}. The ECCO4 and OCCA2 reanalyses are simple to rerun with perturbed surface forcing fields via \pkg{MITgcm.jl}, which is partiucularly convenient for such applications. Multi-decadal solutions produced in this way can then be further downscaled using km-scale model output (Fig.~\ref{fig:km_scale}). At the end of this modeling workflow, \pkg{OceanRobots.jl}, \pkg{MeshArrays.jl} and \pkg{IndividualDisplacements.jl} enable calculations such as Figs.~\ref{fig:Argo_Float_simu} and \ref{fig:drifters_speed_simu}, for any of our models. DTOR can also take advantage of gridded satellite data, incl. sea surface temperature and sea level anomalies, and it is sometimes possible to use these instead of ocean reanalyses.

\begin{figure}[th]
\centerline{\includegraphics[width=\columnwidth]{figs/Snapshot_grad_theta.png}}
\caption{Temperature fronts in a global km-scale MITgcm simulation. Plotted is the logarithm of the spatial gradient of a temperature snapshot.}
\label{fig:km_scale}
\end{figure}

\begin{figure}[th] 
\includegraphics[width=\columnwidth]{figs/Chl_av_NN3D5.jpg}
\caption{Ensemble of model predictions (black curves) by a simple multi-layer perceptron (from Flux.jl) trained to predict Chlorophyll concentration (present in green algea and marine microbes) from environmental variables (T, S, but also oxygen, optical backscatter, and solar radiation). The blue line is the {\it ground truth} that we seek to estimate, and was obtained through proper spatial averaging of the gridded data set from which the training data itself was generated.}
\label{fig:MLP}
\end{figure}

\begin{figure}[th] 
\includegraphics[width=\columnwidth]{figs/HectorDemo.png}
\caption{Prediction of global warming based on different scenarios, called Shared Socioeconomic Pathways (SSPs), as defined by the Intergovernmental Panel on Climate Change (IPCC). These predictions were generated using the Hector model \cite{Hector2015} via \pkg{ClimateModels.jl}.}
\label{fig:globalwarming}
\end{figure}

\section{Planned Extensions}

Further development of the DTOR framework is expected to proceed in several directions. First, we'd like to integrate additional types of ocean observing platforms, starting with those that do not have a data structure listed yet in Tab.~\ref{tab:robots}. Observational networks that focus on the coastal ocean, a specific region, or local field experiments could be supported in the future. A top level API to interact with DTOR as a whole through cloud services is also envisioned.

A second direction to pursue is that of further integration with the Julia software stack. Ocean modeling capabilities such as \pkg{Oceananigans.jl} \cite{OceananigansJOSS}, \pkg{PlanktonIndividuals.jl} \cite{Wu2022}, \pkg{AIBECS.jl} \cite{Pasquier2022}, \pkg{OceanColorData.jl}, and \pkg{WorldOceanAtlasTools.jl} are of immediate relevance. More broadly, there is a lot of very useful work being done across of number of github organizations that DTOR could further leverage and integrate with. To list a few : \pkg{JuliaClimate}, \pkg{JuliaOcean}, \pkg{CLIMA}, \pkg{JuliaGeo}, \pkg{JuliaEarth}, \pkg{JuliaSpace}, \pkg{JuliaRobotics}, \pkg{juliadynamics}, \pkg{MakieOrg}, \pkg{PlutoOrg}, \pkg{JuliaHub}, \pkg{GenieFramework}, \pkg{JuliaStats}, \pkg{SciML}, \pkg{FluxML}, \pkg{Turing}, and \pkg{JuliaAI}.

%MITgcm : \cite{marshall1997fvi,camp-etal:04,HHG05,Forget2015a,Forget2024b}
%OCCA / ECCO : \cite{Forget2007,Forget2010,Forget2015a,FFL15,FP15,Forget2024b}
%More : \cite{Forget2021,Wu2022,OceananigansJOSS,Makie,Innes2018,Pluto}

\section{Science Applications}

Our current focus is on geospatial analyses that track global warming and marine heatwaves using Argo data \cite{Forget2024a}. Another example from our research is with the CStream research program (UK-US) which is releasing drifters near Florida Strait to track the nutrient stream that is associated with the Gulf Stream (Fig.~\ref{fig:Cstream}). Other applications at the scale of oceanic basins include tracking ocean plastic pollution, monitoring biological impacts of extreme events and global warming, or the optimization of the global climate monitoring fleet of ocean robots for e.g. cost. More locally, DTOR could be used in the context of field experiments such as S-MODE, to choose an example from the recent past. Related projects on digital twins, not focused on exploiting Julia, include the EU funded {\it Destination Earth} program, Mercator Ocean International's {\it Digital Twin Ocean}, and the UN Decade Action's DITTO initiative ({\it Digital Twins of The Ocean}).

\begin{figure}[hb] 
\includegraphics[width=\columnwidth]{figs/GulfStream_21_27_snapshot.png}
\caption{Tracking Gulf Stream waters from Florida Strait to the subpolar gyre using virtual drifters that follow the three dimensional ocean circulation. Each dot color indicates the virtual drifter depth -- red dots near the sea surface, while white dots are below 1500m depth.}
\label{fig:Cstream}
\end{figure}

\section{Acknowledgements}

Support from NASA awards 80NSSC20K0796, 80NSSC23K0355, 80NSSC22K1697, 1676067, and 1686358, as well as from the Simons Foundation via the CBIOMES and SCOPE-GRADIENTS program is acknowledged for this work.

\input{bib.tex}

\end{document}

### 2024-06-18 paper/paper.tex
mv docs/paper to paper (fix pdf build?)

--- 2024-05-31 docs/paper/paper.tex
@@
     label={lst:IndDispCode},
-    caption={Simulate surface drifter pathways in the Gulf of Mexico (Fig.~\ref{fig:drifters_speed}) from flow fields $u,v$ and initial positions $x,y$.
-The repetition of `u` and `v` in `FlowFields` reflects that flow fields are treated as time invariant in this example.}
+    caption={Simulate surface drifter pathways in the Gulf of Mexico (Fig.~\ref{fig:drifters_speed}) from flow fields $u,v$ and initial positions $x,y$.}
 ]
-using IndividualDisplacements, DataFrames
+using IndividualDisplacements
 
@@
 T=(0.,dT)
-F=FlowFields(u,u,v,v,T)
+F=FlowFields(u=u,v=v,period=T)
 I=Individuals(F,x,y)
 
-[solve(I,T.+dT*(n-1)) for n in 1:nt]
-trajectories=groupby(record(I),:ID)
+[solve!(I,T.+dT*(n-1)) for n in 1:nt]
+trajectories=groupby(I,:ID)
 \end{lstlisting}

### 2024-06-19 paper/paper.tex
Update paper.tex
try half of .bib
rm accents in ref.bib

@@
 Interaction between model and data is further enabled by the rich Julia ecosystem for machine learning, data assimilation, parameter inference, and so on.
-Fig.~\ref{fig:MLP} provides an example where we used \pkg{Flux.jl} \cite{Innes2018} to train a neural network to predict chlorophyll concentration (linked to marine microbe abundance) from environmental parameters as done in the CANYON model \cite{Sauzède2017,Bittig2018}.
+Fig.~\ref{fig:MLP} provides an example where we used \pkg{Flux.jl} \cite{Innes2018} to train a neural network to predict chlorophyll concentration (linked to marine microbe abundance) from environmental parameters as done in the CANYON model \cite{Sauzede2017,Bittig2018}.
 
@@
 
-%MITgcm : \cite{marshall1997fvi,camp-etal:04,HHG05,Forget2015a,Forget2024b}
-%OCCA / ECCO : \cite{Forget2007,Forget2010,Forget2015a,FFL15,FP15,Forget2024b}
-%More : \cite{Forget2021,Wu2022,OceananigansJOSS,Makie,Innes2018,Pluto}
-
 \section{Science Applications}

### 2024-08-02 docs/paper/paper.tex
fix code snippet

@@
 
-files_list=GDAC.files_list(); wmo=6900900
+lst=GDAC.files_list(); wmo=6900900
 argo=read(ArgoFloat(),wmo=wmo,files_list=lst)
 
-fig=plot(argo,option=:standard,pol=pol)
+fig=plot(argo,option=:standard)
 \end{lstlisting}

### 2024-08-02 src/files.jl
NOAA : get buoy lists, improve notebook

@@ -64,9 +64,47 @@ end #module GliderFiles
 
 module NOAA
 
-using Downloads, CSV, DataFrames, Dates, NCDatasets, Statistics
+using Downloads, CSV, DataFrames, Dates, NCDatasets, Statistics, HTTP
 import OceanRobots: NOAAbuoy, NOAAbuoy_monthly, THREDDS
 import Base: read
+
+"""
+    NOAA.list_stations()
+
+Get stations list from https://www.ndbc.noaa.gov/to_station.shtml
+"""
+function list_stations()
+    myurl0="https://www.ndbc.noaa.gov/to_station.shtml"
+    txt0=String(HTTP.get(myurl0).body)
+    txt1=split(txt0,"station_page.php?station=")[2:end]
+    String.([split(t,"\"")[1] for t in txt1])
+end
+
+"""
+    NOAA.list_realtime(;ext=:all)
+
+Get either files list from https://www.ndbc.noaa.gov/data/realtime2/
+or list of buoy codes that provide some file type 
+(e.g. "txt" for "Standard Meteorological Data")
+
+```
+lst0=NOAA.list_realtime()
+lst1=NOAA.list_realtime(ext=:txt)
+```
+"""
+function list_realtime(;ext=:all)
+    myurl0="https://www.ndbc.noaa.gov/data/realtime2/"
+    txt0=String(HTTP.get(myurl0).body)
+    txt1=split(txt0,"<tr><td valign=\"top\"><img src=\"/icons/text.gif\"")[3:end]
+    lst1=[split(split(t,"href=\"")[2],"\">")[1]  for t in txt1]
+    if ext!==:all
+        extxt=String(ext)
+        lst2=lst1[[split(t,".")[2]==string(ext) for t in lst1]]
+        [split(t,".")[1] for t in  lst2]
+    else
+        lst1
+    end
+end
 
 """
     NOAA.download(stations::Union(Array,Int),path=tempdir())
@@ -84,6 +122,20 @@ function download(stations::Union{Array,Int},path=tempdir())
         push!(files,fil1)
     end
     files
+end
+
+"""
+    NOAA.download(sta::String,path=tempdir())
+
+Download files for stations `sta` from `ndbc.noaa.gov` to `path`.
+"""
+function download(sta::Union{String,SubString},path=tempdir())
+    url0="https://www.ndbc.noaa.gov/data/realtime2/"
+    fil="$sta.txt"
[…]

### 2024-08-02 test/runtests.jl

@@ -59,8 +59,12 @@ using Test
 
     ##
 
-    stations=[41046, 44065]		
-	NOAA.download(stations)
+    allstations=NOAA.station_list()
+    metstations=NOAA.list_realtime(ext=:txt)
+
+    stations=metstations[1:200:end]
+    ids=NOAA.download(stations)
+
     b=read(NOAAbuoy(),41046)
     plot(b,"PRES")
     @test isa(b,NOAAbuoy)

### 2024-08-02 test/runtests.jl
fix

@@ -59,7 +59,7 @@ using Test
 
     ##
 
-    allstations=NOAA.station_list()
+    allstations=NOAA.list_stations()
     metstations=NOAA.list_realtime(ext=:txt)
 
     stations=metstations[1:200:end]

### 2024-08-02 dev/examples/Buoy_NWP_NOAA.jl
build based on e9711c2

@@ -1,5 +1,5 @@
 ### A Pluto.jl notebook ###
-# v0.19.42
+# v0.19.45
 
 using Markdown
 using InteractiveUtils
@@ -21,37 +21,33 @@ begin
 	"Done with packages"
 end
 
-# ╔═╡ 6b5ffee8-a230-42d4-8c49-ff14e65f52b7
-	TableOfContents()
-
 # ╔═╡ d6feeecc-87db-4bfd-8341-adede2df8ea0
 begin
 	img_url="https://nosc.noaa.gov/OSC/images/Kukui_and_NOAA_buoy_1.177308.JPG"
 	md"""# NOAA Buoys
-	
-	$(Resource(img_url,:width => 250))
 
-	!!! note 
-	    For more information about NOAA Buoys, visit <https://www.ndbc.noaa.gov/>
+	Visualize real time data for buoys that report `Standard Meteorological Data`.
 	
+	!!! note 
+	    For more information about NOAA Buoys, visit <https://www.ndbc.noaa.gov/> and links below.
+
+	$(Resource(img_url,:width => 250))
 	"""
 end
 
-# ╔═╡ 8b610dbe-f9ab-4498-8c98-fc8e83474981
-begin
-	md"""## Visualize Data"""
-end
+# ╔═╡ ee3373bb-a848-4919-9163-384b6f33632a
+TableOfContents()
 
 # ╔═╡ 46ff94e2-1b1e-454d-ab92-89be94123a47
-md"""## Appendix
-
-### Code and Data
+md"""## Code and Data
 """
 
 # ╔═╡ db662fb4-7413-11ec-1af6-43b18c0c15a9
 begin
 	#See https://www.ndbc.noaa.gov/
-    stations=[41046, 44065] #, 44097, 44013]		
+    stations=[41046, 44065,  
+		31005, 41047, 41117, 42058, 44027, 44084, 45002, 45136, 45164,
+		45206, 46028, 46077, 46146, 46237, 46277, 51208, 62121, 64045]	
 	NOAA.download(stations)
    	"Done with downloading data"
 end
@@ -60,27 +56,25 @@ end
 begin
 	sta_b = @bind sta Select(stations, default=stations[1])
 	myurl="https://www.ndbc.noaa.gov/station_page.php?station=$(sta)"
[…]

### 2024-08-02 dev/search_index.js

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"visuals/#Visuals","page":"Visuals","title":"Visuals","text":"","category":"section"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"The images below are from the notebook examples listed earlier in this doc.","category":"page"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"Global Data Coverage Individual Data Platforms\n(Image: ) (Image: )","category":"page"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"Argo Float Track Argo Float Profiles\n(Image: ) (Image: )","category":"page"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"Surface Drifter Positions Frequency Spectra\n(Image: ) (Image: )","category":"page"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"Spray Glider Data WHOTS Mooring Data\n(Image: ) (Image: )","category":"page"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"NOAA Time series Measured Ocean Warming\n(Image: ) (Image: )","category":"page"},{"location":"examples/#Notebooks","page":"Notebooks","title":"Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"note: Note\nThe static html rendering of the notebooks (this website) lack the interactivity that comes from Running Examples yourself.","category":"page"},{"location":"examples/#List-of-Notebooks","page":"Notebooks","title":"List of Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"The suite of examples includes :","category":"page"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"OceanOPS.jl (➭ code link) : global ocean observing systems\nBuoy_NWP_NOAA.jl (➭ code link) : NOAA station data (a few days)\nBuoy_NWP_NOAA_monthly.jl (➭ code link) : NOAA station data (monthly means) \nMooring_WHOTS.jl (➭ code link) : WHOTS mooring data\nDrifter_GDP.jl (➭
[…]

### 2024-08-03 src/files.jl
improve plots, notebooks, new GDP_list_*csv

@@ -299,8 +299,12 @@ function read_historical_txt(ID,y)
     df
 end
 
-function summary_table(z,ny=25)
-    T=round.(z.WTMP * 1.8 .+32,digits=1)
+function summary_table(z,ny=25;var="T(°F)")
+    if var=="T(°F)"
+        T=round.(z.WTMP * 1.8 .+32,digits=1)
+    else
+        T=buoy.data[:,var]
+    end
     p=[(T[z.YY.==y],T[z.YY.==y+ny]) for y in 1984:2001]
     i=findall([length(pp[1])*length(pp[2])==1 for pp in p])
     T0=[p[ii][1][1] for ii in i]
@@ -324,7 +328,7 @@ end #module NOAA
 
 module GDP
 
-using DataFrames, FTPClient, NCDatasets
+using DataFrames, FTPClient, NCDatasets, Dates, CSV
 import OceanRobots: SurfaceDrifter
 import Base: read
 
@@ -337,12 +341,19 @@ Get list of drifter files from NOAA ftp server or the corresponding webpage.
 - <https://www.aoml.noaa.gov/ftp/pub/phod/lumpkin/hourly/v2.00/netcdf/>
 """
 function list_files()
-    list_files=DataFrame("folder" => [],"filename" => [])
-    ftp=FTP("ftp://ftp.aoml.noaa.gov/pub/phod/lumpkin/hourly/v2.00/netcdf/")
-    tmp=readdir(ftp)
-    append!(list_files,DataFrame("folder" => "","filename" => tmp))
-    list_files.ID=[parse(Int,split(f,"_")[2][1:end-3]) for f in list_files.filename]
-    list_files
+    td=string(Dates.today())
+    fil=joinpath(tempdir(),"GDP_list_$(td).csv")
+    if isfile(fil)
+        list_files=CSV.read(fil,DataFrame)
+    else
+        list_files=DataFrame("folder" => [],"filename" => [])
+        ftp=FTP("ftp://ftp.aoml.noaa.gov/pub/phod/lumpkin/hourly/v2.00/netcdf/")
+        tmp=readdir(ftp)
+        append!(list_files,DataFrame("folder" => "","filename" => tmp))
+        list_files.ID=[parse(Int,split(f,"_")[2][1:end-3]) for f in list_files.filename]
+        CSV.write(fil,list_files)
+        list_files
+    end
 end
 
[…]

### 2024-08-03 src/files.jl
write/read file lists from temp file

@@ -389,16 +389,19 @@ function download(list_files,ii=1)
 end
 
 """
-    read(x::SurfaceDrifter,ii::Int; list_files=[])
+    read(x::SurfaceDrifter,ii::Int)
 
-Open file `list_files.filename[ii]` from NOAA ftp server using `NCDatasets.Dataset`.
+Open file `ii` from NOAA ftp server using `NCDatasets.Dataset`.
 
 <ftp://ftp.aoml.noaa.gov/pub/phod/lumpkin/hourly/v2.00/netcdf/>
 or the corresponding webpage 
 
+Note: the first time this method is used, it calls `GDP.list_files()` 
+to get the list of drifters from server, and save it to a temporary file.
+
 ```
-lst=GDP.list_files()
-sd=read(SurfaceDrifter(),1,list_files=lst)
+using OceanRobots
+sd=read(SurfaceDrifter(),1)
 ```
 """
 read(x::SurfaceDrifter,ii::Int; list_files=[]) = begin
@@ -555,7 +558,31 @@ end
 
 module ArgoFiles
 
-using NCDatasets, Downloads, CSV, DataFrames, Interpolations, Statistics
+using NCDatasets, Downloads, CSV, DataFrames, Interpolations, Statistics, Dates
+
+"""
+    ArgoFiles.list_floats(;list=DataFrame())
+
+Get list of Argo profilers from file `ArgoFiles.list_floats()`.
+
+Or write provided `list` to file as a DataFrame.
+
+```
+using OceanRobots, ArgoData
+ArgoFiles.list_floats(list=GDAC.files_list())
+```
+"""
+function list_floats(;list=DataFrame())
+    td=string(Dates.today())
+    fil=joinpath(tempdir(),"Argo_list_$(td).csv")
+    if isempty(list)
+        files_list=CSV.read(fil,DataFrame)
+    else
+        files_list=list
+        CSV.write(fil,files_list)
+        files_list
+    end
+end
 
 """
     ArgoFiles.download(files_list,wmo)

### 2024-08-03 test/runtests.jl

@@ -9,8 +9,7 @@ using Test
     @test isa(files[1],String)
     @test isempty(folders)
 
-    lst=GDP.list_files()
-    b=read(SurfaceDrifter(),1,list_files=lst)
+    b=read(SurfaceDrifter(),1)
     @test haskey(b.data,"ve")
 
     f3=plot(b)

### 2024-08-03 src/files.jl
improve docs, adding plots

@@ -391,10 +391,9 @@ end
 """
     read(x::SurfaceDrifter,ii::Int)
 
-Open file `ii` from NOAA ftp server using `NCDatasets.Dataset`.
+Open file number `ii` from NOAA ftp server using `NCDatasets.jl`.
 
-<ftp://ftp.aoml.noaa.gov/pub/phod/lumpkin/hourly/v2.00/netcdf/>
-or the corresponding webpage 
+Server : ftp://ftp.aoml.noaa.gov/pub/phod/lumpkin/hourly/v2.00/netcdf/
 
 Note: the first time this method is used, it calls `GDP.list_files()` 
 to get the list of drifters from server, and save it to a temporary file.

### 2024-08-03 dev/search_index.js
build based on 576fede

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"visuals/#Visuals","page":"Visuals","title":"Visuals","text":"","category":"section"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"The images below are from the notebook examples listed earlier in this doc.","category":"page"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"Global Data Coverage Individual Data Platforms\n(Image: ) (Image: )","category":"page"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"Argo Float Track Argo Float Profiles\n(Image: ) (Image: )","category":"page"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"Surface Drifter Positions Frequency Spectra\n(Image: ) (Image: )","category":"page"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"Spray Glider Data WHOTS Mooring Data\n(Image: ) (Image: )","category":"page"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"NOAA Time series Measured Ocean Warming\n(Image: ) (Image: )","category":"page"},{"location":"examples/#Notebooks","page":"Notebooks","title":"Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"note: Note\nThe static html rendering of the notebooks (this website) lack the interactivity that comes from Running Examples yourself.","category":"page"},{"location":"examples/#List-of-Notebooks","page":"Notebooks","title":"List of Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"The suite of examples includes :","category":"page"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"OceanOPS.jl (➭ code link) : global ocean observing systems\nBuoy_NWP_NOAA.jl (➭ code link) : NOAA station data (a few days)\nBuoy_NWP_NOAA_monthly.jl (➭ code link) : NOAA station data (monthly means) \nMooring_WHOTS.jl (➭ code link) : WHOTS mooring data\nDrifter_GDP.jl (➭
[…]

### 2024-08-04 examples/Glider_Spray.jl
update notebook deps

@@ -1,5 +1,5 @@
 ### A Pluto.jl notebook ###
-# v0.19.42
+# v0.19.45
 
 using Markdown
 using InteractiveUtils
@@ -172,6 +172,11 @@ weakdeps = ["StaticArrays"]
     [deps.Adapt.extensions]
     AdaptStaticArraysExt = "StaticArrays"
 
+[[deps.AdaptivePredicates]]
+git-tree-sha1 = "7d5da5dd472490d048b081ca1bda4a7821b06456"
+uuid = "35492f91-a3bd-45ad-95db-fcad7dcfedb7"
+version = "1.1.1"
+
 [[deps.AliasTables]]
 deps = ["PtrArrays", "Random"]
 git-tree-sha1 = "9876e1e164b144ca45e9e3198d0b689cadfed9ff"
@@ -193,9 +198,9 @@ uuid = "56f22d72-fd6d-98f1-02f0-08ddc0907c33"
 
 [[deps.Automa]]
 deps = ["PrecompileTools", "TranscodingStreams"]
-git-tree-sha1 = "588e0d680ad1d7201d4c6a804dcb1cd9cba79fbb"
+git-tree-sha1 = "014bc22d6c400a7703c0f5dc1fdc302440cf88be"
 uuid = "67c07d97-cdcb-5c2c-af73-a7f9c32a568b"
-version = "1.0.3"
+version = "1.0.4"
 
 [[deps.AxisAlgorithms]]
 deps = ["LinearAlgebra", "Random", "SparseArrays", "WoodburyMatrices"]
@@ -213,9 +218,9 @@ version = "0.4.7"
 uuid = "2a0f44e3-6c83-55bd-87e4-b1978d98bd5f"
 
 [[deps.BitFlags]]
-git-tree-sha1 = "2dc09997850d68179b69dafb58ae806167a32b1b"
+git-tree-sha1 = "0691e34b3bb8be9307330f88d1a3c3f25466c24d"
 uuid = "d1d4a3ce-64b1-5f1a-9ba4-7e7e69966f35"
-version = "0.1.8"
+version = "0.1.9"
 
 [[deps.Blosc_jll]]
 deps = ["Artifacts", "JLLWrappers", "Libdl", "Lz4_jll", "Zlib_jll", "Zstd_jll"]
@@ -262,10 +267,10 @@ uuid = "159f3aea-2a34-519c-b102-8c37f9878175"
 version = "1.0.5"
 
 [[deps.CairoMakie]]
[…]

### 2024-08-04 examples/Mooring_WHOTS.jl

@@ -1,5 +1,5 @@
 ### A Pluto.jl notebook ###
-# v0.19.42
+# v0.19.45
 
 using Markdown
 using InteractiveUtils
@@ -150,6 +150,11 @@ weakdeps = ["StaticArrays"]
     [deps.Adapt.extensions]
     AdaptStaticArraysExt = "StaticArrays"
 
+[[deps.AdaptivePredicates]]
+git-tree-sha1 = "7d5da5dd472490d048b081ca1bda4a7821b06456"
+uuid = "35492f91-a3bd-45ad-95db-fcad7dcfedb7"
+version = "1.1.1"
+
 [[deps.AliasTables]]
 deps = ["PtrArrays", "Random"]
 git-tree-sha1 = "9876e1e164b144ca45e9e3198d0b689cadfed9ff"
@@ -171,9 +176,9 @@ uuid = "56f22d72-fd6d-98f1-02f0-08ddc0907c33"
 
 [[deps.Automa]]
 deps = ["PrecompileTools", "TranscodingStreams"]
-git-tree-sha1 = "588e0d680ad1d7201d4c6a804dcb1cd9cba79fbb"
+git-tree-sha1 = "014bc22d6c400a7703c0f5dc1fdc302440cf88be"
 uuid = "67c07d97-cdcb-5c2c-af73-a7f9c32a568b"
-version = "1.0.3"
+version = "1.0.4"
 
 [[deps.AxisAlgorithms]]
 deps = ["LinearAlgebra", "Random", "SparseArrays", "WoodburyMatrices"]
@@ -191,9 +196,9 @@ version = "0.4.7"
 uuid = "2a0f44e3-6c83-55bd-87e4-b1978d98bd5f"
 
 [[deps.BitFlags]]
-git-tree-sha1 = "2dc09997850d68179b69dafb58ae806167a32b1b"
+git-tree-sha1 = "0691e34b3bb8be9307330f88d1a3c3f25466c24d"
 uuid = "d1d4a3ce-64b1-5f1a-9ba4-7e7e69966f35"
-version = "0.1.8"
+version = "0.1.9"
 
 [[deps.Blosc_jll]]
 deps = ["Artifacts", "JLLWrappers", "Libdl", "Lz4_jll", "Zlib_jll", "Zstd_jll"]
@@ -240,10 +245,10 @@ uuid = "159f3aea-2a34-519c-b102-8c37f9878175"
 version = "1.0.5"
 
 [[deps.CairoMakie]]
[…]

### 2024-08-04 examples/OceanOPS.jl

@@ -1,5 +1,5 @@
 ### A Pluto.jl notebook ###
-# v0.19.42
+# v0.19.45
 
 using Markdown
 using InteractiveUtils
@@ -213,6 +213,11 @@ weakdeps = ["StaticArrays"]
     [deps.Adapt.extensions]
     AdaptStaticArraysExt = "StaticArrays"
 
+[[deps.AdaptivePredicates]]
+git-tree-sha1 = "7d5da5dd472490d048b081ca1bda4a7821b06456"
+uuid = "35492f91-a3bd-45ad-95db-fcad7dcfedb7"
+version = "1.1.1"
+
 [[deps.AliasTables]]
 deps = ["PtrArrays", "Random"]
 git-tree-sha1 = "9876e1e164b144ca45e9e3198d0b689cadfed9ff"
@@ -234,9 +239,9 @@ uuid = "56f22d72-fd6d-98f1-02f0-08ddc0907c33"
 
 [[deps.Automa]]
 deps = ["PrecompileTools", "TranscodingStreams"]
-git-tree-sha1 = "588e0d680ad1d7201d4c6a804dcb1cd9cba79fbb"
+git-tree-sha1 = "014bc22d6c400a7703c0f5dc1fdc302440cf88be"
 uuid = "67c07d97-cdcb-5c2c-af73-a7f9c32a568b"
-version = "1.0.3"
+version = "1.0.4"
 
 [[deps.AxisAlgorithms]]
 deps = ["LinearAlgebra", "Random", "SparseArrays", "WoodburyMatrices"]
@@ -254,9 +259,9 @@ version = "0.4.7"
 uuid = "2a0f44e3-6c83-55bd-87e4-b1978d98bd5f"
 
 [[deps.BitFlags]]
-git-tree-sha1 = "2dc09997850d68179b69dafb58ae806167a32b1b"
+git-tree-sha1 = "0691e34b3bb8be9307330f88d1a3c3f25466c24d"
 uuid = "d1d4a3ce-64b1-5f1a-9ba4-7e7e69966f35"
-version = "0.1.8"
+version = "0.1.9"
 
 [[deps.Blosc_jll]]
 deps = ["Artifacts", "JLLWrappers", "Libdl", "Lz4_jll", "Zlib_jll", "Zstd_jll"]
@@ -271,9 +276,9 @@ uuid = "6e34b625-4abd-537c-b88f-471c36dfa7a0"
 version = "1.0.8+1"
 
 [[deps.CEnum]]
[…]

### 2024-08-04 dev/examples/Buoy_NWP_NOAA.jl
build based on 789b57d

@@ -435,9 +435,9 @@ uuid = "ade2ca70-3891-5945-98fb-dc099432e06a"
 
 [[deps.DelaunayTriangulation]]
 deps = ["AdaptivePredicates", "EnumX", "ExactPredicates", "Random"]
-git-tree-sha1 = "1abb6a8541775a0bf82749ac8373a34e9f2f71e0"
+git-tree-sha1 = "8630ce72d9d2028cfdf6b55ffec1fc7515ef5ce2"
 uuid = "927a84f5-c5f4-47a5-9785-b46e178433df"
-version = "1.1.1"
+version = "1.1.2"
 
 [[deps.DiskArrays]]
 deps = ["LRUCache", "OffsetArrays"]
@@ -1203,9 +1203,9 @@ version = "0.5.5"
 
 [[deps.OceanRobots]]
 deps = ["CFTime", "CSV", "DataFrames", "DataStructures", "Dataverse", "Dates", "Downloads", "FTPClient", "Glob", "HTTP", "Interpolations", "JSON3", "LightXML", "NCDatasets", "Printf", "Statistics", "URIs"]
-git-tree-sha1 = "944b55a822eb1169663a782c7a106a2ec3436661"
+git-tree-sha1 = "05107d8eeabbaf7a77fcffbb333594867292d79e"
 uuid = "0b51df41-3294-4961-8d23-db645e32016d"
-version = "0.2.0"
+version = "0.2.1"
 
     [deps.OceanRobots.extensions]
     OceanRobotsArgoDataExt = ["ArgoData"]

### 2024-08-04 dev/search_index.js

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"visuals/#Visuals","page":"Visuals","title":"Visuals","text":"","category":"section"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"The images below are from the notebook examples listed earlier in this doc.","category":"page"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"Global Data Coverage Individual Data Platforms\n(Image: ) (Image: )","category":"page"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"Argo Float Track Argo Float Profiles\n(Image: ) (Image: )","category":"page"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"Surface Drifter Positions Frequency Spectra\n(Image: ) (Image: )","category":"page"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"Spray Glider Data WHOTS Mooring Data\n(Image: ) (Image: )","category":"page"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"NOAA Time series Measured Ocean Warming\n(Image: ) (Image: )","category":"page"},{"location":"examples/#Notebooks","page":"Notebooks","title":"Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"note: Note\nThe static html rendering of the notebooks (this website) lack the interactivity that comes from Running Examples yourself.","category":"page"},{"location":"examples/#List-of-Notebooks","page":"Notebooks","title":"List of Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"The suite of examples includes :","category":"page"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"OceanOPS.jl (➭ code link) : global ocean observing systems\nBuoy_NWP_NOAA.jl (➭ code link) : NOAA station data (a few days)\nBuoy_NWP_NOAA_monthly.jl (➭ code link) : NOAA station data (monthly means) \nMooring_WHOTS.jl (➭ code link) : WHOTS mooring data\nDrifter_GDP.jl (➭ code link) : drifter time series\nDrifter_CloudDrift.jl (➭ code link) : drifter statistics\nFloat_Argo.j
[…]

### 2024-08-04 v0.2.1/examples/Buoy_NWP_NOAA.jl
build based on 576fede

@@ -1,0 +1,1962 @@
+### A Pluto.jl notebook ###
+# v0.19.45
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
+# ╔═╡ c8d36a50-0473-410a-91fa-102f3d071388
+begin
+	using Downloads, ClimateModels
+	using OceanRobots, PlutoUI, CairoMakie
+	"Done with packages"
+end
+
+# ╔═╡ d6feeecc-87db-4bfd-8341-adede2df8ea0
+begin
+	img_url="https://nosc.noaa.gov/OSC/images/Kukui_and_NOAA_buoy_1.177308.JPG"
+	md"""# NOAA Buoys
+
+	Visualize real time data for buoys that report `Standard Meteorological Data`.
+	
+	!!! note 
+	    For more information about NOAA Buoys, visit <https://www.ndbc.noaa.gov/> and links below.
+
+	$(Resource(img_url,:width => 250))
+	"""
+end
+
+# ╔═╡ ee3373bb-a848-4919-9163-384b6f33632a
+TableOfContents()
+
+# ╔═╡ 46ff94e2-1b1e-454d-ab92-89be94123a47
+md"""## Code and Data
+"""
+
+# ╔═╡ db662fb4-7413-11ec-1af6-43b18c0c15a9
+begin
+	#See https://www.ndbc.noaa.gov/
+    stations=[41046, 44065,  
+		31005, 41047, 41117, 42058, 44027, 44084, 45002, 45136, 45164,
[…]

### 2024-08-04 v0.2.1/examples/Buoy_NWP_NOAA_monthly.jl

@@ -1,0 +1,1907 @@
+### A Pluto.jl notebook ###
+# v0.19.45
+
+using Markdown
+using InteractiveUtils
+
+# ╔═╡ 920b7a98-8478-4ad7-8897-8e5d92737199
+begin
+	using PlutoUI, CairoMakie, OceanRobots
+	"Done with packages"
+end
+
+# ╔═╡ 91db1379-9f47-4982-9716-f755451f819f
+begin
+img_url="https://nosc.noaa.gov/OSC/images/Kukui_and_NOAA_buoy_1.177308.JPG"
+	
+md"""# NOAA Buoys / Monthly Means"""
+end
+
+# ╔═╡ 2f87a4a9-ad5d-46ff-961b-028de3a27a23
+PlutoUI.TableOfContents()
+
+# ╔═╡ d106d4c1-1d2e-40b3-8958-901ea437a524
+begin
+md"""In this notebook, you will compute climatologies and distributions from NOAA buoy data.
+
+$(Resource(img_url,:width => 250))
+
+!!! note 
+	For more information about NOAA Buoys, visit <https://www.ndbc.noaa.gov/> and links below.
+
+## Visualize Data	
+"""
+end
+
+# ╔═╡ 502dde03-9ce3-4e15-bfc4-854c87a60026
+md"""## Data Summary
+
+Plot below shows:
+
+- top left: the full distribution of 25 year temperatue changes, using all individual months and years, is shown in the top left corner.
+- top right: averaged month by month, the 25 year change in temperature is positive for each month -- between +2 and +4 degrees, approximately.
+- bottom: the mean seasonal cycle in the ~1990s (blue) and ~2010s (orange). Range is ~ 25 degree in both cases. Shift between the curves is what's shown in top panel.
+"""
+
+# ╔═╡ 34a9a048-da3e-11ec-2017-b7b762895d86
+begin
+	ID=44013
+    buoy=read(NOAAbuoy_monthly(),ID)
+end
+
+# ╔═╡ 051ea6ce-a699-4a08-a4cf-214875bd3ca7
+plot(buoy;option=:demo)
+
[…]

### 2024-08-04 v0.2.1/examples/Drifter_GDP.jl

@@ -1,0 +1,1910 @@
+### A Pluto.jl notebook ###
+# v0.19.45
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
+# ╔═╡ d61376ca-76f2-11ec-0393-83d9b38831ca
+begin
+	using OceanRobots, PlutoUI, CairoMakie
+	"Done with packages"
+end
+
+# ╔═╡ e6d47534-3bdb-401f-8758-12ebce4232f6
+TableOfContents()
+
+# ╔═╡ 84964782-cdd1-4773-a134-04d486e69856
+md"""# Surface Drifters
+
+Here we learn to download, read, and plot one hourly drifter data file from [NOAA webpage](https://www.aoml.noaa.gov/ftp/pub/phod/lumpkin/hourly/v2.00/netcdf/) or its [ftp server](ftp://ftp.aoml.noaa.gov/pub/phod/lumpkin/hourly/v2.00/netcdf/). 
+
+!!! note
+    See [global drifter website](https://www.aoml.noaa.gov/phod/gdp/hourly_data.php) for more information about this data set.
+"""
+
+# ╔═╡ 568d54ae-19a6-4ff4-ae0b-e131693029e5
+begin
+	url0="https://www.aoml.noaa.gov/wp-content/uploads/2020/12/GDP-map.jpg"
[…]

### 2024-08-04 v0.2.1/examples/Float_Argo.jl

@@ -1,0 +1,2095 @@
+### A Pluto.jl notebook ###
+# v0.19.42
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
+# ╔═╡ 8539e67f-6361-409a-9dbe-e8dcb2c7e10d
+begin
+	using OceanRobots, ArgoData, CairoMakie, PlutoUI, PrettyTables, MeshArrays
+	"Done with packages"
+end
+
+# ╔═╡ dc017980-cde3-49bc-a5e0-44be9bb08cec
+begin
+	using Shapefile, DataDeps
+	pol_file=demo.download_polygons("ne_110m_admin_0_countries.shp")
+	pol=MeshArrays.read_polygons(pol_file)
+	"Done with country boundaries"
+end
+
+# ╔═╡ 89647c4e-e568-4d3a-af57-bcc541744e38
+md"""# Argo Floats
+
+The standard Argo platform is a profiling float that drifts at 1000m depth. They come back to the surface every ten days, just after collecting vertocal profiles of temperature and salinity, and transmit their data via satellite. 
+
+!!! tip
+    For more information about the international Argo program please refer to, for example, <https://argo.ucsd.edu> or <https://biogeochemical-argo.org>.
+"""
+
+# ╔═╡ 09a2aa6e-16bc-4582-9d5f-c50432e3f0ca
+begin
[…]

### 2024-08-04 v0.2.1/examples/Mooring_WHOTS.jl

@@ -1,0 +1,1897 @@
+### A Pluto.jl notebook ###
+# v0.19.42
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
+# ╔═╡ 5fc8cc85-7bd4-4fea-8c6f-01dabee6eb5f
+begin
+	using OceanRobots, CairoMakie, PlutoUI
+	"Done with packages"
+end
+
+# ╔═╡ 538ddc08-85bd-426b-92bc-f5dd78d38d5d
+TableOfContents()
+
+# ╔═╡ 720e1461-81b9-42b6-88be-0115a17268c0
+md"""# WHOTS mooring
+
+Here we plot time series from the [WHOTS mooring](http://www.soest.hawaii.edu/whots/wh_data.html) which measures both Ocean and Atmosphere variables. This is one of the long time series available to study Climate. See <http://www.oceansites.org/> for more data like this.
+"""
+
+# ╔═╡ e7dc453e-3bf2-4289-b55d-66eab3636d7b
+begin
+	url0="https://insideclimatenews.org/wp-content/uploads/2020/07/ohcean-mooring_noaa.jpg"
+	url1="https://aco-ssds.soest.hawaii.edu/ALOHA/img/slideshow3.jpg"
[…]

### 2024-08-04 v0.2.1/examples/SatelliteAltimetry.jl

@@ -1,0 +1,2062 @@
+### A Pluto.jl notebook ###
+# v0.19.42
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
+# ╔═╡ a8e0b727-a416-4aad-b660-69e5470c7e9e
+begin
+	using OceanRobots, CairoMakie, Dataverse, ArchGDAL, PlutoUI
+	OceanRobotsMakieExt=Base.get_extension(OceanRobots, :OceanRobotsMakieExt)
+	"Done with Julia packages"
+end
+
+# ╔═╡ 71e87ed3-5a9f-49aa-99af-cf144501c678
+md"""# Regional Sea Level
+
+Visualize dynamic sea level anomaly (colors) and ocean bathymetry/topography (contours) in the region of the Azores as a function of space and time. 
+
+!!! tip
+    Choose between two data sets (sources: NASA PODAAC, ESA CMEMS), select time, or generate animation.
+"""
+
+# ╔═╡ a58cc4b4-7023-4dcf-a5f4-6366be8047a3
+TableOfContents()
+
+# ╔═╡ 62e0b8a9-0025-4ce7-9538-b6114d97b762
+md"""## Visualize Data
+
+- Color shading is sea level anomaly from a gridded data product based on satellite measurement (altimetry).
[…]

### 2024-08-04 v0.2.1/search_index.js

@@ -1,0 +1,3 @@
+var documenterSearchIndex = {"docs":
+[{"location":"visuals/#Visuals","page":"Visuals","title":"Visuals","text":"","category":"section"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"The images below are from the notebook examples listed earlier in this doc.","category":"page"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"Global Data Coverage Individual Data Platforms\n(Image: ) (Image: )","category":"page"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"Argo Float Track Argo Float Profiles\n(Image: ) (Image: )","category":"page"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"Surface Drifter Positions Frequency Spectra\n(Image: ) (Image: )","category":"page"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"Spray Glider Data WHOTS Mooring Data\n(Image: ) (Image: )","category":"page"},{"location":"visuals/","page":"Visuals","title":"Visuals","text":"NOAA Time series Measured Ocean Warming\n(Image: ) (Image: )","category":"page"},{"location":"examples/#Notebooks","page":"Notebooks","title":"Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"note: Note\nThe static html rendering of the notebooks (this website) lack the interactivity that comes from Running Examples yourself.","category":"page"},{"location":"examples/#List-of-Notebooks","page":"Notebooks","title":"List of Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"The suite of examples includes :","category":"page"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"OceanOPS.jl (➭ code link) : global ocean observing systems\nBuoy_NWP_NOAA.jl (➭ code link) : NOAA station data (a few days)\nBuoy_NWP_NOAA_monthly.jl (➭ code link) : NOAA station data (monthly means) \nMooring_WHOTS.jl (➭ code link) : WHOTS mooring data\nDrifter_GDP.jl (➭ code link) : drifter time series\nDrifter_CloudDrift.jl (➭ code link) : drifter statistics\nFloat_Argo.j
[…]

### 2024-08-05 dev/search_index.js
build based on 6656e6d

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"examples/#Notebooks","page":"Notebooks","title":"Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"note: Note\nThe static html rendering of the notebooks (this website) lack the interactivity that comes from Running Examples yourself.","category":"page"},{"location":"examples/#List-of-Notebooks","page":"Notebooks","title":"List of Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"The suite of examples includes :","category":"page"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"OceanOPS.jl (➭ code link) : global ocean observing systems\nBuoy_NWP_NOAA.jl (➭ code link) : NOAA station data (a few days)\nBuoy_NWP_NOAA_monthly.jl (➭ code link) : NOAA station data (monthly means) \nMooring_WHOTS.jl (➭ code link) : WHOTS mooring data\nDrifter_GDP.jl (➭ code link) : drifter time series\nDrifter_CloudDrift.jl (➭ code link) : drifter statistics\nFloat_Argo.jl (➭ code link) : Argo profiling float data\nGlider_Spray.jl (➭ code link) : underwater glider data\nSatelliteAltimetry.jl (➭ code link) : gridded satellite data","category":"page"},{"location":"examples/#More-Notebooks","page":"Notebooks","title":"More Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"For Argo and state estimates, see ArgoData.jl\nFor drifter data simulations, see IndividualDisplacements.jl","category":"page"},{"location":"examples/#Using-Notebooks","page":"Notebooks","title":"Using Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"The examples are most easily run using Pluto.jl. To do it this way, one just needs to copy a code link provided above and paste this URL into the Pluto.jl interface.","category":"page"},{"location":"reference/#User-Interface-(API)","page":"User Interface","title":"User Interface (API)","text":"",
[…]

### 2024-09-03 dev/examples/Buoy_NWP_NOAA.jl
build based on 66a76b7

@@ -1,5 +1,5 @@
 ### A Pluto.jl notebook ###
-# v0.19.45
+# v0.19.46
 
 using Markdown
 using InteractiveUtils
@@ -131,7 +131,7 @@ PlutoUI = "7f904dfe-b85e-4ff6-b463-dae2292396a8"
 PLUTO_MANIFEST_TOML_CONTENTS = """
 # This file is machine-generated - editing it directly is not advised
 
-julia_version = "1.10.3"
+julia_version = "1.10.4"
 manifest_format = "2.0"
 project_hash = "dab0cebf879211c8791496c0ee2161abb0037489"
 
@@ -257,27 +257,21 @@ version = "0.10.14"
 
 [[deps.Cairo]]
 deps = ["Cairo_jll", "Colors", "Glib_jll", "Graphics", "Libdl", "Pango_jll"]
-git-tree-sha1 = "d0b3f8b4ad16cb0a2988c6788646a5e6a17b6b1b"
+git-tree-sha1 = "7b6ad8c35f4bc3bca8eb78127c8b99719506a5fb"
 uuid = "159f3aea-2a34-519c-b102-8c37f9878175"
-version = "1.0.5"
+version = "1.1.0"
 
 [[deps.CairoMakie]]
 deps = ["CRC32c", "Cairo", "Cairo_jll", "Colors", "FileIO", "FreeType", "GeometryBasics", "LinearAlgebra", "Makie", "PrecompileTools"]
-git-tree-sha1 = "e4da5095557f24713bae4c9f50e34ff4d3b959c0"
+git-tree-sha1 = "361dec06290d76b6d70d0c7dc888038eec9df63a"
 uuid = "13f3f980-e62b-5c42-98c6-ff1f3baf88f0"
-version = "0.12.5"
+version = "0.12.9"
 
 [[deps.Cairo_jll]]
 deps = ["Artifacts", "Bzip2_jll", "CompilerSupportLibraries_jll", "Fontconfig_jll", "FreeType2_jll", "Glib_jll", "JLLWrappers", "LZO_jll", "Libdl", "Pixman_jll", "Xorg_libXext_jll", "Xorg_libXrender_jll", "Zlib_jll", "libpng_jll"]
 git-tree-sha1 = "a2f1c8c668c8e3cb4cca4e57a8efdb09067bb3fd"
 uuid = "83423d85-b0ee-5818-9007-b63ccbeb887a"
 version = "1.18.0+2"
[…]

### 2024-09-03 dev/examples/SatelliteAltimetry.jl

@@ -1,5 +1,5 @@
 ### A Pluto.jl notebook ###
-# v0.19.45
+# v0.19.46
 
 using Markdown
 using InteractiveUtils
@@ -138,7 +138,7 @@ PlutoUI = "7f904dfe-b85e-4ff6-b463-dae2292396a8"
 PLUTO_MANIFEST_TOML_CONTENTS = """
 # This file is machine-generated - editing it directly is not advised
 
-julia_version = "1.10.3"
+julia_version = "1.10.4"
 manifest_format = "2.0"
 project_hash = "fb9e0ab2f9dcd953f9861e0b172e4250ab8d11d0"
 
@@ -280,27 +280,21 @@ version = "0.10.14"
 
 [[deps.Cairo]]
 deps = ["Cairo_jll", "Colors", "Glib_jll", "Graphics", "Libdl", "Pango_jll"]
-git-tree-sha1 = "d0b3f8b4ad16cb0a2988c6788646a5e6a17b6b1b"
+git-tree-sha1 = "7b6ad8c35f4bc3bca8eb78127c8b99719506a5fb"
 uuid = "159f3aea-2a34-519c-b102-8c37f9878175"
-version = "1.0.5"
+version = "1.1.0"
 
 [[deps.CairoMakie]]
 deps = ["CRC32c", "Cairo", "Cairo_jll", "Colors", "FileIO", "FreeType", "GeometryBasics", "LinearAlgebra", "Makie", "PrecompileTools"]
-git-tree-sha1 = "e4da5095557f24713bae4c9f50e34ff4d3b959c0"
+git-tree-sha1 = "361dec06290d76b6d70d0c7dc888038eec9df63a"
 uuid = "13f3f980-e62b-5c42-98c6-ff1f3baf88f0"
-version = "0.12.5"
+version = "0.12.9"
 
 [[deps.Cairo_jll]]
 deps = ["Artifacts", "Bzip2_jll", "CompilerSupportLibraries_jll", "Fontconfig_jll", "FreeType2_jll", "Glib_jll", "JLLWrappers", "LZO_jll", "Libdl", "Pixman_jll", "Xorg_libXext_jll", "Xorg_libXrender_jll", "Zlib_jll", "libpng_jll"]
 git-tree-sha1 = "a2f1c8c668c8e3cb4cca4e57a8efdb09067bb3fd"
 uuid = "83423d85-b0ee-5818-9007-b63ccbeb887a"
[…]

### 2024-09-03 v0.2.3/examples/Buoy_NWP_NOAA.jl
build based on 896c3ea

@@ -1,0 +1,1962 @@
+### A Pluto.jl notebook ###
+# v0.19.46
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
+# ╔═╡ c8d36a50-0473-410a-91fa-102f3d071388
+begin
+	using Downloads, ClimateModels
+	using OceanRobots, PlutoUI, CairoMakie
+	"Done with packages"
+end
+
+# ╔═╡ d6feeecc-87db-4bfd-8341-adede2df8ea0
+begin
+	img_url="https://nosc.noaa.gov/OSC/images/Kukui_and_NOAA_buoy_1.177308.JPG"
+	md"""# NOAA Buoys
+
+	Visualize real time data for buoys that report `Standard Meteorological Data`.
+	
+	!!! note 
+	    For more information about NOAA Buoys, visit <https://www.ndbc.noaa.gov/> and links below.
+
+	$(Resource(img_url,:width => 250))
+	"""
+end
+
+# ╔═╡ ee3373bb-a848-4919-9163-384b6f33632a
+TableOfContents()
+
+# ╔═╡ 46ff94e2-1b1e-454d-ab92-89be94123a47
+md"""## Code and Data
+"""
+
+# ╔═╡ db662fb4-7413-11ec-1af6-43b18c0c15a9
+begin
+	#See https://www.ndbc.noaa.gov/
+    stations=[41046, 44065,  
+		31005, 41047, 41117, 42058, 44027, 44084, 45002, 45136, 45164,
[…]

### 2024-09-03 v0.2.3/examples/Drifter_GDP.jl

@@ -1,0 +1,1910 @@
+### A Pluto.jl notebook ###
+# v0.19.46
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
+# ╔═╡ d61376ca-76f2-11ec-0393-83d9b38831ca
+begin
+	using OceanRobots, PlutoUI, CairoMakie
+	"Done with packages"
+end
+
+# ╔═╡ e6d47534-3bdb-401f-8758-12ebce4232f6
+TableOfContents()
+
+# ╔═╡ 84964782-cdd1-4773-a134-04d486e69856
+md"""# Surface Drifters
+
+Here we learn to download, read, and plot one hourly drifter data file from [NOAA webpage](https://www.aoml.noaa.gov/ftp/pub/phod/lumpkin/hourly/v2.00/netcdf/) or its [ftp server](ftp://ftp.aoml.noaa.gov/pub/phod/lumpkin/hourly/v2.00/netcdf/). 
+
+!!! note
+    See [global drifter website](https://www.aoml.noaa.gov/phod/gdp/hourly_data.php) for more information about this data set.
+"""
+
+# ╔═╡ 568d54ae-19a6-4ff4-ae0b-e131693029e5
+begin
+	url0="https://www.aoml.noaa.gov/wp-content/uploads/2020/12/GDP-map.jpg"
[…]

### 2024-09-03 v0.2.3/examples/Glider_Spray.jl

@@ -1,0 +1,1933 @@
+### A Pluto.jl notebook ###
+# v0.19.46
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
+# ╔═╡ 0247a51e-c89b-11ec-071f-bb82fe257adc
+begin
+	using OceanRobots, PlutoUI, CairoMakie
+	"Done with Software Packages"
+end
+
+# ╔═╡ e5b9772e-cbb5-42f0-bacb-5bae6bc8d5b6
+md"""# Spray Gliders
+
+Spray gliders autonomously collect measurements in the upper kilometer of the ocean during missions typically lasting three to four months and covering 2000-3000 km through the water. ([spraydata.ucsd.edu](http://spraydata.ucsd.edu)).
+"""
+
+# ╔═╡ 0a016d12-de41-45f5-800d-af8f953720e4
+begin
+	url1="https://timesofsandiego.com/wp-content/uploads/2014/06/Spray-Glider.jpg"
+	url2="https://www.whoi.edu/wp-content/uploads/2019/01/GP020002-1-14_506075_510753-1.jpg"
+	url3="https://spraydata.ucsd.edu/assets/img/GS_KE_for_web.png"
+	url4="https://spraydata.ucsd.edu/products/cugn-climatology/plots/66/meanmap/66_meanmap_xz_geov.png"
+	md"""
+	$(Resource(url2,:height => 100))
+	$(Resource(url1,:height => 100))
[…]

### 2024-09-03 v0.2.3/search_index.js

@@ -1,0 +1,3 @@
+var documenterSearchIndex = {"docs":
+[{"location":"examples/#Notebooks","page":"Notebooks","title":"Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"note: Note\nThe static html rendering of the notebooks (this website) lack the interactivity that comes from Running Examples yourself.","category":"page"},{"location":"examples/#List-of-Notebooks","page":"Notebooks","title":"List of Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"The suite of examples includes :","category":"page"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"OceanOPS.jl (➭ code link) : global ocean observing systems\nBuoy_NWP_NOAA.jl (➭ code link) : NOAA station data (a few days)\nBuoy_NWP_NOAA_monthly.jl (➭ code link) : NOAA station data (monthly means) \nMooring_WHOTS.jl (➭ code link) : WHOTS mooring data\nDrifter_GDP.jl (➭ code link) : drifter time series\nDrifter_CloudDrift.jl (➭ code link) : drifter statistics\nFloat_Argo.jl (➭ code link) : Argo profiling float data\nOceanExpedition_CCHDO.jl (➭ code link) : ship CTD and other data\nGlider_Spray.jl (➭ code link) : underwater glider data\nSatelliteAltimetry.jl (➭ code link) : gridded satellite data","category":"page"},{"location":"examples/#More-Notebooks","page":"Notebooks","title":"More Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"For Argo and state estimates, see ArgoData.jl\nFor drifter data simulations, see IndividualDisplacements.jl","category":"page"},{"location":"examples/#Using-Notebooks","page":"Notebooks","title":"Using Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"The examples are most easily run using Pluto.jl. To do it this way, one just needs to copy a code link provided above and paste this URL into the Pluto.jl interface.","category":"page"},{"location":"reference/#User-Interface-(API)","page":"
[…]

### 2024-09-03 ext/OceanRobotsMakieExt.jl
streamline handling of file names in CCHDO

@@ -331,9 +331,9 @@ function plot(x::OceanExpedition;
 
 	fig=Figure(size=size); ax=Axis(fig[1,1],title="$(variable) from cruise $(x.ID)")
 	if variable=="temperature"||variable=="salinity"
-		list1=findall(occursin.(Ref("_ctd.nc"),x.list_files[:,"filename"]))
-		for f in x.list_files[list1,"filename"]
-			ds=CCHDO.read(f)
+		list1=CCHDO.list_CTD_files(x)		
+		for f in list1
+			ds=CCHDO.NCDatasets.Dataset(f)
 			tim=fill(ds["time"][1],ds.dim["pressure"])
 			depth=-ds["pressure"][:]
 			scatter!(tim,depth,color=ds[variable][:],markersize=markersize,colorrange=colorrange)
@@ -346,10 +346,7 @@ function plot(x::OceanExpedition;
 end
 
 function plot_chi!(x;variable="chi_up",colorrange=(-12.0,-10.0),markersize=3)
-	fil0=basename(CCHDO.ancillary_files(x.ID).chipod)
-	ii=findall(occursin.(Ref(fil0),x.list_files[:,"filename"]))[1]
-	fil1=x.list_files[ii,"filename"]
-	ds=CCHDO.read(fil1)
+	ds=CCHDO.open_chipod_file(x)
 
 	time=permutedims(repeat(ds["time"][:],1,ds.dim["pressure"]))
 	pressure=permutedims(repeat(ds["pressure"][:]',ds.dim["station"],1))

### 2024-09-03 src/types.jl

@@ -74,12 +74,10 @@ SeaLevelAnomaly() = SeaLevelAnomaly(:unknown,[],"")
 Base.@kwdef struct OceanExpedition <: AbstractOceanRobotData
     ID::String
     data::Union{Array,Dataset}
-    list_files::DataFrame
+    path::String
 end
 
 OceanExpedition(ID::String)=begin
     path=CCHDO.download(ID)
-    filenames=joinpath.(Ref(path),readdir(path))
-    list1=DataFrames.DataFrame(:filename=>filenames)
-    OceanExpedition(ID,[],list1)
+    OceanExpedition(ID,[],path)
 end

### 2024-09-03 ext/OceanRobotsMakieExt.jl
rename data structure as ShipCruise

@@ -315,17 +315,17 @@ function plot_standard(wmo,arr,spd,T_std,S_std; markersize=2,pol=Any[],size=(900
 end
 
 """
-    plot(x::OceanExpedition; 
+    plot(x::ShipCruise; 
 	markersize=6,pol=Any[],colorrange=(2,20),
 	size=(900,600),variable="temperature")
 
 ```
 using OceanRobots, CairoMakie
-x=OceanExpedition("33RR20160208")
+x=ShipCruise("33RR20160208")
 plot(x)
 ```
 """
-function plot(x::OceanExpedition; 
+function plot(x::ShipCruise; 
 	markersize=6,pol=Any[],colorrange=(2,20),
 	size=(900,600),variable="temperature")
 

### 2024-09-03 src/OceanRobots.jl

@@ -16,6 +16,6 @@ include("gridded_data.jl")
 export cmems_sla, podaac_sla
 
 export NOAAbuoy, NOAAbuoy_monthly, ArgoFloat, SurfaceDrifter, Gliders
-export OceanSite, CloudDrift, SeaLevelAnomaly, OceanExpedition
+export OceanSite, CloudDrift, SeaLevelAnomaly, ShipCruise
 
 end # module

### 2024-09-03 src/types.jl

@@ -71,13 +71,13 @@ end
 
 SeaLevelAnomaly() = SeaLevelAnomaly(:unknown,[],"")
 
-Base.@kwdef struct OceanExpedition <: AbstractOceanRobotData
+Base.@kwdef struct ShipCruise <: AbstractOceanRobotData
     ID::String
     data::Union{Array,Dataset}
     path::String
 end
 
-OceanExpedition(ID::String)=begin
+ShipCruise(ID::String)=begin
     path=CCHDO.download(ID)
-    OceanExpedition(ID,[],path)
+    ShipCruise(ID,[],path)
 end

### 2024-09-03 examples/ShipCruise_CCHDO.jl
update notebook

@@ -4,37 +4,104 @@
 using Markdown
 using InteractiveUtils
 
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
 # ╔═╡ e741dbc2-695b-11ef-1962-5769d79825c0
-using OceanRobots, CairoMakie
+using OceanRobots, CairoMakie, PlutoUI
 
 # ╔═╡ c90d4b04-9810-4736-8f73-bb6ee2c42577
 md"""# CTD profiles from ocean ship expeditions
 
+CCHDO provides access to high quality, global, vessel-based CTD and hydrographic data from GO-SHIP, WOCE, CLIVAR and other repeat hydrography programs. 
+
 !!! note
-    Data displayed here were collected by research vessells. For more information see <https://cchdo.ucsd.edu>
+    For more information see <https://cchdo.ucsd.edu>
 """
 
-# ╔═╡ eab5b722-be6b-4341-b870-5a98cf6a32c3
-#plot(cruise,variable="chi_up",colorrange=(-12,-10))
-
-# ╔═╡ 17b1bef9-719a-4668-a067-c8dabdab9dc2
-md"""## Data and Software"""
+# ╔═╡ 4a1784d6-7850-4c05-b302-013db8966c3a
+@bind ID Select(["33RR20160208","74EQ20151206","33RO20131223"])
 
 # ╔═╡ f5415f1d-0e98-41e3-a6fb-459580141611
-cruise=OceanExpedition("33RR20160208")
[…]

### 2024-09-03 ext/OceanRobotsMakieExt.jl
improve plotting for ShipCruise

@@ -317,20 +317,27 @@ end
 
 """
     plot(x::ShipCruise; 
-	markersize=6,pol=Any[],colorrange=(2,20),
-	size=(900,600),variable="temperature")
+		markersize=6,pol=Any[],colorrange=(2,20),
+		size=(900,600),variable="temperature",apply_log10=false)
 
 ```
 using OceanRobots, CairoMakie
-x=ShipCruise("33RR20160208")
-plot(x)
+cruise=ShipCruise("33RR20160208")
+plot(cruise)
+```
+
+or 
+```
+plot(cruise,variable="chi_up",apply_log10=true,colorrange=(-12,-10))
 ```
 """
 function plot(x::ShipCruise; 
 	markersize=6,pol=Any[],colorrange=(2,20),
-	size=(900,600),variable="temperature")
+	size=(900,600),variable="temperature",apply_log10=false)
 
 	fig=Figure(size=size); ax=Axis(fig[1,1],title="$(variable) from cruise $(x.ID)")
+
+	known_chipod_variables=["chi_up","chi_dn","KT_up","KT_dn"]
 	if variable=="temperature"||variable=="salinity"
 		list1=CCHDO.list_CTD_files(x)		
 		for f in list1
@@ -339,24 +346,30 @@ function plot(x::ShipCruise;
 			depth=-ds["pressure"][:]
 			scatter!(tim,depth,color=ds[variable][:],markersize=markersize,colorrange=colorrange)
 		end
-	elseif variable=="chi_up"||variable=="chi_dn"
-		plot_chi!(x;variable=variable,colorrange=colorrange,markersize=markersize)
+	elseif variable in known_chipod_variables
+		plot_chi!(x;variable=variable,apply_log10=apply_log10,
+			colorrange=colorrange,markersize=markersize)
 	end
 	Colorbar(fig[1,2], colorrange=colorrange, height=Relative(0.65))
 	fig
 end
 
-function plot_chi!(x;variable="chi_up",colorrange=(-12.0,-10.0),markersize=3)
+function plot_chi!(x;variable="chi_up",colorrange=(-12.0,-10.0),apply_log10=true,markersize=3)
 	ds=CCHDO.open_chipod_file(x)
 
 	time=permutedims(repeat(ds["time"][:],1,ds.dim["pressure"]))
[…]

### 2024-09-03 dev/examples/Drifter_GDP.jl
build based on 6dd5e1e

@@ -331,14 +331,14 @@ uuid = "f0e56b4a-5159-44fe-b623-3e5288b988bb"
 version = "2.4.2"
 
 [[deps.ConstructionBase]]
-deps = ["LinearAlgebra"]
-git-tree-sha1 = "a33b7ced222c6165f624a3f2b55945fac5a598d9"
+git-tree-sha1 = "76219f1ed5771adbb096743bff43fb5fdd4c1157"
 uuid = "187b0558-2788-49d3-abe0-74a17ed4e7c9"
-version = "1.5.7"
-weakdeps = ["IntervalSets", "StaticArrays"]
+version = "1.5.8"
+weakdeps = ["IntervalSets", "LinearAlgebra", "StaticArrays"]
 
     [deps.ConstructionBase.extensions]
     ConstructionBaseIntervalSetsExt = "IntervalSets"
+    ConstructionBaseLinearAlgebraExt = "LinearAlgebra"
     ConstructionBaseStaticArraysExt = "StaticArrays"
 
 [[deps.Contour]]
@@ -1153,9 +1153,9 @@ version = "0.5.5"
 
 [[deps.OceanRobots]]
 deps = ["CFTime", "CSV", "DataFrames", "DataStructures", "Dataverse", "Dates", "Downloads", "FTPClient", "Glob", "HTTP", "Interpolations", "JSON3", "LightXML", "NCDatasets", "Printf", "Statistics", "URIs"]
-git-tree-sha1 = "cc465516ec877501c515bf04429cec576e0102f2"
+git-tree-sha1 = "70e15a9c6fe33aaf969f91b986dce3383a94c3c2"
 uuid = "0b51df41-3294-4961-8d23-db645e32016d"
-version = "0.2.2"
+version = "0.2.3"
 
     [deps.OceanRobots.extensions]
     OceanRobotsArgoDataExt = ["ArgoData"]

### 2024-09-03 dev/examples/OceanExpedition_CCHDO.jl

@@ -1,1792 +1,0 @@
-### A Pluto.jl notebook ###
-# v0.19.46
-
-using Markdown
-using InteractiveUtils
-
-# ╔═╡ e741dbc2-695b-11ef-1962-5769d79825c0
-using OceanRobots, CairoMakie
-
-# ╔═╡ c90d4b04-9810-4736-8f73-bb6ee2c42577
-md"""# CTD profiles from ocean ship expeditions
-
-!!! note
-    Data displayed here were collected by research vessells. For more information see <https://cchdo.ucsd.edu>
-"""
-
-# ╔═╡ eab5b722-be6b-4341-b870-5a98cf6a32c3
-#plot(cruise,variable="chi_up",colorrange=(-12,-10))
-
-# ╔═╡ 17b1bef9-719a-4668-a067-c8dabdab9dc2
-md"""## Data and Software"""
-
-# ╔═╡ f5415f1d-0e98-41e3-a6fb-459580141611
-cruise=OceanExpedition("33RR20160208")
-
-# ╔═╡ 19a5cf7c-fa71-435b-bdff-d369658d3260
-plot(cruise,variable="salinity",colorrange=(33.5,35.0))
-
-# ╔═╡ 00000000-0000-0000-0000-000000000001
-PLUTO_PROJECT_TOML_CONTENTS = """
-[deps]
-CairoMakie = "13f3f980-e62b-5c42-98c6-ff1f3baf88f0"
-OceanRobots = "0b51df41-3294-4961-8d23-db645e32016d"
-
-[compat]
-CairoMakie = "~0.12.9"
-OceanRobots = "~0.2.1"
-"""
-
-# ╔═╡ 00000000-0000-0000-0000-000000000002
-PLUTO_MANIFEST_TOML_CONTENTS = """
-# This file is machine-generated - editing it directly is not advised
-
-julia_version = "1.10.4"
-manifest_format = "2.0"
-project_hash = "0bb01b4475c900c10989d79fa18fb64c96d81b58"
-
-[[deps.AbstractFFTs]]
-deps = ["LinearAlgebra"]
-git-tree-sha1 = "d92ad398961a3ed262d8bf04a1a2b8340f915fef"
-uuid = "621f4979-c628-5d54-868e-fcf4e3e8185c"
-version = "1.5.0"
-weakdeps = ["ChainRulesCore", "Test"]
-
[…]

### 2024-09-03 dev/search_index.js

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"examples/#Notebooks","page":"Notebooks","title":"Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"note: Note\nThe static html rendering of the notebooks (this website) lack the interactivity that comes from Running Examples yourself.","category":"page"},{"location":"examples/#List-of-Notebooks","page":"Notebooks","title":"List of Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"The suite of examples includes :","category":"page"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"OceanOPS.jl (➭ code link) : global ocean observing systems\nBuoy_NWP_NOAA.jl (➭ code link) : NOAA station data (a few days)\nBuoy_NWP_NOAA_monthly.jl (➭ code link) : NOAA station data (monthly means) \nMooring_WHOTS.jl (➭ code link) : WHOTS mooring data\nDrifter_GDP.jl (➭ code link) : drifter time series\nDrifter_CloudDrift.jl (➭ code link) : drifter statistics\nFloat_Argo.jl (➭ code link) : Argo profiling float data\nOceanExpedition_CCHDO.jl (➭ code link) : ship CTD and other data\nGlider_Spray.jl (➭ code link) : underwater glider data\nSatelliteAltimetry.jl (➭ code link) : gridded satellite data","category":"page"},{"location":"examples/#More-Notebooks","page":"Notebooks","title":"More Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"For Argo and state estimates, see ArgoData.jl\nFor drifter data simulations, see IndividualDisplacements.jl","category":"page"},{"location":"examples/#Using-Notebooks","page":"Notebooks","title":"Using Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"The examples are most easily run using Pluto.jl. To do it this way, one just needs to copy a code link provided above and paste this URL into the Pluto.jl interface.","category":"page"},{"location":"reference/#User-Interface-(API)","page":"
[…]

### 2024-09-03 examples/ShipCruise_CCHDO.jl
update plot

@@ -47,6 +47,22 @@ Some of these ocean expeditions measure ocean mixing using `chipod` sensors.
 # ╔═╡ 457d85eb-08a8-4304-82a7-0372514b1bec
 @bind va Select(["chi_up","chi_dn","KT_up","KT_dn"])
 
+# ╔═╡ eab5b722-be6b-4341-b870-5a98cf6a32c3
+begin
+	if occursin("chi",va)
+		cr=(-12,-10)
+		lo=true
+	elseif occursin("KT",va)
+		cr=(-6,-3)
+		lo=true
+	else
+		error("unknown variable range")
+	end
+		
+	#chipod_plot(cruise,variable=va,colorrange=cr,apply_log10=lo)
+	plot(cruise,variable=va,colorrange=cr,apply_log10=lo)
+end
+
 # ╔═╡ beed86ef-5e86-45a4-8842-f21f2dcef504
 ds=CCHDO.open_chipod_file(cruise)
 
@@ -74,21 +90,6 @@ function chipod_plot(x;variable="chi_up",colorrange=(-12.0,-10.0),apply_log10=tr
 	Colorbar(fig[1,2], sc, height=Relative(0.65))
 
 	fig
-end
-
-# ╔═╡ eab5b722-be6b-4341-b870-5a98cf6a32c3
-begin
-	if occursin("chi",va)
-		cr=(-12,-10)
-		lo=true
-	elseif occursin("KT",va)
-		cr=(-6,-3)
-		lo=true
-	else
-		error("unknown variable range")
-	end
-		
-	chipod_plot(cruise,variable=va,colorrange=cr,apply_log10=lo)
 end
 
 # ╔═╡ 00000000-0000-0000-0000-000000000001
@@ -1899,6 +1900,6 @@ version = "3.6.0+0"
 # ╟─beed86ef-5e86-45a4-8842-f21f2dcef504
 # ╟─17b1bef9-719a-4668-a067-c8dabdab9dc2
 # ╠═e741dbc2-695b-11ef-1962-5769d79825c0
-# ╠═bc007619-ff00-49c8-a8e4-e2e8a96a0326
+# ╟─bc007619-ff00-49c8-a8e4-e2e8a96a0326
 # ╟─00000000-0000-0000-0000-000000000001
 # ╟─00000000-0000-0000-0000-000000000002

### 2024-09-03 ext/OceanRobotsMakieExt.jl
fix

@@ -371,7 +371,7 @@ function plot_chi!(x;variable="chi_up",colorrange=(-12.0,-10.0),apply_log10=true
 	ax=current_axis()
 	ax.title="variable = $(variable) (in $u$l) ; cruise = $(x.ID)"
 
-	scatter!(a,b,color=c,markersize=3,colorrange=colorrange)
+	scatter!(a,b,color=c,markersize=markersize,colorrange=colorrange)
 end
 
 """

### 2024-09-03 dev/search_index.js
build based on 2deb6a6

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"examples/#Notebooks","page":"Notebooks","title":"Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"note: Note\nThe static html rendering of the notebooks (this website) lack the interactivity that comes from Running Examples yourself.","category":"page"},{"location":"examples/#Included-Notebooks","page":"Notebooks","title":"Included Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"OceanOPS.jl (➭ code link) : global ocean observing systems\nShipCruise_CCHDO.jl (➭ code link) : ship CTD and other data\nFloat_Argo.jl (➭ code link) : Argo profiling float data\nDrifter_GDP.jl (➭ code link) : drifter time series\nDrifter_CloudDrift.jl (➭ code link) : drifter statistics\nGlider_Spray.jl (➭ code link) : underwater glider data\nBuoy_NWP_NOAA.jl (➭ code link) : NOAA station data (a few days)\nBuoy_NWP_NOAA_monthly.jl (➭ code link) : NOAA station data (monthly means) \nMooring_WHOTS.jl (➭ code link) : WHOTS mooring data\nSatelliteAltimetry.jl (➭ code link) : gridded satellite data","category":"page"},{"location":"examples/#More-Notebooks","page":"Notebooks","title":"More Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"For Argo and state estimates, see ArgoData.jl\nFor drifter data simulations, see IndividualDisplacements.jl","category":"page"},{"location":"examples/#Using-Notebooks","page":"Notebooks","title":"Using Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"The examples are most easily run using Pluto.jl. To do it this way, one just needs to copy a code link provided above and paste this URL into the Pluto.jl interface.","category":"page"},{"location":"reference/#User-Interface-(API)","page":"User Interface","title":"User Interface (API)","text":"","category":"section"},{"location":"reference/","page":"User In
[…]

### 2024-09-03 v0.2.4/examples/Drifter_CloudDrift.jl
build based on 130a0d3

@@ -1,0 +1,1896 @@
+### A Pluto.jl notebook ###
+# v0.19.46
+
+using Markdown
+using InteractiveUtils
+
+# ╔═╡ bf29d9b6-be57-11ec-2b83-87ce1f770075
+using CairoMakie, OceanRobots, FFTW, PlutoUI
+
+# ╔═╡ 97537903-fb3b-4837-9e7c-461cb9e4ef5e
+md"""# Transpose _Cloud-Drift_ workflow into Julia
+
+See <https://github.com/Cloud-Drift/earthcube-meeting-2022> for context and detail.
+"""
+
+# ╔═╡ c56e7f24-7be8-4209-8fc9-843cb674fd6e
+TableOfContents()
+
+# ╔═╡ f3c351c7-3fba-4ee8-8522-80fd0e8921af
+md"""## Visualize Data"""
+
+# ╔═╡ 05b32012-927d-42b4-8a18-fdfcb051a3fd
+md"""## Per Trajectory Statistics"""
+
+
+# ╔═╡ 89c82c13-9221-48b8-9138-79b91603d7e6
+md"""## Appendix
+
+Packages, grid, functions used in the notebook are defined here.
+"""
+
+# ╔═╡ d0362426-0609-4fcf-a888-77892db9b7e7
+begin
+    GDP_CD=read(CloudDrift(),"")
+    df=GDP_CD.data.main
+    df_subset=GDP_CD.data.subset
+	"Done reading data"
+end
+
+# ╔═╡ 60479536-8238-4077-bdcd-776e07330621
+let
+	ii=findall(isfinite.(df_subset.longitude.*df_subset.latitude))	
+	scatter(df_subset.longitude[ii], df_subset.latitude[ii], markersize=2,
+		color=sqrt.(df_subset.ve.^2+df_subset.vn.^2), colorrange=(0,2.5), colormap=:speed)
+end
+
+# ╔═╡ d4af67e7-2308-4135-929e-c7fc6572d6c7
+heatmap(GDP_CD.data.grid.lon,GDP_CD.data.grid.lat,GDP_CD.data.ve)
+
+# ╔═╡ a25027b5-5b0e-4190-b4b6-987f4e16ccd8
+begin
+	gdf2=GDP_CloudDrift.groupby(df,:ID)
+	df2=GDP_CloudDrift.trajectory_stats(gdf2)
+	trajectory_periodogram(cv) = 1/24 *abs.(fft(cv[:])).^2
[…]

### 2024-09-03 v0.2.4/examples/Float_Argo.jl

@@ -1,0 +1,2107 @@
+### A Pluto.jl notebook ###
+# v0.19.46
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
+# ╔═╡ 8539e67f-6361-409a-9dbe-e8dcb2c7e10d
+begin
+	using OceanRobots, ArgoData, CairoMakie, PlutoUI, PrettyTables, MeshArrays
+	"Done with packages"
+end
+
+# ╔═╡ dc017980-cde3-49bc-a5e0-44be9bb08cec
+begin
+	using Shapefile, DataDeps
+	pol_file=demo.download_polygons("ne_110m_admin_0_countries.shp")
+	pol=MeshArrays.read_polygons(pol_file)
+	"Done with country boundaries"
+end
+
+# ╔═╡ 89647c4e-e568-4d3a-af57-bcc541744e38
+md"""# Argo Floats
+
+The standard Argo platform is a profiling float that drifts at 1000m depth. They come back to the surface every ten days, just after collecting vertocal profiles of temperature and salinity, and transmit their data via satellite. 
+
+!!! tip
+    For more information about the international Argo program please refer to, for example, <https://argo.ucsd.edu> or <https://biogeochemical-argo.org>.
+"""
+
+# ╔═╡ 09a2aa6e-16bc-4582-9d5f-c50432e3f0ca
+begin
[…]

### 2024-09-03 v0.2.4/examples/ShipCruise_CCHDO.jl

@@ -1,0 +1,1792 @@
+### A Pluto.jl notebook ###
+# v0.19.46
+
+using Markdown
+using InteractiveUtils
+
+# ╔═╡ e741dbc2-695b-11ef-1962-5769d79825c0
+using OceanRobots, CairoMakie
+
+# ╔═╡ c90d4b04-9810-4736-8f73-bb6ee2c42577
+md"""# CTD profiles from ocean ship expeditions
+
+!!! note
+    Data displayed here were collected by research vessells. For more information see <https://cchdo.ucsd.edu>
+"""
+
+# ╔═╡ eab5b722-be6b-4341-b870-5a98cf6a32c3
+#plot(cruise,variable="chi_up",colorrange=(-12,-10))
+
+# ╔═╡ 17b1bef9-719a-4668-a067-c8dabdab9dc2
+md"""## Data and Software"""
+
+# ╔═╡ f5415f1d-0e98-41e3-a6fb-459580141611
+cruise=OceanExpedition("33RR20160208")
+
+# ╔═╡ 19a5cf7c-fa71-435b-bdff-d369658d3260
+plot(cruise,variable="salinity",colorrange=(33.5,35.0))
+
+# ╔═╡ 00000000-0000-0000-0000-000000000001
+PLUTO_PROJECT_TOML_CONTENTS = """
+[deps]
+CairoMakie = "13f3f980-e62b-5c42-98c6-ff1f3baf88f0"
+OceanRobots = "0b51df41-3294-4961-8d23-db645e32016d"
+
+[compat]
+CairoMakie = "~0.12.9"
+OceanRobots = "~0.2.1"
+"""
+
+# ╔═╡ 00000000-0000-0000-0000-000000000002
+PLUTO_MANIFEST_TOML_CONTENTS = """
+# This file is machine-generated - editing it directly is not advised
+
+julia_version = "1.10.4"
+manifest_format = "2.0"
+project_hash = "0bb01b4475c900c10989d79fa18fb64c96d81b58"
+
+[[deps.AbstractFFTs]]
+deps = ["LinearAlgebra"]
+git-tree-sha1 = "d92ad398961a3ed262d8bf04a1a2b8340f915fef"
+uuid = "621f4979-c628-5d54-868e-fcf4e3e8185c"
+version = "1.5.0"
+weakdeps = ["ChainRulesCore", "Test"]
+
[…]

### 2024-09-03 v0.2.4/search_index.js

@@ -1,0 +1,3 @@
+var documenterSearchIndex = {"docs":
+[{"location":"examples/#Notebooks","page":"Notebooks","title":"Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"note: Note\nThe static html rendering of the notebooks (this website) lack the interactivity that comes from Running Examples yourself.","category":"page"},{"location":"examples/#Included-Notebooks","page":"Notebooks","title":"Included Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"OceanOPS.jl (➭ code link) : global ocean observing systems\nShipCruise_CCHDO.jl (➭ code link) : ship CTD and other data\nFloat_Argo.jl (➭ code link) : Argo profiling float data\nDrifter_GDP.jl (➭ code link) : drifter time series\nDrifter_CloudDrift.jl (➭ code link) : drifter statistics\nGlider_Spray.jl (➭ code link) : underwater glider data\nBuoy_NWP_NOAA.jl (➭ code link) : NOAA station data (a few days)\nBuoy_NWP_NOAA_monthly.jl (➭ code link) : NOAA station data (monthly means) \nMooring_WHOTS.jl (➭ code link) : WHOTS mooring data\nSatelliteAltimetry.jl (➭ code link) : gridded satellite data","category":"page"},{"location":"examples/#More-Notebooks","page":"Notebooks","title":"More Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"For Argo and state estimates, see ArgoData.jl\nFor drifter data simulations, see IndividualDisplacements.jl","category":"page"},{"location":"examples/#Using-Notebooks","page":"Notebooks","title":"Using Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"The examples are most easily run using Pluto.jl. To do it this way, one just needs to copy a code link provided above and paste this URL into the Pluto.jl interface.","category":"page"},{"location":"reference/#User-Interface-(API)","page":"User Interface","title":"User Interface (API)","text":"","category":"section"},{"location":"reference/","page":"User In
[…]

### 2024-09-03 examples/ShipCruise_CCHDO.jl
update & improve CCHDO notebook

@@ -18,12 +18,15 @@ end
 using OceanRobots, CairoMakie, PlutoUI
 
 # ╔═╡ c90d4b04-9810-4736-8f73-bb6ee2c42577
-md"""# CTD profiles from ocean ship expeditions
+md"""# CTD profiles from oceanographic expeditions
 
-CCHDO provides access to high quality, global, vessel-based CTD and hydrographic data from GO-SHIP, WOCE, CLIVAR and other repeat hydrography programs. 
+CCHDO provides access to high quality, global, ship-based CTD (Conductivity-Temperature-Depth) and hydrographic data from GO-SHIP, WOCE, CLIVAR and other repeat hydrography programs. 
 
 !!! note
     For more information see <https://cchdo.ucsd.edu>
+
+### Select Cruise
+
 """
 
 # ╔═╡ 4a1784d6-7850-4c05-b302-013db8966c3a
@@ -32,8 +35,29 @@ CCHDO provides access to high quality, global, vessel-based CTD and hydrographic
 # ╔═╡ f5415f1d-0e98-41e3-a6fb-459580141611
 cruise=ShipCruise(ID)
 
+# ╔═╡ fa2c9be1-1198-4852-b7b1-623e42f5c871
+begin
+	vari_bind = @bind vari Select(["temperature","salinity"],default="salinity")
+	cmin_bind = @bind cmin TextField(default="33.5")
+	cmax_bind = @bind cmax TextField(default="35.0")
+	md"""
+!!! note
+	Selecting a new data set will start by downloading it, if needed, which may take a little while.
+
+### Plot One Variable
+
+- variable : $(vari_bind)
+- color range minimum	: $(cmin_bind)
+- color range maximum	: $(cmax_bind)
+	"""
+end
+	
+
 # ╔═╡ 19a5cf7c-fa71-435b-bdff-d369658d3260
-plot(cruise,variable="salinity",colorrange=(33.5,35.0))
+begin
+	crng=(parse(Float64,cmin),parse(Float64,cmax))
+	plot(cruise,variable=vari,colorrange=crng)
+end
 
[…]

### 2024-09-03 dev/examples/ShipCruise_CCHDO.jl
build based on 2b16a11

@@ -4,37 +4,128 @@
 using Markdown
 using InteractiveUtils
 
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
 # ╔═╡ e741dbc2-695b-11ef-1962-5769d79825c0
-using OceanRobots, CairoMakie
+using OceanRobots, CairoMakie, PlutoUI
 
 # ╔═╡ c90d4b04-9810-4736-8f73-bb6ee2c42577
-md"""# CTD profiles from ocean ship expeditions
+md"""# CTD profiles from oceanographic expeditions
+
+CCHDO provides access to high quality, global, ship-based CTD (Conductivity-Temperature-Depth) and hydrographic data from GO-SHIP, WOCE, CLIVAR and other repeat hydrography programs. 
 
 !!! note
-    Data displayed here were collected by research vessells. For more information see <https://cchdo.ucsd.edu>
+    For more information see <https://cchdo.ucsd.edu>
+
+### Select Cruise
+
 """
 
-# ╔═╡ eab5b722-be6b-4341-b870-5a98cf6a32c3
-#plot(cruise,variable="chi_up",colorrange=(-12,-10))
-
-# ╔═╡ 17b1bef9-719a-4668-a067-c8dabdab9dc2
-md"""## Data and Software"""
+# ╔═╡ 4a1784d6-7850-4c05-b302-013db8966c3a
+@bind ID Select(["33RR20160208","74EQ20151206","33RO20131223"])
 
[…]

### 2024-09-05 dev/search_index.js
build based on 3ffcc22

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"examples/#Notebooks","page":"Notebooks","title":"Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"note: Note\nThe static html rendering of the notebooks (this website) lack the interactivity that comes from Running Examples yourself.","category":"page"},{"location":"examples/#Included-Notebooks","page":"Notebooks","title":"Included Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"OceanOPS.jl (➭ code link) : global ocean observing systems\nShipCruise_CCHDO.jl (➭ code link) : ship CTD and other data\nFloat_Argo.jl (➭ code link) : Argo profiling float data\nDrifter_GDP.jl (➭ code link) : drifter time series\nDrifter_CloudDrift.jl (➭ code link) : drifter statistics\nGlider_Spray.jl (➭ code link) : underwater glider data\nBuoy_NWP_NOAA.jl (➭ code link) : NOAA station data (a few days)\nBuoy_NWP_NOAA_monthly.jl (➭ code link) : NOAA station data (monthly means) \nMooring_WHOTS.jl (➭ code link) : WHOTS mooring data\nSatelliteAltimetry.jl (➭ code link) : gridded satellite data","category":"page"},{"location":"examples/#More-Notebooks","page":"Notebooks","title":"More Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"For Argo and state estimates, see ArgoData.jl\nFor drifter data simulations, see IndividualDisplacements.jl","category":"page"},{"location":"examples/#Using-Notebooks","page":"Notebooks","title":"Using Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"The examples are most easily run using Pluto.jl. To do it this way, one just needs to copy a code link provided above and paste this URL into the Pluto.jl interface.","category":"page"},{"location":"reference/#User-Interface-(API)","page":"User Interface","title":"User Interface (API)","text":"","category":"section"},{"location":"reference/","page":"User In
[…]

### 2024-09-05 paper/header.tex
header, plots

% **************GENERATED FILE, DO NOT EDIT**************

\title{Digital Twins for Ocean Robots}

\author[1]{Gaël Forget}
\affil[1]{Earth, Atmospheric and Planetary Sciences, Massachusetts Institute of Technology, 77 Massachusetts Avenue, Cambridge, 02139, MA, USA}

\keywords{Julia, OptimizatOcean, Climate, Robot, Observation, Platform, Sensor, Drifter, Buoy, Profiler, Satellite, Modeling, Artificial Intelligence, Data Assimilation, Parameter Inference, Climatology, Geospatial, Statistics}

\hypersetup{
pdftitle = {Digital Twins for Ocean Robots},
pdfsubject = {JuliaCon 2022 Proceedings},
pdfauthor = {Gaël Forget},
pdfkeywords = {Julia, OptimizatOcean, Climate, Robot, Observation, Platform, Sensor, Drifter, Buoy, Profiler, Satellite, Modeling, Artificial Intelligence, Data Assimilation, Parameter Inference, Climatology, Geospatial, Statistics},
}

### 2024-09-06 dev/search_index.js
build based on c0da030

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"examples/#Tutorial-Notebooks","page":"Notebooks","title":"Tutorial Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"note: Note\nThe version of the notebooks found in the online docs is static html rendering (this website).\nThe version found in the src folder is the underlying code of the notebooks (.jl files).\nTo run the notebooks interactively see How-To section.","category":"page"},{"location":"examples/#Included-Notebooks","page":"Notebooks","title":"Included Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"OceanOPS.jl (➭ code link) : global ocean observing systems\nShipCruise_CCHDO.jl (➭ code link) : ship CTD and other data\nFloat_Argo.jl (➭ code link) : Argo profiling float data\nDrifter_GDP.jl (➭ code link) : drifter time series\nDrifter_CloudDrift.jl (➭ code link) : drifter statistics\nGlider_Spray.jl (➭ code link) : underwater glider data\nBuoy_NWP_NOAA.jl (➭ code link) : NOAA station data (a few days)\nBuoy_NWP_NOAA_monthly.jl (➭ code link) : NOAA station data (monthly means) \nMooring_WHOTS.jl (➭ code link) : WHOTS mooring data","category":"page"},{"location":"examples/#More-Notebooks","page":"Notebooks","title":"More Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"For Argo and state estimates, see ArgoData.jl\nFor simulations of drifter data, see IndividualDisplacements.jl\nSatelliteAltimetry.jl (➭ code link) : gridded satellite data","category":"page"},{"location":"examples/#How-To","page":"Notebooks","title":"How-To","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"To install OceanRobots.jl in julia proceed as usual via the package manager (using Pkg; Pkg.add(OceanRobots)).","category":"page"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"To run a notebook interactively (.jl files) you want to use Pluto.jl. For example, copy and paste one of the a
[…]

### 2024-09-06 v0.2.5/examples/Buoy_NWP_NOAA_monthly.jl
build based on a0328e1

@@ -1,0 +1,1907 @@
+### A Pluto.jl notebook ###
+# v0.19.46
+
+using Markdown
+using InteractiveUtils
+
+# ╔═╡ 920b7a98-8478-4ad7-8897-8e5d92737199
+begin
+	using PlutoUI, CairoMakie, OceanRobots
+	"Done with packages"
+end
+
+# ╔═╡ 91db1379-9f47-4982-9716-f755451f819f
+begin
+img_url="https://nosc.noaa.gov/OSC/images/Kukui_and_NOAA_buoy_1.177308.JPG"
+	
+md"""# NOAA Buoys / Monthly Means"""
+end
+
+# ╔═╡ 2f87a4a9-ad5d-46ff-961b-028de3a27a23
+PlutoUI.TableOfContents()
+
+# ╔═╡ d106d4c1-1d2e-40b3-8958-901ea437a524
+begin
+md"""In this notebook, you will compute climatologies and distributions from NOAA buoy data.
+
+$(Resource(img_url,:width => 250))
+
+!!! note 
+	For more information about NOAA Buoys, visit <https://www.ndbc.noaa.gov/> and links below.
+
+## Visualize Data	
+"""
+end
+
+# ╔═╡ 502dde03-9ce3-4e15-bfc4-854c87a60026
+md"""## Data Summary
+
+Plot below shows:
+
+- top left: the full distribution of 25 year temperatue changes, using all individual months and years, is shown in the top left corner.
+- top right: averaged month by month, the 25 year change in temperature is positive for each month -- between +2 and +4 degrees, approximately.
+- bottom: the mean seasonal cycle in the ~1990s (blue) and ~2010s (orange). Range is ~ 25 degree in both cases. Shift between the curves is what's shown in top panel.
+"""
+
+# ╔═╡ 34a9a048-da3e-11ec-2017-b7b762895d86
+begin
+	ID=44013
+    buoy=read(NOAAbuoy_monthly(),ID)
+end
+
+# ╔═╡ 051ea6ce-a699-4a08-a4cf-214875bd3ca7
+plot(buoy;option=:demo)
+
[…]

### 2024-09-06 v0.2.5/examples/Drifter_GDP.jl

@@ -1,0 +1,1910 @@
+### A Pluto.jl notebook ###
+# v0.19.46
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
+# ╔═╡ d61376ca-76f2-11ec-0393-83d9b38831ca
+begin
+	using OceanRobots, PlutoUI, CairoMakie
+	"Done with packages"
+end
+
+# ╔═╡ e6d47534-3bdb-401f-8758-12ebce4232f6
+TableOfContents()
+
+# ╔═╡ 84964782-cdd1-4773-a134-04d486e69856
+md"""# Surface Drifters
+
+Here we learn to download, read, and plot one hourly drifter data file from [NOAA webpage](https://www.aoml.noaa.gov/ftp/pub/phod/lumpkin/hourly/v2.00/netcdf/) or its [ftp server](ftp://ftp.aoml.noaa.gov/pub/phod/lumpkin/hourly/v2.00/netcdf/). 
+
+!!! note
+    See [global drifter website](https://www.aoml.noaa.gov/phod/gdp/hourly_data.php) for more information about this data set.
+"""
+
+# ╔═╡ 568d54ae-19a6-4ff4-ae0b-e131693029e5
+begin
+	url0="https://www.aoml.noaa.gov/wp-content/uploads/2020/12/GDP-map.jpg"
[…]

### 2024-09-06 v0.2.5/examples/Mooring_WHOTS.jl

@@ -1,0 +1,1909 @@
+### A Pluto.jl notebook ###
+# v0.19.46
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
+# ╔═╡ 5fc8cc85-7bd4-4fea-8c6f-01dabee6eb5f
+begin
+	using OceanRobots, CairoMakie, PlutoUI
+	"Done with packages"
+end
+
+# ╔═╡ 538ddc08-85bd-426b-92bc-f5dd78d38d5d
+TableOfContents()
+
+# ╔═╡ 720e1461-81b9-42b6-88be-0115a17268c0
+md"""# WHOTS mooring
+
+Here we plot time series from the [WHOTS mooring](http://www.soest.hawaii.edu/whots/wh_data.html) which measures both Ocean and Atmosphere variables. This is one of the long time series available to study Climate. See <http://www.oceansites.org/> for more data like this.
+"""
+
+# ╔═╡ e7dc453e-3bf2-4289-b55d-66eab3636d7b
+begin
+	url0="https://insideclimatenews.org/wp-content/uploads/2020/07/ohcean-mooring_noaa.jpg"
+	url1="https://aco-ssds.soest.hawaii.edu/ALOHA/img/slideshow3.jpg"
[…]

### 2024-09-06 v0.2.5/examples/OceanOPS.jl

@@ -1,0 +1,2108 @@
+### A Pluto.jl notebook ###
+# v0.19.46
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
+# ╔═╡ ccf98691-9386-41b9-a957-3cdeba51312b
+using OceanRobots, CairoMakie, PlutoUI, MeshArrays
+
+# ╔═╡ 30277358-0a8d-437e-9d2e-ebc7c307db31
+using Shapefile, GeoJSON, DataDeps, PrettyTables, Proj
+
+# ╔═╡ 5fa93c17-0a01-44c6-8679-d712c786907a
+md"""# OceanOPS : Global Ocean Metadata
+
+Source : <https://www.ocean-ops.org/board>, <https://www.ocean-ops.org/share/>
+
+## Visualize Data Cover
+"""
+
+# ╔═╡ 31fe91d7-dea2-49e3-902b-31aa62075986
+TableOfContents()
+
+# ╔═╡ 1042f70c-4337-4bf2-b533-edf27a422365
+md"""## Select a Platform Type
+
+Each color represents one type of observing platform.
+"""
+
+# ╔═╡ 596bce95-e13f-4439-858f-e944834c0924
+begin
+	bind_nam = @bind nam Select([:Argo,:Drifter])
+	md"""## Explore Platform Metadata
+
+	Here you can select a data set and then a platform. Meta-data from that platform is displayed as a result.
+	
+	Data set : $(bind_nam)
[…]

### 2024-09-06 v0.2.5/examples/SatelliteAltimetry.jl

@@ -1,0 +1,2069 @@
+### A Pluto.jl notebook ###
+# v0.19.46
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
+# ╔═╡ a8e0b727-a416-4aad-b660-69e5470c7e9e
+begin
+	using OceanRobots, CairoMakie, Dataverse, ArchGDAL, PlutoUI
+	OceanRobotsMakieExt=Base.get_extension(OceanRobots, :OceanRobotsMakieExt)
+	"Done with Julia packages"
+end
+
+# ╔═╡ 71e87ed3-5a9f-49aa-99af-cf144501c678
+md"""# Regional Sea Level
+
+Visualize dynamic sea level anomaly (colors) and ocean bathymetry/topography (contours) in the region of the Azores as a function of space and time. 
+
+!!! tip
+    Choose between two data sets (sources: NASA PODAAC, ESA CMEMS), select time, or generate animation.
+"""
+
+# ╔═╡ a58cc4b4-7023-4dcf-a5f4-6366be8047a3
+TableOfContents()
+
+# ╔═╡ 62e0b8a9-0025-4ce7-9538-b6114d97b762
+md"""## Visualize Data
+
+- Color shading is sea level anomaly from a gridded data product based on satellite measurement (altimetry).
[…]

### 2024-09-06 v0.2.5/examples/ShipCruise_CCHDO.jl

@@ -1,0 +1,1931 @@
+### A Pluto.jl notebook ###
+# v0.19.46
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
+# ╔═╡ e741dbc2-695b-11ef-1962-5769d79825c0
+using OceanRobots, CairoMakie, PlutoUI
+
+# ╔═╡ c90d4b04-9810-4736-8f73-bb6ee2c42577
+md"""# CTD profiles from oceanographic expeditions
+
+CCHDO provides access to high quality, global, ship-based CTD (Conductivity-Temperature-Depth) and hydrographic data from GO-SHIP, WOCE, CLIVAR and other repeat hydrography programs. 
+
+!!! note
+    For more information see <https://cchdo.ucsd.edu>
+
+### Select Cruise
+
+"""
+
+# ╔═╡ 4a1784d6-7850-4c05-b302-013db8966c3a
+@bind ID Select(["33RR20160208","74EQ20151206","33RO20131223"])
+
+# ╔═╡ f5415f1d-0e98-41e3-a6fb-459580141611
+cruise=ShipCruise(ID)
+
+# ╔═╡ fa2c9be1-1198-4852-b7b1-623e42f5c871
+begin
+	vari_bind = @bind vari Select(["temperature","salinity"],default="salinity")
+	cmin_bind = @bind cmin TextField(default="33.5")
+	cmax_bind = @bind cmax TextField(default="35.0")
[…]

### 2024-09-06 v0.2.5/search_index.js

@@ -1,0 +1,3 @@
+var documenterSearchIndex = {"docs":
+[{"location":"examples/#Tutorial-Notebooks","page":"Notebooks","title":"Tutorial Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"note: Note\nThe version of the notebooks found in the online docs is static html rendering (this website).\nThe version found in the src folder is the underlying code of the notebooks (.jl files).\nTo run the notebooks interactively see How-To section.","category":"page"},{"location":"examples/#Included-Notebooks","page":"Notebooks","title":"Included Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"OceanOPS.html (➭ code link) : global ocean observing systems\nShipCruise_CCHDO.html (➭ code link) : ship CTD and other data\nFloat_Argo.html (➭ code link) : Argo profiling float data\nDrifter_GDP.html (➭ code link) : drifter time series\nDrifter_CloudDrift.html (➭ code link) : drifter statistics\nGlider_Spray.html (➭ code link) : underwater glider data\nBuoy_NWP_NOAA.html (➭ code link) : NOAA station data (a few days)\nBuoy_NWP_NOAA_monthly.html (➭ code link) : NOAA station data (monthly means) \nMooring_WHOTS.html (➭ code link) : WHOTS mooring data","category":"page"},{"location":"examples/#More-Notebooks","page":"Notebooks","title":"More Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"For Argo and state estimates, see ArgoData.jl\nFor simulations of drifter data, see IndividualDisplacements.jl\nSatelliteAltimetry.html (➭ code link) : gridded satellite data","category":"page"},{"location":"examples/#How-To","page":"Notebooks","title":"How-To","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"To install OceanRobots.jl in julia proceed as usual via the package manager (using Pkg; Pkg.add(OceanRobots)).","category":"page"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"To run a notebook interactively (.jl files) you want to use Pluto.jl. For example, copy and paste on
[…]

### 2024-09-07 examples/Drifter_GDP.jl
update notebook deps

@@ -772,18 +772,20 @@ weakdeps = ["Unitful"]
 
 [[deps.IntervalArithmetic]]
 deps = ["CRlibm_jll", "MacroTools", "RoundingEmulator"]
-git-tree-sha1 = "433b0bb201cd76cb087b017e49244f10394ebe9c"
+git-tree-sha1 = "01fa84a20be8c7c867edf3b9ef33ac15f4089c1a"
 uuid = "d1acc4aa-44c8-5952-acd4-ba5d80a2a253"
-version = "0.22.14"
+version = "0.22.15"
 
     [deps.IntervalArithmetic.extensions]
     IntervalArithmeticDiffRulesExt = "DiffRules"
     IntervalArithmeticForwardDiffExt = "ForwardDiff"
     IntervalArithmeticRecipesBaseExt = "RecipesBase"
+    IntervalArithmeticsIntervalSetsExt = "IntervalSets"
 
     [deps.IntervalArithmetic.weakdeps]
     DiffRules = "b552c78f-8df3-52c6-915a-8e097449b14b"
     ForwardDiff = "f6369f11-7733-5829-9624-2563aa707210"
+    IntervalSets = "8197267c-284f-5f27-9208-e0e47529a953"
     RecipesBase = "3cdcf5f2-1ef4-517c-9805-6587b60abb01"
 
 [[deps.IntervalSets]]
@@ -1153,9 +1155,9 @@ version = "0.5.5"
 
 [[deps.OceanRobots]]
 deps = ["CFTime", "CSV", "DataFrames", "DataStructures", "Dataverse", "Dates", "Downloads", "FTPClient", "Glob", "HTTP", "Interpolations", "JSON3", "LightXML", "NCDatasets", "Printf", "Statistics", "URIs"]
-git-tree-sha1 = "70e15a9c6fe33aaf969f91b986dce3383a94c3c2"
+git-tree-sha1 = "9d3415e0de6d97ea5854d1bdc55e57f28e609b67"
 uuid = "0b51df41-3294-4961-8d23-db645e32016d"
-version = "0.2.3"
+version = "0.2.5"
 
     [deps.OceanRobots.extensions]
     OceanRobotsArgoDataExt = ["ArgoData"]
@@ -1216,9 +1218,9 @@ version = "1.4.3"
 
 [[deps.OpenSSL_jll]]
[…]

### 2024-09-07 dev/examples/Buoy_NWP_NOAA.jl
build based on dec618a

@@ -367,14 +367,14 @@ uuid = "f0e56b4a-5159-44fe-b623-3e5288b988bb"
 version = "2.4.2"
 
 [[deps.ConstructionBase]]
-deps = ["LinearAlgebra"]
-git-tree-sha1 = "a33b7ced222c6165f624a3f2b55945fac5a598d9"
+git-tree-sha1 = "76219f1ed5771adbb096743bff43fb5fdd4c1157"
 uuid = "187b0558-2788-49d3-abe0-74a17ed4e7c9"
-version = "1.5.7"
-weakdeps = ["IntervalSets", "StaticArrays"]
+version = "1.5.8"
+weakdeps = ["IntervalSets", "LinearAlgebra", "StaticArrays"]
 
     [deps.ConstructionBase.extensions]
     ConstructionBaseIntervalSetsExt = "IntervalSets"
+    ConstructionBaseLinearAlgebraExt = "LinearAlgebra"
     ConstructionBaseStaticArraysExt = "StaticArrays"
 
 [[deps.Contour]]
@@ -820,18 +820,20 @@ weakdeps = ["Unitful"]
 
 [[deps.IntervalArithmetic]]
 deps = ["CRlibm_jll", "MacroTools", "RoundingEmulator"]
-git-tree-sha1 = "433b0bb201cd76cb087b017e49244f10394ebe9c"
+git-tree-sha1 = "01fa84a20be8c7c867edf3b9ef33ac15f4089c1a"
 uuid = "d1acc4aa-44c8-5952-acd4-ba5d80a2a253"
-version = "0.22.14"
+version = "0.22.15"
 
     [deps.IntervalArithmetic.extensions]
     IntervalArithmeticDiffRulesExt = "DiffRules"
     IntervalArithmeticForwardDiffExt = "ForwardDiff"
     IntervalArithmeticRecipesBaseExt = "RecipesBase"
+    IntervalArithmeticsIntervalSetsExt = "IntervalSets"
 
     [deps.IntervalArithmetic.weakdeps]
     DiffRules = "b552c78f-8df3-52c6-915a-8e097449b14b"
     ForwardDiff = "f6369f11-7733-5829-9624-2563aa707210"
+    IntervalSets = "8197267c-284f-5f27-9208-e0e47529a953"
     RecipesBase = "3cdcf5f2-1ef4-517c-9805-6587b60abb01"
 
[…]

### 2024-09-07 dev/examples/Buoy_NWP_NOAA_monthly.jl

@@ -331,14 +331,14 @@ uuid = "f0e56b4a-5159-44fe-b623-3e5288b988bb"
 version = "2.4.2"
 
 [[deps.ConstructionBase]]
-deps = ["LinearAlgebra"]
-git-tree-sha1 = "a33b7ced222c6165f624a3f2b55945fac5a598d9"
+git-tree-sha1 = "76219f1ed5771adbb096743bff43fb5fdd4c1157"
 uuid = "187b0558-2788-49d3-abe0-74a17ed4e7c9"
-version = "1.5.7"
-weakdeps = ["IntervalSets", "StaticArrays"]
+version = "1.5.8"
+weakdeps = ["IntervalSets", "LinearAlgebra", "StaticArrays"]
 
     [deps.ConstructionBase.extensions]
     ConstructionBaseIntervalSetsExt = "IntervalSets"
+    ConstructionBaseLinearAlgebraExt = "LinearAlgebra"
     ConstructionBaseStaticArraysExt = "StaticArrays"
 
 [[deps.Contour]]
@@ -772,18 +772,20 @@ weakdeps = ["Unitful"]
 
 [[deps.IntervalArithmetic]]
 deps = ["CRlibm_jll", "MacroTools", "RoundingEmulator"]
-git-tree-sha1 = "433b0bb201cd76cb087b017e49244f10394ebe9c"
+git-tree-sha1 = "01fa84a20be8c7c867edf3b9ef33ac15f4089c1a"
 uuid = "d1acc4aa-44c8-5952-acd4-ba5d80a2a253"
-version = "0.22.14"
+version = "0.22.15"
 
     [deps.IntervalArithmetic.extensions]
     IntervalArithmeticDiffRulesExt = "DiffRules"
     IntervalArithmeticForwardDiffExt = "ForwardDiff"
     IntervalArithmeticRecipesBaseExt = "RecipesBase"
+    IntervalArithmeticsIntervalSetsExt = "IntervalSets"
 
     [deps.IntervalArithmetic.weakdeps]
     DiffRules = "b552c78f-8df3-52c6-915a-8e097449b14b"
     ForwardDiff = "f6369f11-7733-5829-9624-2563aa707210"
+    IntervalSets = "8197267c-284f-5f27-9208-e0e47529a953"
     RecipesBase = "3cdcf5f2-1ef4-517c-9805-6587b60abb01"
 
[…]

### 2024-09-07 dev/examples/Mooring_WHOTS.jl

@@ -334,14 +334,14 @@ uuid = "f0e56b4a-5159-44fe-b623-3e5288b988bb"
 version = "2.4.2"
 
 [[deps.ConstructionBase]]
-deps = ["LinearAlgebra"]
-git-tree-sha1 = "a33b7ced222c6165f624a3f2b55945fac5a598d9"
+git-tree-sha1 = "76219f1ed5771adbb096743bff43fb5fdd4c1157"
 uuid = "187b0558-2788-49d3-abe0-74a17ed4e7c9"
-version = "1.5.7"
-weakdeps = ["IntervalSets", "StaticArrays"]
+version = "1.5.8"
+weakdeps = ["IntervalSets", "LinearAlgebra", "StaticArrays"]
 
     [deps.ConstructionBase.extensions]
     ConstructionBaseIntervalSetsExt = "IntervalSets"
+    ConstructionBaseLinearAlgebraExt = "LinearAlgebra"
     ConstructionBaseStaticArraysExt = "StaticArrays"
 
 [[deps.Contour]]
@@ -775,18 +775,20 @@ weakdeps = ["Unitful"]
 
 [[deps.IntervalArithmetic]]
 deps = ["CRlibm_jll", "MacroTools", "RoundingEmulator"]
-git-tree-sha1 = "433b0bb201cd76cb087b017e49244f10394ebe9c"
+git-tree-sha1 = "01fa84a20be8c7c867edf3b9ef33ac15f4089c1a"
 uuid = "d1acc4aa-44c8-5952-acd4-ba5d80a2a253"
-version = "0.22.14"
+version = "0.22.15"
 
     [deps.IntervalArithmetic.extensions]
     IntervalArithmeticDiffRulesExt = "DiffRules"
     IntervalArithmeticForwardDiffExt = "ForwardDiff"
     IntervalArithmeticRecipesBaseExt = "RecipesBase"
+    IntervalArithmeticsIntervalSetsExt = "IntervalSets"
 
     [deps.IntervalArithmetic.weakdeps]
     DiffRules = "b552c78f-8df3-52c6-915a-8e097449b14b"
     ForwardDiff = "f6369f11-7733-5829-9624-2563aa707210"
+    IntervalSets = "8197267c-284f-5f27-9208-e0e47529a953"
     RecipesBase = "3cdcf5f2-1ef4-517c-9805-6587b60abb01"
 
[…]

### 2024-09-07 src/gridded_data.jl
increase codecov

@@ -13,22 +13,31 @@ path0=joinpath(pwd(),"SEA_SURFACE_HEIGHT_ALT_GRIDS_L4_2SATS_5DAY_6THDEG_V_JPL220
 #url=url1*"oscar_currents_interim_20230101.nc"
 #path1=joinpath(pwd(),"OSCAR_L4_OC_INTERIM_V2.0")*"/"
 
-function get_grid(;url0=url0,
-        range_lon=360.0.+(-35.0,-22),
-        range_lat=(34.0,45),
-        )
-    url=url0*"ssh_grids_v2205_1992101012.dap.nc"
-#    fil=joinpath(tempdir(),"ssh_grids_v2205_1992101012.dap.nc")
-    fil=Downloads.download(url)
 
-    ds=Dataset(fil)
-    lon=Float64.(ds["Longitude"][:])
-    lat=Float64.(ds["Latitude"][:])
+"""
+    get_grid(;url=url0,file="",range_lon=360.0.+(-35.0,-22),range_lat=(34.0,45))
+
+"""
+function get_grid(;url=url0,file="",range_lon=360.0.+(-35.0,-22),range_lat=(34.0,45))
+
+    if !isempty(file)
+        fil=file
+        ds=Dataset(fil)
+        lon=ds["lon"][:]
+        lat=ds["lat"][:]
+    else
+        url=url*"ssh_grids_v2205_1992101012.dap.nc"
+    #    fil=joinpath(tempdir(),"ssh_grids_v2205_1992101012.dap.nc")
+        fil=Downloads.download(url)
+        ds=Dataset(fil)
+        lon=Float64.(ds["Longitude"][:])
+        lat=Float64.(ds["Latitude"][:])        
+    end
 
     ii=findall( (lon.>range_lon[1]) .& (lon.<range_lon[2]) )
     jj=findall( (lat.>range_lat[1]) .& (lat.<range_lat[2]) )
 
-    (lon=lon,lat=lat,ii=ii,jj=jj,nt=2190,url0=url0)
+    (lon=lon,lat=lat,ii=ii,jj=jj,nt=2190,file=fil)
 end
 
 function file_name(n)

### 2024-09-07 test/runtests.jl

@@ -103,11 +103,11 @@ using Test
 
     ##
 
-    b=read(SeaLevelAnomaly(),:sla_podaac)
-    f3=plot(b)
+    SLA=read(SeaLevelAnomaly(),:sla_podaac)
+    f3=plot(SLA)
     @test isa(f3,Figure)
 
-    podaac_sla.file_name(1)
+    podaac_sla.get_grid(file=SLA.file)
 
     ##
 

### 2024-09-07 src/gridded_data.jl
increase codecov

@@ -62,7 +62,7 @@ end
 For download directions, see [this site](https://podaac.jpl.nasa.gov/dataset/SEA_SURFACE_HEIGHT_ALT_GRIDS_L4_2SATS_5DAY_6THDEG_V_JPL2205)
 
 ```
-podaac_sla.subset()
+podaac_sla.subset(; read_from_file=SLA.file)
 ```
 """
 function subset(;
@@ -71,17 +71,26 @@ function subset(;
     password="unknown",
     range_lon=360.0.+(-35.0,-22),
     range_lat=(34.0,45),
+    read_from_file="",
     save_to_file=true,
     )
-    
-    gr=get_grid(range_lon=range_lon,range_lat=range_lat)
-    show(gr)
-    i0=1; i1=gr.nt    
-    data=zeros(length(gr.ii),length(gr.jj),i1-i0+1)
-    for n=i0:i1
-        mod(n,100)==0 ? println(n) : nothing
-        data[:,:,n-i0+1]=read_slice(path0*file_name(n),gr)
+
+    if !isempty(read_from_file)
+        gr=podaac_sla.get_grid(file=read_from_file)
+        ds=podaac_sla.Dataset(read_from_file)
+        i0=1; i1=gr.nt
+        data=ds["SLA"][:,:,:]
+    else
+        gr=get_grid(range_lon=range_lon,range_lat=range_lat)
+        i0=1; i1=gr.nt    
+        data=zeros(length(gr.ii),length(gr.jj),i1-i0+1)
+        for n=i0:i1
+            mod(n,100)==0 ? println(n) : nothing
+            data[:,:,n-i0+1]=read_slice(path0*file_name(n),gr)
+        end
     end
+
+    show(gr)
 
     if save_to_file
         fil=joinpath(tempdir(),"sla_$(i0)_$(i1).nc")

### 2024-09-07 test/runtests.jl

@@ -107,7 +107,10 @@ using Test
     f3=plot(SLA)
     @test isa(f3,Figure)
 
-    podaac_sla.get_grid(file=SLA.file)
+    gr=podaac_sla.get_grid(file=SLA.file)
+    data=podaac_sla.read_slice(SLA.file,gr)
+    filename=podaac_sla.subset(; read_from_file=SLA.file)
+    @test ispath(filename)
 
     ##
 

### 2024-09-07 src/gridded_data.jl
increase codecov

@@ -93,7 +93,8 @@ function subset(;
     show(gr)
 
     if save_to_file
-        fil=joinpath(tempdir(),"sla_$(i0)_$(i1).nc")
+#        fil=joinpath(tempdir(),"sla_$(i0)_$(i1).nc")
+        fil=joinpath(tempdir(),"podaac_sla_dev.nc")
         Dataset(fil,"c",attrib = OrderedDict("title" => "Azores Regional Subset")) do ds
             defVar(ds,"SLA",data,("lon","lat","time"), attrib = OrderedDict(
                 "units" => "m", "long_name" => "Sea Level Anomaly",
@@ -134,24 +135,30 @@ function subset(;
     password="unknown",
     range_lon=(-35.0,-22),
     range_lat=(34.0,45),
+    read_from_file="",
     save_to_file=true,
     )
 
-    url="https://my.cmems-du.eu/thredds/dodsC/"*var
-    url2 = string(URI(URI(url),userinfo = string(username,":",password)))
-    ds = NCDataset(url2)
-
-    lon=ds["longitude"][:]
-    lat=ds["latitude"][:]
+    if !isempty(read_from_file)
+        ds=Dataset(read_from_file)
+        SSH=ds["SLA"]
+        lon=ds["lon"][:]
+        lat=ds["lat"][:]
+    else
+        url="https://my.cmems-du.eu/thredds/dodsC/"*var
+        url2 = string(URI(URI(url),userinfo = string(username,":",password)))
+        ds = NCDataset(url2)
+        SSH=ds["sla"]
+        lon=ds["longitude"][:]
+        lat=ds["latitude"][:]
+    end
 
     ii=findall( (lon.>range_lon[1]) .& (lon.<range_lon[2]) )
     jj=findall( (lat.>range_lat[1]) .& (lat.<range_lat[2]) )
-
-    SSH=ds["sla"]
-
     data = SSH[ii,jj,:]
+
     if save_to_file
-        fil=tempname()
+        fil=joinpath(tempdir(),"cmems_sla_dev.nc")
         Dataset(fil,"c",attrib = OrderedDict("title" => "Azores Regional Subset")) do ds
             defVar(ds,"SLA",data,("lon","lat","time"), attrib = OrderedDict(
                 "units" => "m", "long_name" => "Sea Level Anomaly",

### 2024-09-07 test/runtests.jl

@@ -112,6 +112,10 @@ using Test
     filename=podaac_sla.subset(; read_from_file=SLA.file)
     @test ispath(filename)
 
+    SLA=read(SeaLevelAnomaly(),:sla_cmems)
+    filename=cmems_sla.subset(; read_from_file=SLA.file)
+    @test ispath(filename)
+
     ##
 
     ID="33RR20160208"

### 2024-09-07 dev/search_index.js
build based on 198fd70

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"examples/#Tutorial-Notebooks","page":"Notebooks","title":"Tutorial Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"note: Note\nThe version of the notebooks found in the online docs is static html rendering (this website).\nThe version found in the src folder is the underlying code of the notebooks (.jl files).\nTo run the notebooks interactively see How-To section.","category":"page"},{"location":"examples/#Included-Notebooks","page":"Notebooks","title":"Included Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"OceanOPS.html (➭ code link) : global ocean observing systems\nShipCruise_CCHDO.html (➭ code link) : ship CTD and other data\nFloat_Argo.html (➭ code link) : Argo profiling float data\nDrifter_GDP.html (➭ code link) : drifter time series\nDrifter_CloudDrift.html (➭ code link) : drifter statistics\nGlider_Spray.html (➭ code link) : underwater glider data\nBuoy_NWP_NOAA.html (➭ code link) : NOAA station data (a few days)\nBuoy_NWP_NOAA_monthly.html (➭ code link) : NOAA station data (monthly means) \nMooring_WHOTS.html (➭ code link) : WHOTS mooring data","category":"page"},{"location":"examples/#More-Notebooks","page":"Notebooks","title":"More Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"For Argo and state estimates, see ArgoData.jl\nFor simulations of drifter data, see IndividualDisplacements.jl\nSatelliteAltimetry.html (➭ code link) : gridded satellite data","category":"page"},{"location":"examples/#How-To","page":"Notebooks","title":"How-To","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"To install OceanRobots.jl in julia proceed as usual via the package manager (using Pkg; Pkg.add(OceanRobots)).","category":"page"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"To run a notebook interactively (.jl files) you want to use Pluto.jl. For example, copy and paste on
[…]

### 2024-09-07 dev/search_index.js
build based on c2380c6

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"examples/#Tutorial-Notebooks","page":"Notebooks","title":"Tutorial Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"note: Note\nThe version of the notebooks found in the online docs is static html rendering (this website).\nThe version found in the src folder is the underlying code of the notebooks (.jl files).\nTo run the notebooks interactively see How-To section.","category":"page"},{"location":"examples/#Included-Notebooks","page":"Notebooks","title":"Included Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"OceanOPS.html (➭ code link) : global ocean observing systems\nShipCruise_CCHDO.html (➭ code link) : ship CTD and other data\nFloat_Argo.html (➭ code link) : Argo profiling float data\nDrifter_GDP.html (➭ code link) : drifter time series\nDrifter_CloudDrift.html (➭ code link) : drifter statistics\nGlider_Spray.html (➭ code link) : underwater glider data\nBuoy_NWP_NOAA.html (➭ code link) : NOAA station data (a few days)\nBuoy_NWP_NOAA_monthly.html (➭ code link) : NOAA station data (monthly means) \nMooring_WHOTS.html (➭ code link) : WHOTS mooring data","category":"page"},{"location":"examples/#More-Notebooks","page":"Notebooks","title":"More Notebooks","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"For Argo and state estimates, see ArgoData.jl\nFor simulations of drifter data, see IndividualDisplacements.jl\nSatelliteAltimetry.html (➭ code link) : gridded satellite data","category":"page"},{"location":"examples/#How-To","page":"Notebooks","title":"How-To","text":"","category":"section"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"To install OceanRobots.jl in julia proceed as usual via the package manager (using Pkg; Pkg.add(OceanRobots)).","category":"page"},{"location":"examples/","page":"Notebooks","title":"Notebooks","text":"To run a notebook interactively (.jl files) you want to use Pluto.jl. For example, copy and paste on
[…]

### 2024-09-07 v0.2.6/examples/Buoy_NWP_NOAA.jl
build based on c2380c6

@@ -1,0 +1,1964 @@
+### A Pluto.jl notebook ###
+# v0.19.46
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
+# ╔═╡ c8d36a50-0473-410a-91fa-102f3d071388
+begin
+	using Downloads, ClimateModels
+	using OceanRobots, PlutoUI, CairoMakie
+	"Done with packages"
+end
+
+# ╔═╡ d6feeecc-87db-4bfd-8341-adede2df8ea0
+begin
+	img_url="https://nosc.noaa.gov/OSC/images/Kukui_and_NOAA_buoy_1.177308.JPG"
+	md"""# NOAA Buoys
+
+	Visualize real time data for buoys that report `Standard Meteorological Data`.
+	
+	!!! note 
+	    For more information about NOAA Buoys, visit <https://www.ndbc.noaa.gov/> and links below.
+
+	$(Resource(img_url,:width => 250))
+	"""
+end
+
+# ╔═╡ ee3373bb-a848-4919-9163-384b6f33632a
+TableOfContents()
+
+# ╔═╡ 46ff94e2-1b1e-454d-ab92-89be94123a47
+md"""## Code and Data
+"""
+
+# ╔═╡ db662fb4-7413-11ec-1af6-43b18c0c15a9
+begin
+	#See https://www.ndbc.noaa.gov/
+    stations=[41046, 44065,  
+		31005, 41047, 41117, 42058, 44027, 44084, 45002, 45136, 45164,
[…]

### 2024-09-07 v0.2.6/examples/Buoy_NWP_NOAA_monthly.jl

@@ -1,0 +1,1909 @@
+### A Pluto.jl notebook ###
+# v0.19.46
+
+using Markdown
+using InteractiveUtils
+
+# ╔═╡ 920b7a98-8478-4ad7-8897-8e5d92737199
+begin
+	using PlutoUI, CairoMakie, OceanRobots
+	"Done with packages"
+end
+
+# ╔═╡ 91db1379-9f47-4982-9716-f755451f819f
+begin
+img_url="https://nosc.noaa.gov/OSC/images/Kukui_and_NOAA_buoy_1.177308.JPG"
+	
+md"""# NOAA Buoys / Monthly Means"""
+end
+
+# ╔═╡ 2f87a4a9-ad5d-46ff-961b-028de3a27a23
+PlutoUI.TableOfContents()
+
+# ╔═╡ d106d4c1-1d2e-40b3-8958-901ea437a524
+begin
+md"""In this notebook, you will compute climatologies and distributions from NOAA buoy data.
+
+$(Resource(img_url,:width => 250))
+
+!!! note 
+	For more information about NOAA Buoys, visit <https://www.ndbc.noaa.gov/> and links below.
+
+## Visualize Data	
+"""
+end
+
+# ╔═╡ 502dde03-9ce3-4e15-bfc4-854c87a60026
+md"""## Data Summary
+
+Plot below shows:
+
+- top left: the full distribution of 25 year temperatue changes, using all individual months and years, is shown in the top left corner.
+- top right: averaged month by month, the 25 year change in temperature is positive for each month -- between +2 and +4 degrees, approximately.
+- bottom: the mean seasonal cycle in the ~1990s (blue) and ~2010s (orange). Range is ~ 25 degree in both cases. Shift between the curves is what's shown in top panel.
+"""
+
+# ╔═╡ 34a9a048-da3e-11ec-2017-b7b762895d86
+begin
+	ID=44013
+    buoy=read(NOAAbuoy_monthly(),ID)
+end
+
+# ╔═╡ 051ea6ce-a699-4a08-a4cf-214875bd3ca7
+plot(buoy;option=:demo)
+
[…]

### 2024-09-07 v0.2.6/examples/Drifter_CloudDrift.jl

@@ -1,0 +1,1898 @@
+### A Pluto.jl notebook ###
+# v0.19.46
+
+using Markdown
+using InteractiveUtils
+
+# ╔═╡ bf29d9b6-be57-11ec-2b83-87ce1f770075
+using CairoMakie, OceanRobots, FFTW, PlutoUI
+
+# ╔═╡ 97537903-fb3b-4837-9e7c-461cb9e4ef5e
+md"""# Transpose _Cloud-Drift_ workflow into Julia
+
+See <https://github.com/Cloud-Drift/earthcube-meeting-2022> for context and detail.
+"""
+
+# ╔═╡ c56e7f24-7be8-4209-8fc9-843cb674fd6e
+TableOfContents()
+
+# ╔═╡ f3c351c7-3fba-4ee8-8522-80fd0e8921af
+md"""## Visualize Data"""
+
+# ╔═╡ 05b32012-927d-42b4-8a18-fdfcb051a3fd
+md"""## Per Trajectory Statistics"""
+
+
+# ╔═╡ 89c82c13-9221-48b8-9138-79b91603d7e6
+md"""## Appendix
+
+Packages, grid, functions used in the notebook are defined here.
+"""
+
+# ╔═╡ d0362426-0609-4fcf-a888-77892db9b7e7
+begin
+    GDP_CD=read(CloudDrift(),"")
+    df=GDP_CD.data.main
+    df_subset=GDP_CD.data.subset
+	"Done reading data"
+end
+
+# ╔═╡ 60479536-8238-4077-bdcd-776e07330621
+let
+	ii=findall(isfinite.(df_subset.longitude.*df_subset.latitude))	
+	scatter(df_subset.longitude[ii], df_subset.latitude[ii], markersize=2,
+		color=sqrt.(df_subset.ve.^2+df_subset.vn.^2), colorrange=(0,2.5), colormap=:speed)
+end
+
+# ╔═╡ d4af67e7-2308-4135-929e-c7fc6572d6c7
+heatmap(GDP_CD.data.grid.lon,GDP_CD.data.grid.lat,GDP_CD.data.ve)
+
+# ╔═╡ a25027b5-5b0e-4190-b4b6-987f4e16ccd8
+begin
+	gdf2=GDP_CloudDrift.groupby(df,:ID)
+	df2=GDP_CloudDrift.trajectory_stats(gdf2)
+	trajectory_periodogram(cv) = 1/24 *abs.(fft(cv[:])).^2
[…]

### 2024-09-07 v0.2.6/examples/Drifter_GDP.jl

@@ -1,0 +1,1912 @@
+### A Pluto.jl notebook ###
+# v0.19.46
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
+# ╔═╡ d61376ca-76f2-11ec-0393-83d9b38831ca
+begin
+	using OceanRobots, PlutoUI, CairoMakie
+	"Done with packages"
+end
+
+# ╔═╡ e6d47534-3bdb-401f-8758-12ebce4232f6
+TableOfContents()
+
+# ╔═╡ 84964782-cdd1-4773-a134-04d486e69856
+md"""# Surface Drifters
+
+Here we learn to download, read, and plot one hourly drifter data file from [NOAA webpage](https://www.aoml.noaa.gov/ftp/pub/phod/lumpkin/hourly/v2.00/netcdf/) or its [ftp server](ftp://ftp.aoml.noaa.gov/pub/phod/lumpkin/hourly/v2.00/netcdf/). 
+
+!!! note
+    See [global drifter website](https://www.aoml.noaa.gov/phod/gdp/hourly_data.php) for more information about this data set.
+"""
+
+# ╔═╡ 568d54ae-19a6-4ff4-ae0b-e131693029e5
+begin
+	url0="https://www.aoml.noaa.gov/wp-content/uploads/2020/12/GDP-map.jpg"
[…]

### 2024-09-07 v0.2.6/examples/Glider_Spray.jl

@@ -1,0 +1,1935 @@
+### A Pluto.jl notebook ###
+# v0.19.46
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
+# ╔═╡ 0247a51e-c89b-11ec-071f-bb82fe257adc
+begin
+	using OceanRobots, PlutoUI, CairoMakie
+	"Done with Software Packages"
+end
+
+# ╔═╡ e5b9772e-cbb5-42f0-bacb-5bae6bc8d5b6
+md"""# Spray Gliders
+
+Spray gliders autonomously collect measurements in the upper kilometer of the ocean during missions typically lasting three to four months and covering 2000-3000 km through the water. ([spraydata.ucsd.edu](http://spraydata.ucsd.edu)).
+"""
+
+# ╔═╡ 0a016d12-de41-45f5-800d-af8f953720e4
+begin
+	url1="https://timesofsandiego.com/wp-content/uploads/2014/06/Spray-Glider.jpg"
+	url2="https://www.whoi.edu/wp-content/uploads/2019/01/GP020002-1-14_506075_510753-1.jpg"
+	url3="https://spraydata.ucsd.edu/assets/img/GS_KE_for_web.png"
+	url4="https://spraydata.ucsd.edu/products/cugn-climatology/plots/66/meanmap/66_meanmap_xz_geov.png"
+	md"""
+	$(Resource(url2,:height => 100))
+	$(Resource(url1,:height => 100))
[…]

### 2024-09-07 v0.2.6/examples/Mooring_WHOTS.jl

@@ -1,0 +1,1911 @@
+### A Pluto.jl notebook ###
+# v0.19.46
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
+# ╔═╡ 5fc8cc85-7bd4-4fea-8c6f-01dabee6eb5f
+begin
+	using OceanRobots, CairoMakie, PlutoUI
+	"Done with packages"
+end
+
+# ╔═╡ 538ddc08-85bd-426b-92bc-f5dd78d38d5d
+TableOfContents()
+
+# ╔═╡ 720e1461-81b9-42b6-88be-0115a17268c0
+md"""# WHOTS mooring
+
+Here we plot time series from the [WHOTS mooring](http://www.soest.hawaii.edu/whots/wh_data.html) which measures both Ocean and Atmosphere variables. This is one of the long time series available to study Climate. See <http://www.oceansites.org/> for more data like this.
+"""
+
+# ╔═╡ e7dc453e-3bf2-4289-b55d-66eab3636d7b
+begin
+	url0="https://insideclimatenews.org/wp-content/uploads/2020/07/ohcean-mooring_noaa.jpg"
+	url1="https://aco-ssds.soest.hawaii.edu/ALOHA/img/slideshow3.jpg"
[…]

### 2024-09-07 v0.2.6/examples/OceanOPS.jl

@@ -1,0 +1,2110 @@
+### A Pluto.jl notebook ###
+# v0.19.46
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
+# ╔═╡ ccf98691-9386-41b9-a957-3cdeba51312b
+using OceanRobots, CairoMakie, PlutoUI, MeshArrays
+
+# ╔═╡ 30277358-0a8d-437e-9d2e-ebc7c307db31
+using Shapefile, GeoJSON, DataDeps, PrettyTables, Proj
+
+# ╔═╡ 5fa93c17-0a01-44c6-8679-d712c786907a
+md"""# OceanOPS : Global Ocean Metadata
+
+Source : <https://www.ocean-ops.org/board>, <https://www.ocean-ops.org/share/>
+
+## Visualize Data Cover
+"""
+
+# ╔═╡ 31fe91d7-dea2-49e3-902b-31aa62075986
+TableOfContents()
+
+# ╔═╡ 1042f70c-4337-4bf2-b533-edf27a422365
+md"""## Select a Platform Type
+
+Each color represents one type of observing platform.
+"""
+
+# ╔═╡ 596bce95-e13f-4439-858f-e944834c0924
+begin
+	bind_nam = @bind nam Select([:Argo,:Drifter])
+	md"""## Explore Platform Metadata
+
+	Here you can select a data set and then a platform. Meta-data from that platform is displayed as a result.
+	
+	Data set : $(bind_nam)
[…]

### 2024-09-07 v0.2.6/examples/ShipCruise_CCHDO.jl

@@ -1,0 +1,1931 @@
+### A Pluto.jl notebook ###
+# v0.19.46
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+end
+
+# ╔═╡ e741dbc2-695b-11ef-1962-5769d79825c0
+using OceanRobots, CairoMakie, PlutoUI
+
+# ╔═╡ c90d4b04-9810-4736-8f73-bb6ee2c42577
+md"""# CTD profiles from oceanographic expeditions
+
+CCHDO provides access to high quality, global, ship-based CTD (Conductivity-Temperature-Depth) and hydrographic data from GO-SHIP, WOCE, CLIVAR and other repeat hydrography programs. 
+
+!!! note
+    For more information see <https://cchdo.ucsd.edu>
+
+### Select Cruise
+
+"""
+
+# ╔═╡ 4a1784d6-7850-4c05-b302-013db8966c3a
+@bind ID Select(["33RR20160208","74EQ20151206","33RO20131223"])
+
+# ╔═╡ f5415f1d-0e98-41e3-a6fb-459580141611
+cruise=ShipCruise(ID)
+
+# ╔═╡ fa2c9be1-1198-4852-b7b1-623e42f5c871
+begin
+	vari_bind = @bind vari Select(["temperature","salinity"],default="salinity")
+	cmin_bind = @bind cmin TextField(default="33.5")
+	cmax_bind = @bind cmax TextField(default="35.0")
[…]

### 2024-09-07 v0.2.6/search_index.js

@@ -1,0 +1,3 @@
+var documenterSearchIndex = {"docs":
+[{"location":"contributing/#Contributors-Guide","page":"Contribute","title":"Contributors Guide","text":"","category":"section"},{"location":"contributing/","page":"Contribute","title":"Contribute","text":"Thank you for considering contributing to OceanRobots.jl! If you're interested in contributing we want your help no matter how big or small a contribution you make! ","category":"page"},{"location":"contributing/#Table-of-Contents","page":"Contribute","title":"Table of Contents","text":"","category":"section"},{"location":"contributing/","page":"Contribute","title":"Contribute","text":"How to Contribute\nReporting Bugs\nSuggesting Enhancements\nCode Contribution\nPull Request Process\nLicense","category":"page"},{"location":"contributing/#How-to-Contribute","page":"Contribute","title":"How to Contribute","text":"","category":"section"},{"location":"contributing/#Reporting-Bugs","page":"Contribute","title":"Reporting Bugs","text":"","category":"section"},{"location":"contributing/","page":"Contribute","title":"Contribute","text":"If you encounter a bug, please help us fix it by following these steps:","category":"page"},{"location":"contributing/","page":"Contribute","title":"Contribute","text":"Ensure the bug is not already reported by checking the issue tracker.\nIf the bug isn't reported, open a new issue. Clearly describe the issue, including steps to reproduce it.","category":"page"},{"location":"contributing/#Suggesting-Enhancements","page":"Contribute","title":"Suggesting Enhancements","text":"","category":"section"},{"location":"contributing/","page":"Contribute","title":"Contribute","text":"If you have ideas for enhancements, new features, or improvements, we'd love to hear them! Follow these steps:","category":"page"},{"location":"contributing/","page":"Contribute","title":"Contribute","text":"Check the issue tracker to see if your suggestion has been discussed.\nIf not, open a new issue, providing a detailed description of your suggestion and the use case it addresses.","category":"page"},{"location":"contributing/#Code-Contribution","page":"Contribute","title":"Code Contribution","text":"","category":"section"},{"location":"contributing/","page":"Contribute","title":"
[…]

### 2024-11-12 paper/paper.tex
update refs

@@
 Through a streamlined workflow, \pkg{ClimateModels.jl} (JuliaCon 2021, 2023) makes it easy to operate these models that can provide a virtual environment for the virtual ocean robot fleet to observe and navigate.
-\pkg{IndividualDisplacements.jl} \cite{Forget2021} can be use to predict pathways of ocean robots that tend to follow ocean currents.
+\pkg{Drifters.jl} \cite{Forget2021} can be use to predict pathways of ocean robots that tend to follow ocean currents.
 \pkg{MeshArrays.jl} adds basic geospatial support for global climate model grids, providing capabilities such as interpolation and geolocation on a grid.
@@
 sea gliders & \struct{Gliders} \\
+expendable bathythermographs & \tbd \\
+sea gliders & \struct{Gliders} \\
 sail drones & \tbd \\
-research vessels & \tbd \\
+research vessels & CCHDO \\
 ships of opportunity & \tbd \\
@@
 
-Here we used the OCCA climatology \cite{Forget2010} to provide $T,S(x,y,z,t)$ and create Fig.~\ref{fig:Argo_Float_simu}, with \pkg{MeshArrays.jl} providing the geospatial tools.
+To create Fig.~\ref{fig:Argo_Float_simu}, we use \pkg{Climatology.jl} to access the OCCA climatology \cite{Forget2010}, and then interpolate $T,S(x,y,z,t)$ via the geospatial tools in \pkg{MeshArrays.jl} providing.
 OCCA is essentially a previously trained model that consists of 12 monthly three-dimensional fields of $T,S$ (one per calendar month).
@@
 This basic simulation of surface drifter pathways uses the geostatistical average of velocities calculated in Fig.~\ref{fig:drifters_ve} as a predictive model for the $U,V(x,y,t)$ velocity fields.
-This gridded data set is simply provided as input to \pkg{IndividualDisplacements.jl}, which then releases virtual drifters and calculates their trajectories following the flow field (code~\ref{lst:IndDispCode}).
+This gridded data set is simply provided as input to \pkg{Drifters.jl}, which then releases virtual drifters and calculates their trajectories following the flow field (code~\ref{lst:IndDispCode}).
 The combination of these two model elements represents a previously trained model to predict surface drifter trajectories.
@@
 \centerline{\includegraphics[width=\columnwidth]{figs/20240529_speed_subset_IndDisp.png}}
-\caption{Virtual drifter trajectories predicted using (1) just the climatological mean flow field estimated from drifters (Fig.~\ref{fig:drifters_ve}, and the northward component) and (2) \pkg{IndividualDisplacements.jl} to calculate trajectories.}
+\caption{Virtual drifter trajectories predicted using (1) just the climatological mean flow field estimated from drifters (Fig.~\ref{fig:drifters_ve}, and the northward component) and (2) \pkg{Drifters.jl} to calculate trajectories.}
 \label{fig:drifters_speed_simu}
@@
 ]
-using IndividualDisplacements
+using Drifters
 
@@
 
-The core of DTOR is formed by \pkg{OceanRobots.jl}, \pkg{ArgoData.jl}, and \pkg{MeshArrays.jl} for the physical twins, along with \pkg{ClimateModels.jl}, \pkg{MITgcm.jl}, and \pkg{IndividualDisplacements.jl} for the virtual twins (i.e., predictive modeling).
+The core of DTOR is formed by \pkg{OceanRobots.jl}, \pkg{ArgoData.jl}, and \pkg{MeshArrays.jl} for the physical twins, along with \pkg{ClimateModels.jl}, \pkg{MITgcm.jl}, and \pkg{Drifters.jl} for the virtual twins (i.e., predictive modeling).
 The \pkg{ClimateModels.jl} interface streamlines the use of models implemented in various languages.
@@
 Multi-decadal solutions produced in this way can then be further downscaled using km-scale model output (Fig.~\ref{fig:km_scale}).
-At the end of this modeling workflow, \pkg{OceanRobots.jl}, \pkg{MeshArrays.jl} and \pkg{IndividualDisplacements.jl} enable calculations such as Figs.~\ref{fig:Argo_Float_simu} and \ref{fig:drifters_speed_simu}, for any of our models.
+At the end of this modeling workflow, \pkg{OceanRobots.jl}, \pkg{MeshArrays.jl} and \pkg{Drifters.jl} enable calculations such as Figs.~\ref{fig:Argo_Float_simu} and \ref{fig:drifters_speed_simu}, for any of our models.
 DTOR can also take advantage of gridded satellite data, incl.
@@
 Our current focus is on geospatial analyses that track global warming and marine heatwaves using Argo data \cite{Forget2024a}.
-Another example from our research is with the CStream research program (UK-US) which is releasing drifters near Florida Strait to track the nutrient stream that is associated with the Gulf Stream (Fig.~\ref{fig:Cstream}).
+Another example from our research is with the C-Streams research program (UK-US) which is releasing drifters near Florida Strait to track the nutrient stream that is associated with the Gulf Stream.
+The example in Fig.~\ref{fig:Cstream} is based on the monthly mean ECCO climatology for ocean transports \cite{Forget2015a,Forget2019,Rousselet2021}, and using \pkg{Climatology.jl}, \pkg{MeshArrays.jl}, and \pkg{Drifters.jl} to calculate pathways.
 Other applications at the scale of oceanic basins include tracking ocean plastic pollution, monitoring biological impacts of extreme events and global warming, or the optimization of the global climate monitoring fleet of ocean robots for e.g.

### 2024-11-12 paper/paper.tex
minor text edits / proofreading

@@
 Digital twins provide a bridge to predictive models that enables machine learning.
-In turn, simulating observations in a virtual environment can help evaluate observational strategies a priori, during deployment, or afterwards.
+In turn, simulating observations in a digital environment can help evaluate observational strategies a priori, during deployment, or afterwards.
 In this paper we present the framework, review simulated ocean robots, and discuss envisioned applications.
@@
 At JuliaCon 2023, we presented a solution to (1) access and manipulate the data collected by ocean robots (inc.
-\pkg{OceanRobots.jl} and \pkg{ArgoData.jl}), and (2) simulate such observations in a virtual environment using a hierarchy of models (incl.
+\pkg{OceanRobots.jl} and \pkg{ArgoData.jl}), and (2) simulate such observations in a digital environment using a hierarchy of models (incl.
 \pkg{ClimateModels.jl} and \pkg{MITgcm.jl}).
@@
 The model hierarchy includes fast climate model emulators, global model output, ocean reanalyses, high-resolution models, and several ways to represent marine ecosystems.
-Through a streamlined workflow, \pkg{ClimateModels.jl} (JuliaCon 2021, 2023) makes it easy to operate these models that can provide a virtual environment for the virtual ocean robot fleet to observe and navigate.
+Through a streamlined workflow, \pkg{ClimateModels.jl} (JuliaCon 2021, 2023) makes it easy to operate these models that can provide a digital environment for the virtual ocean robot fleet to observe and navigate.
 \pkg{Drifters.jl} \cite{Forget2021} can be use to predict pathways of ocean robots that tend to follow ocean currents.
@@
 To create this map, \pkg{OceanRobots.jl} queries the meta-data-base from Ocean-OPS.org, which keeps track of the whole ocean fleet of scientific observation platforms in real time, and provides a restful API.
-\pkg{OceanRobots.jl} provides a simple interface to this API via the `OceanOPS` module.
-It then provides dedicated data structures to access and utilize data from common ocean robot types such as  `SurfaceDrifter` and `ArgoFloat` (shown in Fig.~\ref{fig:ocean-ops}).
+The \pkg{OceanRobots.jl} package provides a simple interface to this API via the `OceanOPS` module.
+\pkg{OceanRobots.jl} defines data structures to access and utilize data from common ocean robot types such as  `SurfaceDrifter` and `ArgoFloat` (shown in Fig.~\ref{fig:ocean-ops}).
 A non-exhaustive list of ocean observing platform categories within the scope of \pkg{OceanRobots.jl} is provided in Tab.~\ref{tab:robots}.
@@
 Argo profiling floats (blue dots in Fig.~\ref{fig:ocean-ops}; Code~\ref{lst:ArgoCode}) are one of our main tools to monitor global warming below the sea surface.
-These devices provide a less detailed view of oceanic pathways (Fig.~\ref{fig:Argo_Float}, top panels) than surface drifters do (e.g., Fig.~\ref{fig:drifters}) with just one location being recorded every ten days.
+These devices provide a less detailed view of oceanic pathways (Fig.~\ref{fig:Argo_Float}, top panels) than surface drifters do (e.g., Fig.~\ref{fig:drifters}), since Argo floats only report their location once every ten days.
 However, Argo floats have a crucial diving capability that surface drifters don't have -- they go up and down the water column to measure temperature and salinity (T,S; bottom panels of Fig.~\ref{fig:Argo_Float}).
-As a result, the advent of Argo in the early 2000s \cite{Roemmich2019} opened up a whole new era of geospatial analysis, state estimation, and parameter inference over the global Ocean  \cite{Forget2007,Forget2010,MFF14,Forget2015a,FFL15,FP15,Forget2024a}.
+As a result, the advent of the Argo array in the early 2000s \cite{Roemmich2019} opened up a whole new era of geospatial analysis, state estimation, and parameter inference over the global Ocean  \cite{Forget2007,Forget2010,MFF14,Forget2015a,FFL15,FP15,Forget2024a}.
 There were 3837 Argo floats at sea on `2024/05/27`, and a total of 18730 in the Argo data base.
-Since the Argo array is such an important and somewhat complex observing system, a dedicated package called \pkg{ArgoData.jl} was created that \pkg{OceanRobots.jl} uses under the hood.
+Since the Argo array is such an important observing system, a dedicated package called \pkg{ArgoData.jl} was created that \pkg{OceanRobots.jl} uses under the hood.
 
@@
 It provides a bridge to climate scientists working on observations and models, who are interested in leveraging the powerful Julia software ecosystem (e.g., for numerical modeling, machine learning, and statistical analysis), and have much expertise to contribute.
-The development of \pkg{OceanRobots.jl} aims to help advance (1) how we understand and simulate observations of climate change, and (2) climate literacy and education by providing simple apps that anyone should be able to use.
+The development of \pkg{OceanRobots.jl} aims to help advance (1) how we understand and simulate observations that monitor climate change in the oceans, and (2) climate literacy and education by providing simple apps that anyone can use.
 
@@
 Many research activities involve combining ocean models and observations, with the typical goal of learning model parameters and dynamics from data \cite{Forget2010,Forget2015a,FFL15,FP15,Forget2024a}.
-Observing system simulations in a virtual environment (using models) enable a wide range of applications -- to test out innovative platform or sensor designs ahead of deployment, to optimize global monitoring strategies, or to guide deployed assets in real time for example.
+Observing system simulations in a digital environment (using models) enable a wide range of applications -- to test out innovative platform or sensor designs ahead of deployment, to optimize global monitoring strategies, or to guide deployed assets in real time for example.
 
@@
 First, in Fig.~\ref{fig:Argo_Float_simu} we simulate an Argo data collection for temperature (T) and salinity (S) by sampling an ocean climatology along the track of the Argo float (the one from Fig.~\ref{fig:Argo_Float}).
-This calculation requires (1) a model prediction of $T,S(x,y,z,t)$, which can be based on statistical or mechanistic models, e.g.
-on a discrete grid, and (2) tools that deal with the Earth geography, can localize observations on a grid, and perform interpolation tasks.
+This calculation requires (1) a model prediction of $T,S(x,y,z,t)$, which can be based on statistical or mechanistic models on a grid, and (2) tools that deal with the Earth geography, and can localize observations on a grid, and perform interpolation tasks.
 
@@
 The combination of these two model elements represents a previously trained model to predict surface drifter trajectories.
-While it neglects time-variability and small scales in ocean currents altogether, this model is sufficient to capture the mean pathway of sea water through this region -- the well-known loop current feeding the Gulf Stream via Florida Strait (Fig.~\ref{fig:drifters_speed_simu}).
+While this simple calculation neglects time-variability and small scales in ocean currents altogether, the model is sufficient to capture the mean pathway of sea water through this region -- the well-known loop current feeding the Gulf Stream via Florida Strait (Fig.~\ref{fig:drifters_speed_simu}).
 
@@
 ]
-using Drifters
+using Drifters, DataFrames
 
@@
 The tutorial examples in \pkg{OceanRobots.jl}, \pkg{ArgoData.jl}, \pkg{ClimateModels.jl}, and \pkg{MITgcm.jl} \cite{Forget2024b} are notably available as Pluto notebooks.
-Interaction between model and data is further enabled by the rich Julia ecosystem for machine learning, data assimilation, parameter inference, and so on.
-Fig.~\ref{fig:MLP} provides an example where we used \pkg{Flux.jl} \cite{Innes2018} to train a neural network to predict chlorophyll concentration (linked to marine microbe abundance) from environmental parameters as done in the CANYON model \cite{Sauzede2017,Bittig2018}.
+Interaction between model and data is further enabled by the rich Julia ecosystem for machine learning, data assimilation, parameter inference, etc.
+Fig.~\ref{fig:MLP} provides an example where \pkg{Flux.jl} \cite{Innes2018} is used to train neural networks to predict chlorophyll concentration (linked to marine microbe abundance) from environmental parameters as done in the CANYON model \cite{Sauzede2017,Bittig2018}.
 
-The core of DTOR is formed by \pkg{OceanRobots.jl}, \pkg{ArgoData.jl}, and \pkg{MeshArrays.jl} for the physical twins, along with \pkg{ClimateModels.jl}, \pkg{MITgcm.jl}, and \pkg{Drifters.jl} for the virtual twins (i.e., predictive modeling).
+The core of DTOR is formed by \pkg{OceanRobots.jl}, \pkg{ArgoData.jl}, and \pkg{MeshArrays.jl} for the physical twins, along with \pkg{Climatology.jl}, \pkg{ClimateModels.jl}, \pkg{MITgcm.jl}, and \pkg{Drifters.jl} for the virtual twins (i.e., predictive modeling).
 The \pkg{ClimateModels.jl} interface streamlines the use of models implemented in various languages.
-Our current model hierarchy supported via \pkg{ClimateModels.jl} includes, but is not limited to, the models used in this paper.
-DTOR can notably simulate observations in the future based on climate model predictions using \pkg{ClimateModels.jl}, which provides two options for this kind of applications -- either querying the CMIP6 archive of model output \cite{CMIP6} or using a fast emulator such as Hector \cite{Hector2015} (Fig.~\ref{fig:globalwarming}).
+The model hierarchy already includes the models used in this paper, and is easy to extend via pkg{ClimateModels.jl}.
+DTOR can notably simulate observations in the future based on climate model predictions, and \pkg{ClimateModels.jl} provides two options for this kind of applications -- either querying the CMIP6 archive of model output \cite{CMIP6} or using a fast emulator such as Hector \cite{Hector2015} (Fig.~\ref{fig:globalwarming}).
 
@@
 DTOR can also take advantage of gridded satellite data, incl.
-sea surface temperature and sea level anomalies, and it is sometimes possible to use these instead of ocean reanalyses.
+sea surface temperature and sea level anomalies via \pkg{Climatology.jl}, and it is sometimes possible to use these instead of ocean reanalyses.
 
@@
 First, we'd like to integrate additional types of ocean observing platforms, starting with those that do not have a data structure listed yet in Tab.~\ref{tab:robots}.
-Observational networks that focus on the coastal ocean, a specific region, or local field experiments could be supported in the future.
+Observational networks that focus on either the coastal ocean, a specific region, or local field experiments could be supported in the future.
 A top level API to interact with DTOR as a whole through cloud services is also envisioned.
@@
 Our current focus is on geospatial analyses that track global warming and marine heatwaves using Argo data \cite{Forget2024a}.
-Another example from our research is with the C-Streams research program (UK-US) which is releasing drifters near Florida Strait to track the nutrient stream that is associated with the Gulf Stream.
-The example in Fig.~\ref{fig:Cstream} is based on the monthly mean ECCO climatology for ocean transports \cite{Forget2015a,Forget2019,Rousselet2021}, and using \pkg{Climatology.jl}, \pkg{MeshArrays.jl}, and \pkg{Drifters.jl} to calculate pathways.
-Other applications at the scale of oceanic basins include tracking ocean plastic pollution, monitoring biological impacts of extreme events and global warming, or the optimization of the global climate monitoring fleet of ocean robots for e.g.
-cost.
-More locally, DTOR could be used in the context of field experiments such as S-MODE, to choose an example from the recent past.
-Related projects on digital twins, not focused on exploiting Julia, include the EU funded {\it Destination Earth} program, Mercator Ocean International's {\it Digital Twin Ocean}, and the UN Decade Action's DITTO initiative ({\it Digital Twins of The Ocean}).
+Another example from our research is with the C-Streams observational program (UK-US) which is releasing drifters near Florida Strait to track the nutrient stream that is associated with the Gulf Stream.
+A simulation of these pathways is shown in Fig.~\ref{fig:Cstream}, which is based on the monthly mean ECCO4 climatology for ocean transports \cite{Forget2015a,Forget2019,Rousselet2021}, and uses \pkg{Climatology.jl}, \pkg{MeshArrays.jl}, and \pkg{Drifters.jl} to calculate pathways.
+Other applications at the scale of oceanic basins include tracking ocean plastic pollution, monitoring biological impacts of extreme events and global warming, or the optimization of the global climate monitoring fleet of ocean robots.
+DTOR could be used to pilot field experiments (e.g., S-MODE, to choose an example from the recent past).
+Related projects on digital twins, not focused on exploiting Julia but interested in ocean observations, include the EU funded {\it Destination Earth} program, Mercator Ocean International's {\it Digital Twin Ocean}, and the UN Decade Action's DITTO initiative ({\it Digital Twins of The Ocean}).
 

### 2024-11-14 paper/paper.tex
address reviewer minor comments

@@
 DTOR is a framework to access and simulate the global fleet of ocean observing devices (or {\it ocean robots}) that monitor climate change.
-It brings these observations to Julia and let's us pair ocean robots with virtual counterparts (or {\it twins}).
+It brings these observations to Julia and lets us pair ocean robots with virtual counterparts (or {\it twins}).
 Digital twins provide a bridge to predictive models that enables machine learning.
@@
 Part of the fleet of ocean robots currently at sea is depicted in Fig.~\ref{fig:ocean-ops}, focusing on some of the most common observing platforms.
-To create this map, \pkg{OceanRobots.jl} queries the meta-data-base from Ocean-OPS.org, which keeps track of the whole ocean fleet of scientific observation platforms in real time, and provides a restful API.
+To create this map, \pkg{OceanRobots.jl} queries the meta-data-base from Ocean-OPS.org, which keeps track of the whole ocean fleet of scientific observation platforms in real time, and provides a RESTful API.
 The \pkg{OceanRobots.jl} package provides a simple interface to this API via the `OceanOPS` module.
@@
 These drifting buoys tend to follow near-surface ocean currents (at approximately 15 depth).
-They can measure sea surface temperature and sea level pressure along their trajectories.
+They can measure sea surface temperature and sea level pressure along their trajectory.
 The data archive currently holds 19396 drifter trajectories, collected over the past 50 years, which allow us to create climatologies such as the one shown in Fig.~\ref{fig:drifters_ve}.
@@
 The combination of these two model elements represents a previously trained model to predict surface drifter trajectories.
-While this simple calculation neglects time-variability and small scales in ocean currents altogether, the model is sufficient to capture the mean pathway of sea water through this region -- the well-known loop current feeding the Gulf Stream via Florida Strait (Fig.~\ref{fig:drifters_speed_simu}).
+While this simple calculation neglects time variability and small scales in ocean currents altogether, the model is sufficient to capture the mean pathway of sea water through this region -- the well-known loop current feeding the Gulf Stream via Florida Strait (Fig.~\ref{fig:drifters_speed_simu}).
 
@@
 Within our model hierarchy, future climate scenarios like Fig.~\ref{fig:globalwarming} can be downscaled using gridded climatologies and reanalyses \cite{Forget2010,Forget2015a,Forget2024a}.
-The ECCO4 and OCCA2 reanalyses are simple to rerun with perturbed surface forcing fields via \pkg{MITgcm.jl}, which is partiucularly convenient for such applications.
+The ECCO4 and OCCA2 reanalyses are simple to rerun with perturbed surface forcing fields via \pkg{MITgcm.jl}, which is particularly convenient for such applications.
 Multi-decadal solutions produced in this way can then be further downscaled using km-scale model output (Fig.~\ref{fig:km_scale}).

### 2024-11-14 paper/paper.tex
fix my name in paper (oups)

@@
 pdfsubject = {JuliaCon 2023 Proceedings},
-pdfauthor = {Gaël.Forget},
+pdfauthor = {Gaël Forget},
 pdfkeywords = {Julia, Ocean, Robots, Observation, In Situ, Model},

### 2024-11-17 paper/paper.tex
consolidate  section
update example to avoid warning

@@
 
-\author[1]{Gaël.Forget}
+\author[1]{Gaël Forget}
 \affil[1]{Earth, Atmospheric and Planetary Sciences, Massachusetts Institute of Technology, \newline
@@
 using OceanRobots, ArgoData, CairoMakie
-
-lst=GDAC.files_list(); wmo=6900900
-argo=read(ArgoFloat(),wmo=wmo,files_list=lst)
-
+argo=read(ArgoFloat(),wmo=6900900)
 fig=plot(argo,option=:standard)

### 2024-11-17 src/files.jl
get SurfaceDrifter from http server (instead of failing ftp server)

@@ -466,9 +466,10 @@ end #module NOAA
 
 module GDP
 
-using DataFrames, FTPClient, NCDatasets, Dates, CSV
+using DataFrames, NCDatasets, Dates, CSV
 import OceanRobots: SurfaceDrifter
 import Base: read
+import Downloads, FTPClient
 
 """
     list_files()
@@ -547,6 +548,30 @@ read(x::SurfaceDrifter,ii::Int; list_files=[]) = begin
 	ds=Dataset(fil)
     wmo=ds[:WMO][1]
     SurfaceDrifter(lst.ID[ii],ds,wmo,lst)
+end
+
+"""
+    read(x::SurfaceDrifter; ID=300234065515480, version="v2.01")
+
+Download file from NOAA http server read it using `NCDatasets.jl`.
+
+Server : https://www.aoml.noaa.gov/ftp/pub/phod/lumpkin/hourly/
+
+```
+using OceanRobots
+sd=read(SurfaceDrifter(),ID=300234065515480)
+```
+"""
+read(x::SurfaceDrifter; ID=300234065515480, version="v2.01") = begin
+    prefix = (version=="v2.01" ? "drifter_hourly_" : "drifter_")
+    fil=prefix*"$(ID).nc"
+    url0="https://www.aoml.noaa.gov/ftp/pub/phod/lumpkin/hourly/$(version)/netcdf/"
+    path0=joinpath(tempdir(),"drifters_hourly_noaa")
+    !isdir(path0) ? mkdir(path0) : nothing
+    Downloads.download(url0*fil,path0*fil)
+	ds=Dataset(path0*fil)
+    wmo=ds[:WMO][1]
+    SurfaceDrifter(ID,ds,wmo,DataFrame())
 end
 
 missing_to_NaN(x) = [(ismissing(y) ? NaN : y) for y in x]

### 2024-11-17 src/files.jl
import rather than using for FTPClient

@@ -486,7 +486,7 @@ function list_files()
         list_files=CSV.read(fil,DataFrame)
     else
         list_files=DataFrame("folder" => [],"filename" => [])
-        ftp=FTP("ftp://ftp.aoml.noaa.gov/pub/phod/lumpkin/hourly/v2.00/netcdf/")
+        ftp=FTPClient.FTP("ftp://ftp.aoml.noaa.gov/pub/phod/lumpkin/hourly/v2.00/netcdf/")
         tmp=readdir(ftp)
         append!(list_files,DataFrame("folder" => "","filename" => tmp))
         list_files.ID=[parse(Int,split(f,"_")[2][1:end-3]) for f in list_files.filename]
@@ -515,7 +515,7 @@ function download(list_files,ii=1)
     url0="ftp://ftp.aoml.noaa.gov/pub/phod/lumpkin/hourly/v2.00/netcdf/"
     pth0=list_files[ii,"folder"]
     url1=(ismissing(pth0) ? url0 : joinpath(url0,pth0))
-    ftp=FTP(url1)
+    ftp=FTPClient.FTP(url1)
 
     fil=list_files[ii,"filename"]
     
@@ -720,7 +720,8 @@ end
 
 module OceanSites
 
-using NCDatasets, FTPClient, CSV, DataFrames, Dates
+using NCDatasets, CSV, DataFrames, Dates
+import FTPClient
 import OceanRobots: OceanSite
 import Base: read
 
@@ -782,7 +783,7 @@ oceansites_index=OceanSites.index()
 function index()
     url="ftp://ftp.ifremer.fr/ifremer/oceansites/"
     fil=joinpath(tempdir(),"oceansites_index.txt")
-    ftp=FTP(url)
+    ftp=FTPClient.FTP(url)
     !isfile(fil) ? FTPClient.download(ftp, "oceansites_index.txt",fil) : nothing
 
     #main table

### 2024-11-17 docs/make.jl
docs improvement from JCON proceeding paper review

@@ -16,7 +16,7 @@ makedocs(;
         "Home" => "index.md",
         "User Interface" => "reference.md",
         "Notebooks" => "examples.md",
-        "Contribute" => "contributing.md",
+        "User Directions" => "contributing.md",
         ],
     repo="https://github.com/JuliaOcean/OceanRobots.jl/blob/{commit}{path}#L{line}",
     sitename="OceanRobots.jl",

### 2024-11-24 paper/paper.tex
update table

@@
 sea gliders & \struct{Gliders} \\
-expendable bathythermographs & \tbd \\
-sea gliders & \struct{Gliders} \\
+expendable bathy-thermographs & \tbd \\
 sail drones & \tbd \\
-research vessels & CCHDO \\
-ships of opportunity & \tbd \\
-orbiting satellites & \struct{SeaLevelAnomaly} \\
-suborbital flights & \tbd \\
+\hline
+research vessel data & CCHDO \\
+ships of opportunity data & \tbd \\
 marine mammals & \tbd \\\hline

### 2024-11-24 examples/Float_Argo.jl
update deps

@@ -182,7 +182,7 @@ Shapefile = "8e980c4a-a4fe-5da2-b3a7-4b4b0353a2f4"
 PLUTO_MANIFEST_TOML_CONTENTS = """
 # This file is machine-generated - editing it directly is not advised
 
-julia_version = "1.10.4"
+julia_version = "1.11.1"
 manifest_format = "2.0"
 project_hash = "06aedfd2c48d9dcc3a5a903f4cea9cd3e4b45dd2"
 
@@ -208,26 +208,20 @@ git-tree-sha1 = "2d9c9a55f9c93e8887ad391fbae72f8ef55e1177"
 uuid = "1520ce14-60c1-5f80-bbc7-55ef81b5835c"
 version = "0.4.5"
 
-[[deps.AccurateArithmetic]]
-deps = ["LinearAlgebra", "Random", "VectorizationBase"]
-git-tree-sha1 = "07af26e8d08c211ef85918f3e25d4c0990d20d70"
-uuid = "22286c92-06ac-501d-9306-4abd417d9753"
-version = "0.3.8"
-
 [[deps.Adapt]]
 deps = ["LinearAlgebra", "Requires"]
-git-tree-sha1 = "6a55b747d1812e699320963ffde36f1ebdda4099"
+git-tree-sha1 = "50c3c56a52972d78e8be9fd135bfb91c9574c140"
 uuid = "79e6a3ab-5dfb-504d-930d-738a2a938a0e"
-version = "4.0.4"
+version = "4.1.1"
 weakdeps = ["StaticArrays"]
 
     [deps.Adapt.extensions]
     AdaptStaticArraysExt = "StaticArrays"
 
 [[deps.AdaptivePredicates]]
-git-tree-sha1 = "7d5da5dd472490d048b081ca1bda4a7821b06456"
+git-tree-sha1 = "7e651ea8d262d2d74ce75fdf47c4d63c07dba7a6"
 uuid = "35492f91-a3bd-45ad-95db-fcad7dcfedb7"
-version = "1.1.1"
+version = "1.2.0"
 
 [[deps.AliasTables]]
 deps = ["PtrArrays", "Random"]
@@ -237,68 +231,45 @@ version = "1.1.3"
 
 [[deps.Animations]]
 deps = ["Colors"]
-git-tree-sha1 = "e81c509d2c8e49592413bfb0bb3b08150056c79d"
[…]

### 2024-11-24 examples/Buoy_NWP_NOAA.jl
update notebook dependencies

@@ -1,17 +1,19 @@
 ### A Pluto.jl notebook ###
-# v0.19.46
+# v0.20.3
 
 using Markdown
 using InteractiveUtils
 
 # This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
 macro bind(def, element)
+    #! format: off
     quote
         local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
         local el = $(esc(element))
         global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
         el
     end
+    #! format: on
 end
 
 # ╔═╡ c8d36a50-0473-410a-91fa-102f3d071388
@@ -143,7 +145,7 @@ PlutoUI = "7f904dfe-b85e-4ff6-b463-dae2292396a8"
 PLUTO_MANIFEST_TOML_CONTENTS = """
 # This file is machine-generated - editing it directly is not advised
 
-julia_version = "1.10.5"
+julia_version = "1.11.1"
 manifest_format = "2.0"
 project_hash = "dab0cebf879211c8791496c0ee2161abb0037489"
 
@@ -171,18 +173,18 @@ version = "0.4.5"
 
 [[deps.Adapt]]
 deps = ["LinearAlgebra", "Requires"]
-git-tree-sha1 = "6a55b747d1812e699320963ffde36f1ebdda4099"
+git-tree-sha1 = "50c3c56a52972d78e8be9fd135bfb91c9574c140"
 uuid = "79e6a3ab-5dfb-504d-930d-738a2a938a0e"
-version = "4.0.4"
+version = "4.1.1"
 weakdeps = ["StaticArrays"]
 
     [deps.Adapt.extensions]
     AdaptStaticArraysExt = "StaticArrays"
 
 [[deps.AdaptivePredicates]]
[…]

### 2024-11-24 examples/Drifter_GDP.jl

@@ -1,17 +1,19 @@
 ### A Pluto.jl notebook ###
-# v0.19.46
+# v0.20.3
 
 using Markdown
 using InteractiveUtils
 
 # This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
 macro bind(def, element)
+    #! format: off
     quote
         local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
         local el = $(esc(element))
         global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
         el
     end
+    #! format: on
 end
 
 # ╔═╡ d61376ca-76f2-11ec-0393-83d9b38831ca

### 2024-11-24 examples/Float_Argo.jl

@@ -2009,15 +2009,15 @@ version = "1.8.6+0"
 
 [[deps.Xorg_libXau_jll]]
 deps = ["Artifacts", "JLLWrappers", "Libdl"]
-git-tree-sha1 = "6035850dcc70518ca32f012e46015b9beeda49d8"
+git-tree-sha1 = "2b0e27d52ec9d8d483e2ca0b72b3cb1a8df5c27a"
 uuid = "0c0b7dd1-d40b-584c-a123-a41640f87eec"
-version = "1.0.11+0"
+version = "1.0.11+1"
 
 [[deps.Xorg_libXdmcp_jll]]
 deps = ["Artifacts", "JLLWrappers", "Libdl"]
-git-tree-sha1 = "34d526d318358a859d7de23da945578e8e8727b7"
+git-tree-sha1 = "02054ee01980c90297412e4c809c8694d7323af3"
 uuid = "a3789734-cfe1-5b06-b2d0-1dd0d9d62d05"
-version = "1.1.4+0"
+version = "1.1.4+1"
 
 [[deps.Xorg_libXext_jll]]
 deps = ["Artifacts", "JLLWrappers", "Libdl", "Xorg_libX11_jll"]
@@ -2045,9 +2045,9 @@ version = "1.17.0+0"
 
 [[deps.Xorg_xtrans_jll]]
 deps = ["Artifacts", "JLLWrappers", "Libdl"]
-git-tree-sha1 = "e92a1a012a10506618f10b7047e478403a046c77"
+git-tree-sha1 = "b9ead2d2bdb27330545eb14234a2e300da61232e"
 uuid = "c5fb5394-a638-5e4d-96e5-b29de1b5cf10"
-version = "1.5.0+0"
+version = "1.5.0+1"
 
 [[deps.YAML]]
 deps = ["Base64", "Dates", "Printf", "StringEncodings"]

### 2024-11-24 examples/Mooring_WHOTS.jl

@@ -1,17 +1,19 @@
 ### A Pluto.jl notebook ###
-# v0.19.46
+# v0.20.3
 
 using Markdown
 using InteractiveUtils
 
 # This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
 macro bind(def, element)
+    #! format: off
     quote
         local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
         local el = $(esc(element))
         global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
         el
     end
+    #! format: on
 end
 
 # ╔═╡ 5fc8cc85-7bd4-4fea-8c6f-01dabee6eb5f

### 2024-11-24 dev/examples/Float_Argo.jl
build based on 1866b99

@@ -1,17 +1,19 @@
 ### A Pluto.jl notebook ###
-# v0.19.46
+# v0.20.3
 
 using Markdown
 using InteractiveUtils
 
 # This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
 macro bind(def, element)
+    #! format: off
     quote
         local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
         local el = $(esc(element))
         global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
         el
     end
+    #! format: on
 end
 
 # ╔═╡ 8539e67f-6361-409a-9dbe-e8dcb2c7e10d
@@ -180,7 +182,7 @@ Shapefile = "8e980c4a-a4fe-5da2-b3a7-4b4b0353a2f4"
 PLUTO_MANIFEST_TOML_CONTENTS = """
 # This file is machine-generated - editing it directly is not advised
 
-julia_version = "1.10.4"
+julia_version = "1.11.1"
 manifest_format = "2.0"
 project_hash = "06aedfd2c48d9dcc3a5a903f4cea9cd3e4b45dd2"
 
@@ -206,26 +208,20 @@ git-tree-sha1 = "2d9c9a55f9c93e8887ad391fbae72f8ef55e1177"
 uuid = "1520ce14-60c1-5f80-bbc7-55ef81b5835c"
 version = "0.4.5"
 
-[[deps.AccurateArithmetic]]
-deps = ["LinearAlgebra", "Random", "VectorizationBase"]
-git-tree-sha1 = "07af26e8d08c211ef85918f3e25d4c0990d20d70"
-uuid = "22286c92-06ac-501d-9306-4abd417d9753"
-version = "0.3.8"
-
 [[deps.Adapt]]
 deps = ["LinearAlgebra", "Requires"]
[…]

### 2024-11-24 dev/examples/Glider_Spray.jl

@@ -1,17 +1,19 @@
 ### A Pluto.jl notebook ###
-# v0.19.46
+# v0.20.3
 
 using Markdown
 using InteractiveUtils
 
 # This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
 macro bind(def, element)
+    #! format: off
     quote
         local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
         local el = $(esc(element))
         global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
         el
     end
+    #! format: on
 end
 
 # ╔═╡ 0247a51e-c89b-11ec-071f-bb82fe257adc
@@ -136,7 +138,7 @@ PlutoUI = "7f904dfe-b85e-4ff6-b463-dae2292396a8"
 PLUTO_MANIFEST_TOML_CONTENTS = """
 # This file is machine-generated - editing it directly is not advised
 
-julia_version = "1.10.4"
+julia_version = "1.11.1"
 manifest_format = "2.0"
 project_hash = "3d176982a7e409a871197b287fe1b56c0e1130ee"
 
@@ -164,18 +166,18 @@ version = "0.4.5"
 
 [[deps.Adapt]]
 deps = ["LinearAlgebra", "Requires"]
-git-tree-sha1 = "6a55b747d1812e699320963ffde36f1ebdda4099"
+git-tree-sha1 = "50c3c56a52972d78e8be9fd135bfb91c9574c140"
 uuid = "79e6a3ab-5dfb-504d-930d-738a2a938a0e"
-version = "4.0.4"
+version = "4.1.1"
 weakdeps = ["StaticArrays"]
 
     [deps.Adapt.extensions]
     AdaptStaticArraysExt = "StaticArrays"
 
 [[deps.AdaptivePredicates]]
[…]

### 2024-11-24 dev/search_index.js

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"contributing/#Contributors-Guide","page":"Contribute","title":"Contributors Guide","text":"","category":"section"},{"location":"contributing/","page":"Contribute","title":"Contribute","text":"Thank you for considering contributing to OceanRobots.jl! If you're interested in contributing we want your help no matter how big or small a contribution you make! ","category":"page"},{"location":"contributing/#Table-of-Contents","page":"Contribute","title":"Table of Contents","text":"","category":"section"},{"location":"contributing/","page":"Contribute","title":"Contribute","text":"How to Contribute\nReporting Bugs\nSuggesting Enhancements\nCode Contribution\nPull Request Process\nLicense","category":"page"},{"location":"contributing/#How-to-Contribute","page":"Contribute","title":"How to Contribute","text":"","category":"section"},{"location":"contributing/#Reporting-Bugs","page":"Contribute","title":"Reporting Bugs","text":"","category":"section"},{"location":"contributing/","page":"Contribute","title":"Contribute","text":"If you encounter a bug, please help us fix it by following these steps:","category":"page"},{"location":"contributing/","page":"Contribute","title":"Contribute","text":"Ensure the bug is not already reported by checking the issue tracker.\nIf the bug isn't reported, open a new issue. Clearly describe the issue, including steps to reproduce it.","category":"page"},{"location":"contributing/#Suggesting-Enhancements","page":"Contribute","title":"Suggesting Enhancements","text":"","category":"section"},{"location":"contributing/","page":"Contribute","title":"Contribute","text":"If you have ideas for enhancements, new features, or improvements, we'd love to hear them! Follow these steps:","category":"page"},{"location":"contributing/","page":"Contribute","title":"Contribute","text":"Check the issue tracker to see if your suggestion has been discussed.\nIf not, open a new issue, providing a detailed description of your suggestion and the use case it addresses.","category":"page"},{"location":"contributing/#Code-Contribution","page":"Contribute","title":"Code Contribution","text":"","category":"section"},{"location":"contributing/","page":"Contribute","title":"Contribute","text":"If you'd l
[…]

### 2024-11-24 dev/search_index.js
build based on 88c04d3

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"contributing/#User-Directions","page":"User Directions","title":"User Directions","text":"","category":"section"},{"location":"contributing/#Table-of-Contents","page":"User Directions","title":"Table of Contents","text":"","category":"section"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"How to Install and Use\nHow to Seek Support\nHow to Contribute\nReporting Bugs\nSuggesting Enhancements\nCode Contribution\nPull Request Process\nLicense","category":"page"},{"location":"contributing/#how-to-install-use","page":"User Directions","title":"How to Install and Use","text":"","category":"section"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"To install OceanRobots.jl in julia proceed as usual via the package manager (using Pkg; Pkg.add(\"OceanRobots\")).","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"To run a notebook interactively (.jl files) you want to use Pluto.jl. For example, copy and paste one of the above code links in the Pluto.jl interface. This will let you spin up the notebook in a web browser from the copied URL.","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"All you need to do beforehand is to install julia and Pluto.jl. The installation of OceanRobots.jl and other Julia packages will then happen automatically when you run the notebook. ","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"You can also download the notebooks folder and run them as normal Julia programs. We recommend runing each notebook in its own environment as shown below. ","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"note: Note\nTo download OceanRobots.jl folder, which includes the notebooks folder, you can use Git.jl.","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"using Pkg; Pkg.add(\"Git\"); using Git\nurl=\"https://github.com/JuliaOcean/OceanRobots.jl\"\nrun(`$(git()) clone $(url)`)","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"using Pkg; Pkg.add(\"Pluto\"); using Pluto\n\n
[…]

### 2024-11-24 v0.2.8/examples/OceanOPS.jl
build based on 88c04d3

@@ -1,0 +1,2213 @@
+### A Pluto.jl notebook ###
+# v0.20.3
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    #! format: off
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+    #! format: on
+end
+
+# ╔═╡ ccf98691-9386-41b9-a957-3cdeba51312b
+using OceanRobots, CairoMakie, PlutoUI, MeshArrays
+
+# ╔═╡ 30277358-0a8d-437e-9d2e-ebc7c307db31
+using Shapefile, GeoJSON, DataDeps, PrettyTables, Proj
+
+# ╔═╡ 5fa93c17-0a01-44c6-8679-d712c786907a
+md"""# OceanOPS : Global Ocean Metadata
+
+Source : <https://www.ocean-ops.org/board>, <https://www.ocean-ops.org/share/>
+
+## Visualize Data Cover
+"""
+
+# ╔═╡ 31fe91d7-dea2-49e3-902b-31aa62075986
+TableOfContents()
+
+# ╔═╡ 1042f70c-4337-4bf2-b533-edf27a422365
+md"""## Select a Platform Type
+
+Each color represents one type of observing platform.
+"""
+
+# ╔═╡ 596bce95-e13f-4439-858f-e944834c0924
+begin
+	bind_nam = @bind nam Select([:Argo,:Drifter])
+	md"""## Explore Platform Metadata
+
+	Here you can select a data set and then a platform. Meta-data from that platform is displayed as a result.
[…]

### 2024-11-24 v0.2.8/search_index.js

@@ -1,0 +1,3 @@
+var documenterSearchIndex = {"docs":
+[{"location":"contributing/#User-Directions","page":"User Directions","title":"User Directions","text":"","category":"section"},{"location":"contributing/#Table-of-Contents","page":"User Directions","title":"Table of Contents","text":"","category":"section"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"How to Install and Use\nHow to Seek Support\nHow to Contribute\nReporting Bugs\nSuggesting Enhancements\nCode Contribution\nPull Request Process\nLicense","category":"page"},{"location":"contributing/#how-to-install-use","page":"User Directions","title":"How to Install and Use","text":"","category":"section"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"To install OceanRobots.jl in julia proceed as usual via the package manager (using Pkg; Pkg.add(\"OceanRobots\")).","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"To run a notebook interactively (.jl files) you want to use Pluto.jl. For example, copy and paste one of the above code links in the Pluto.jl interface. This will let you spin up the notebook in a web browser from the copied URL.","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"All you need to do beforehand is to install julia and Pluto.jl. The installation of OceanRobots.jl and other Julia packages will then happen automatically when you run the notebook. ","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"You can also download the notebooks folder and run them as normal Julia programs. We recommend runing each notebook in its own environment as shown below. ","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"note: Note\nTo download OceanRobots.jl folder, which includes the notebooks folder, you can use Git.jl.","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"using Pkg; Pkg.add(\"Git\"); using Git\nurl=\"https://github.com/JuliaOcean/OceanRobots.jl\"\nrun(`$(git()) clone $(url)`)","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"using Pkg; Pkg.add(\"Pluto\"); using Pluto\n\n
[…]

### 2024-11-27 src/files.jl
fixes / updates

@@ -642,8 +642,13 @@ function to_DataFrame(ds)
 	in("drogue_status",names(df)) ? df.drogue_status=ds[:drogue_status][:] : nothing
 	df.sst1=ds[:sst1][:]
 	df.sst2=ds[:sst2][:]
-	df.longitude=ds[:longitude][:]
-	df.latitude=ds[:latitude][:]
+    if haskey(ds,"longitude")
+        df.longitude=ds[:longitude][:]
+        df.latitude=ds[:latitude][:]
+    else
+        df.longitude=ds[:lon][:]
+        df.latitude=ds[:lat][:]
+    end    
 	df.time=ds[:time][:]
 	df
 end
@@ -669,10 +674,9 @@ end
 function add_ID!(df,ds)
 	tmp=ds[:ID][:]
 	rowsize=ds[:rowsize][:]
-	ID=fill(0,0)
-	[push!(ID,fill(tmp[i],rowsize[i])...) for i in 1:length(rowsize)]
-
-	df.ID=ID
+    nn=[0 ; cumsum(ds["rowsize"])]
+	df.ID=fill(0,nn[end])
+	[df.ID[nn[i]+1:nn[i+1]].=tmp[i] for i in 1:length(nn)-1];
 end
 
 """
@@ -680,6 +684,7 @@ end
 """
 function to_Grid(gdf,grid)
 	df2=combine(gdf) do df
+#		(ve=median(df.ve) , vn=median(df.vn) )
 		(ve=mean(df.ve) , vn=mean(df.vn) )
 	end
 		

### 2024-11-27 examples/Drifters_Gulf_of_Mexico.jl
code that prepares Drifters_example.jld2 for JCON paper

@@ -1,0 +1,67 @@
+module Drifters_Gulf_of_Mexico
+
+using OceanRobots
+import MeshArrays, Shapefile, DataDeps, CairoMakie, JLD2
+
+function read_polygons()
+    fil=MeshArrays.demo.download_polygons("ne_110m_admin_0_countries.shp")
+    MeshArrays.read_polygons(fil)
+end
+
+function read_GDP_subset(file::String)
+    GDP_CD=read(CloudDrift(),file)
+
+    ii_box=findall( (GDP_CD.data.grid.lon.>=-100).&&(GDP_CD.data.grid.lon.<=-75) )
+    jj_box=findall( (GDP_CD.data.grid.lat.>=17).&&(GDP_CD.data.grid.lat.<=33) )
+    (ii_box,jj_box)
+
+    x=GDP_CD.data.grid.lon[ii_box]
+    y=GDP_CD.data.grid.lat[jj_box]
+    u=GDP_CD.data.ve[ii_box,jj_box]
+    v=GDP_CD.data.vn[ii_box,jj_box]
+
+    GM=Dict("x"=>x,"y"=>y,"u"=>u,"v"=>v)
+    
+    GDP_CD,GM
+end
+
+"""
+    Drifters_example_prep(file::String)
+
+```
+file=GDP_CloudDrift.CloudDrift_subset_download()
+#file="gdp-v2.01.nc"
+Main.Drifters_Gulf_of_Mexico.Drifters_example_prep()
+```
+"""
+function Drifters_example_prep(file::String)
+    pol=read_polygons()
+    GDP_CD,GM=read_GDP_subset(file)
+
+    res=1/2
+    dx=res*100000.0
+    dT=1/4*86400
+    nt=120*86400/dT
+
+    uC=GM["u"]/dx; uC[isnan.(uC)].=0
+    vC=GM["v"]/dx; vC[isnan.(vC)].=0
+    "done with defining flow field at grid cell centers"
+
+    u=0.5*(circshift(uC, (1,0))+uC) #staggered u converted to grid point units (m/s -> 1/s)
+    v=0.5*(circshift(vC, (0,1))+vC) #staggered v converted to grid point units (m/s -> 1/s)
+    T=(0.,dT)
+
+    np,nq=size(u)
+    x0=np*(0.5 .+ 0.3*rand(1000))
+    y0=nq*(0.0 .+ 0.3*rand(1000))
+
[…]

### 2024-11-27 paper/paper.tex
update table
update code snippets

@@
 \setcounter{page}{1}
+\usepackage[utf8]{inputenc}
 
@@
 \hline
-research vessel data & CCHDO \\
+research vessel data & \struct{CCHDO} \\
 ships of opportunity data & \tbd \\
@@
     language = Julia,
-    numbers=left,
+%    numbers=left,
     label={lst:ArgoCode},
@@
 ]
-using OceanRobots, ArgoData, CairoMakie
-argo=read(ArgoFloat(),wmo=6900900)
+using OceanRobots, ArgoData, CairoMakie;
+argo=read(ArgoFloat(),wmo=6900900);
 fig=plot(argo,option=:standard)
@@
     language = Julia,
-    numbers=left,
     label={lst:IndDispCode},
-    caption={Simulate surface drifter pathways in the Gulf of Mexico (Fig.~\ref{fig:drifters_speed}) from flow fields $u,v$ and initial positions $x,y$.}
+    caption={Simulate surface drifter pathways in the Gulf of Mexico (Fig.~\ref{fig:drifters_speed}) from flow fields $u,v$ and initial positions $x,y$. 
+    Visualization code is provided in the \pkg{Drifters.jl} documentation.}
 ]
-using Drifters, DataFrames
 
-dT=6*3600 #6 hours
-nt=120*86400/dT #120 days
-
-T=(0.,dT)
-F=FlowFields(u=u,v=v,period=T)
-I=Individuals(F,x,y)
-
-[solve!(I,T.+dT*(n-1)) for n in 1:nt]
-trajectories=groupby(I,:ID)
+using JLD2, CairoMakie, Drifters, OceanRobots;
+P=Drifters.Gulf_of_Mexico_setup();
+F=FlowFields(u=P.u,v=P.v,period=P.T);
+I=Individuals(F,P.x0,P.y0);
+[solve!(I,P.T .+P.dT*(n-1)) for n in 1:P.nt]
 \end{lstlisting}

### 2024-11-28 dev/search_index.js
build based on 0ac37fc

@@ -1,3 +1,3 @@
 var documenterSearchIndex = {"docs":
-[{"location":"contributing/#User-Directions","page":"User Directions","title":"User Directions","text":"","category":"section"},{"location":"contributing/#Table-of-Contents","page":"User Directions","title":"Table of Contents","text":"","category":"section"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"How to Install and Use\nHow to Seek Support\nHow to Contribute\nReporting Bugs\nSuggesting Enhancements\nCode Contribution\nPull Request Process\nLicense","category":"page"},{"location":"contributing/#how-to-install-use","page":"User Directions","title":"How to Install and Use","text":"","category":"section"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"To install OceanRobots.jl in julia proceed as usual via the package manager (using Pkg; Pkg.add(\"OceanRobots\")).","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"To run a notebook interactively (.jl files) you want to use Pluto.jl. For example, copy and paste one of the above code links in the Pluto.jl interface. This will let you spin up the notebook in a web browser from the copied URL.","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"All you need to do beforehand is to install julia and Pluto.jl. The installation of OceanRobots.jl and other Julia packages will then happen automatically when you run the notebook. ","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"You can also download the notebooks folder and run them as normal Julia programs. We recommend runing each notebook in its own environment as shown below. ","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"note: Note\nTo download OceanRobots.jl folder, which includes the notebooks folder, you can use Git.jl.","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"using Pkg; Pkg.add(\"Git\"); using Git\nurl=\"https://github.com/JuliaOcean/OceanRobots.jl\"\nrun(`$(git()) clone $(url)`)","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"using Pkg; Pkg.add(\"Pluto\"); using Pluto\n\n
[…]

### 2024-11-29 src/files.jl
fix case when WHP netCDF is not included

@@ -33,9 +33,11 @@ function download(cruise::Union{Symbol,String,Vector},path=tempdir())
             Dataverse.unzip(fil2)
             #unzip ctd files
             tmp1=readdir(path1)
-            tmp2=findall(occursin.(Ref("_nc_ctd.zip"),tmp1))[1]
-            fil3=joinpath(path1,tmp1[tmp2])
-            Dataverse.unzip(fil3)
+            tmp2=findall(occursin.(Ref("_nc_ctd.zip"),tmp1))
+            if length(tmp2)>1
+                fil3=joinpath(path1,tmp1[tmp2[1]])
+                Dataverse.unzip(fil3)
+            end
             #download ancillary files
             for i in list
                 isempty(i) ? nothing : Downloads.download(i,joinpath(path1,basename(i)))

### 2024-11-29 v0.2.9/examples/Float_Argo.jl
build based on 0ac37fc

@@ -1,0 +1,2191 @@
+### A Pluto.jl notebook ###
+# v0.20.3
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    #! format: off
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+    #! format: on
+end
+
+# ╔═╡ 8539e67f-6361-409a-9dbe-e8dcb2c7e10d
+begin
+	using OceanRobots, ArgoData, CairoMakie, PlutoUI, PrettyTables, MeshArrays
+	"Done with packages"
+end
+
+# ╔═╡ dc017980-cde3-49bc-a5e0-44be9bb08cec
+begin
+	using Shapefile, DataDeps
+	pol_file=demo.download_polygons("ne_110m_admin_0_countries.shp")
+	pol=MeshArrays.read_polygons(pol_file)
+	"Done with country boundaries"
+end
+
+# ╔═╡ 89647c4e-e568-4d3a-af57-bcc541744e38
+md"""# Argo Floats
+
+The standard Argo platform is a profiling float that drifts at 1000m depth. They come back to the surface every ten days, just after collecting vertocal profiles of temperature and salinity, and transmit their data via satellite. 
+
+!!! tip
+    For more information about the international Argo program please refer to, for example, <https://argo.ucsd.edu> or <https://biogeochemical-argo.org>.
+"""
+
+# ╔═╡ 09a2aa6e-16bc-4582-9d5f-c50432e3f0ca
+begin
[…]

### 2024-11-29 v0.2.9/examples/Mooring_WHOTS.jl

@@ -1,0 +1,2078 @@
+### A Pluto.jl notebook ###
+# v0.20.3
+
+using Markdown
+using InteractiveUtils
+
+# This Pluto notebook uses @bind for interactivity. When running this notebook outside of Pluto, the following 'mock version' of @bind gives bound variables a default value (instead of an error).
+macro bind(def, element)
+    #! format: off
+    quote
+        local iv = try Base.loaded_modules[Base.PkgId(Base.UUID("6e696c72-6542-2067-7265-42206c756150"), "AbstractPlutoDingetjes")].Bonds.initial_value catch; b -> missing; end
+        local el = $(esc(element))
+        global $(esc(def)) = Core.applicable(Base.get, el) ? Base.get(el) : iv(el)
+        el
+    end
+    #! format: on
+end
+
+# ╔═╡ 5fc8cc85-7bd4-4fea-8c6f-01dabee6eb5f
+begin
+	using OceanRobots, CairoMakie, PlutoUI
+	"Done with packages"
+end
+
+# ╔═╡ 538ddc08-85bd-426b-92bc-f5dd78d38d5d
+TableOfContents()
+
+# ╔═╡ 720e1461-81b9-42b6-88be-0115a17268c0
+md"""# WHOTS mooring
+
+Here we plot time series from the [WHOTS mooring](http://www.soest.hawaii.edu/whots/wh_data.html) which measures both Ocean and Atmosphere variables. This is one of the long time series available to study Climate. See <http://www.oceansites.org/> for more data like this.
+"""
+
+# ╔═╡ e7dc453e-3bf2-4289-b55d-66eab3636d7b
+begin
+	url0="https://insideclimatenews.org/wp-content/uploads/2020/07/ohcean-mooring_noaa.jpg"
+	url1="https://aco-ssds.soest.hawaii.edu/ALOHA/img/slideshow3.jpg"
[…]

### 2024-11-29 v0.2.9/search_index.js

@@ -1,0 +1,3 @@
+var documenterSearchIndex = {"docs":
+[{"location":"contributing/#User-Directions","page":"User Directions","title":"User Directions","text":"","category":"section"},{"location":"contributing/#Table-of-Contents","page":"User Directions","title":"Table of Contents","text":"","category":"section"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"How to Install and Use\nHow to Seek Support\nHow to Contribute\nReporting Bugs\nSuggesting Enhancements\nCode Contribution\nPull Request Process\nLicense","category":"page"},{"location":"contributing/#how-to-install-use","page":"User Directions","title":"How to Install and Use","text":"","category":"section"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"To install OceanRobots.jl in julia proceed as usual via the package manager (using Pkg; Pkg.add(\"OceanRobots\")).","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"To run a notebook interactively (.jl files) you want to use Pluto.jl. For example, copy and paste one of the above code links in the Pluto.jl interface. This will let you spin up the notebook in a web browser from the copied URL.","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"All you need to do beforehand is to install julia and Pluto.jl. The installation of OceanRobots.jl and other Julia packages will then happen automatically when you run the notebook. ","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"You can also download the notebooks folder and run them as normal Julia programs. We recommend runing each notebook in its own environment as shown below. ","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"note: Note\nTo download OceanRobots.jl folder, which includes the notebooks folder, you can use Git.jl.","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"using Pkg; Pkg.add(\"Git\"); using Git\nurl=\"https://github.com/JuliaOcean/OceanRobots.jl\"\nrun(`$(git()) clone $(url)`)","category":"page"},{"location":"contributing/","page":"User Directions","title":"User Directions","text":"using Pkg; Pkg.add(\"Pluto\"); using Pluto\n\nnotebook=\"MITgcm.jl/examples/Float_Argo.jl\"\nimport OceanRobots; 
[…]

### 2024-11-29 paper/paper.tex
final proofreading and edits (part 1)

@@
 
-\keywords{Julia, Ocean, Climate, Robot, Observation, Platform, Sensor, Drifter, Buoy, Profiler, Satellite, Modeling, Artificial Intelligence, Data Assimilation, Parameter Inference, Climatology, Geospatial, Statistics}
+\keywords{Julia, Ocean, Climate, Robot, Observation, Observing, Platform, Sensor, Drifter, Buoy, Profiler, Model, Modeling, Machine Learning, Artificial Intelligence, Data Assimilation, Parameter Inference, Climatology, Geospatial, Statistics}
 
@@
 
-DTOR is a framework to access and simulate the global fleet of ocean observing devices (or {\it ocean robots}) that monitor climate change.
+DTOR is a framework to access, analyze, and simulate the global fleet of ocean observing devices (or {\it ocean robots}) that monitor climate change.
 It brings these observations to Julia and lets us pair ocean robots with virtual counterparts (or {\it twins}).
-Digital twins provide a bridge to predictive models that enables machine learning.
-In turn, simulating observations in a digital environment can help evaluate observational strategies a priori, during deployment, or afterwards.
-In this paper we present the framework, review simulated ocean robots, and discuss envisioned applications.
+Digital twins provide a bridge from the data to predictive models and enable machine learning.
+In turn, observing system simulations in a digital environment can help evaluate observational strategies a priori, during deployment, or afterwards.
+In this paper we present the DTOR framework, its supported observing systems, capabilities to simulate ocean robots, and envisioned applications.
 
@@
 
-The DTOR framework was introduced at the Symposium on Advances in Ocean Observation in 2022, and later presented to US-CLIVAR and JuliaCon in 2023.
+The DTOR framework was introduced at the Symposium on Advances in Ocean Observation in 2022, and later presented to US-CLIVAR and JuliaCon in 2023, and the OceanPredict Symposium in 2024.
 The primary goal of DTOR is to associate ocean observing systems (or {\it ocean robots}) with virtual counterparts (or {\it twins}), and do it for the whole fleet of ocean robots that are currently at sea or have observed the Ocean in the past (Fig.~\ref{fig:ocean-ops}).
@@
 The framework leverages and links to a variety of highly capable Julia packages from the community.
-It notably provides extension for visualization with \pkg{Makie.jl}, and tutorial examples in the form of \pkg{Pluto.jl} notebooks.
+It notably provides user-friendly plotting recipes via its \pkg{Makie.jl} extension, and tutorial examples in the form of \pkg{Pluto.jl} notebooks.
 
@@
 
-Part of the fleet of ocean robots currently at sea is depicted in Fig.~\ref{fig:ocean-ops}, focusing on some of the most common observing platforms.
-To create this map, \pkg{OceanRobots.jl} queries the meta-data-base from Ocean-OPS.org, which keeps track of the whole ocean fleet of scientific observation platforms in real time, and provides a RESTful API.
-The \pkg{OceanRobots.jl} package provides a simple interface to this API via the `OceanOPS` module.
-\pkg{OceanRobots.jl} defines data structures to access and utilize data from common ocean robot types such as  `SurfaceDrifter` and `ArgoFloat` (shown in Fig.~\ref{fig:ocean-ops}).
-A non-exhaustive list of ocean observing platform categories within the scope of \pkg{OceanRobots.jl} is provided in Tab.~\ref{tab:robots}.
+Part of the fleet of ocean robots currently at sea is depicted in Fig.~\ref{fig:ocean-ops}, focusing on a few widely used observing platforms.
+To create this map, \pkg{OceanRobots.jl} queries the meta-data-base from Ocean-OPS.org, which keeps track of the whole ocean fleet of scientific observing platforms in real time, and provides a RESTful API.
+The \pkg{OceanRobots.jl} package provides an interface to this API via the `OceanOPS` module.
+It then defines data structures such as  `SurfaceDrifter` and `ArgoFloat` to access and utilize data from widely used ocean observing platforms.
+The list of ocean observing platforms currently supported by \pkg{OceanRobots.jl} is in Tab.~\ref{tab:robots}.
 
@@
 
-A small fraction of the geospatial data obtained in the past using surface ocean drifters (green dots in Fig.~\ref{fig:ocean-ops}) is depicted in Fig.~\ref{fig:drifters} (using \pkg{OceanRobots.jl} and \pkg{Makie.jl}).
-These drifting buoys tend to follow near-surface ocean currents (at approximately 15 depth).
+A fraction of the geospatial data obtained by surface ocean drifters in the past (green dots in Fig.~\ref{fig:ocean-ops}) is depicted in Fig.~\ref{fig:drifters} using \pkg{OceanRobots.jl} and \pkg{Makie.jl}.
+These drifting buoys tend to follow ocean currents at approximately 15 depth.
 They can measure sea surface temperature and sea level pressure along their trajectory.
@@
 However, Argo floats have a crucial diving capability that surface drifters don't have -- they go up and down the water column to measure temperature and salinity (T,S; bottom panels of Fig.~\ref{fig:Argo_Float}).
-As a result, the advent of the Argo array in the early 2000s \cite{Roemmich2019} opened up a whole new era of geospatial analysis, state estimation, and parameter inference over the global Ocean  \cite{Forget2007,Forget2010,MFF14,Forget2015a,FFL15,FP15,Forget2024a}.
-There were 3837 Argo floats at sea on `2024/05/27`, and a total of 18730 in the Argo data base.
+The advent of the Argo array in the early 2000s \cite{Roemmich2019} thus opened up a whole new era of geospatial analysis, state estimation, and parameter inference over the global Ocean  \cite{Forget2007,Forget2010,MFF14,Forget2015a,FFL15,FP15,Forget2024a}.
+On `2024/05/27` for example there were 3837 Argo floats at sea, and a total of 18730 in the Argo data base.
 Since the Argo array is such an important observing system, a dedicated package called \pkg{ArgoData.jl} was created that \pkg{OceanRobots.jl} uses under the hood.
@@
 ]
-using OceanRobots, ArgoData, CairoMakie;
+using OceanRobots, CairoMakie;
 argo=read(ArgoFloat(),wmo=6900900);
@@
 Numerical modeling is thus often motivated and driven by observations.
-Many research activities involve combining ocean models and observations, with the typical goal of learning model parameters and dynamics from data \cite{Forget2010,Forget2015a,FFL15,FP15,Forget2024a}.
+Many research activities involve combining ocean models and observations, with the typical goal of learning model parameters, statistics, and dynamics from data \cite{Forget2010,Forget2015a,FFL15,FP15,Forget2024a}.
 Observing system simulations in a digital environment (using models) enable a wide range of applications -- to test out innovative platform or sensor designs ahead of deployment, to optimize global monitoring strategies, or to guide deployed assets in real time for example.
@@
 First, in Fig.~\ref{fig:Argo_Float_simu} we simulate an Argo data collection for temperature (T) and salinity (S) by sampling an ocean climatology along the track of the Argo float (the one from Fig.~\ref{fig:Argo_Float}).
-This calculation requires (1) a model prediction of $T,S(x,y,z,t)$, which can be based on statistical or mechanistic models on a grid, and (2) tools that deal with the Earth geography, and can localize observations on a grid, and perform interpolation tasks.
+This calculation requires (1) a model prediction of $T(x,y,z,t)$ and $S(x,y,z,t)$, which can be based on statistical or mechanistic models on a grid, and (2) tools that deal with the Earth geography, and can localize observations on a grid, and perform interpolation tasks.
 
-To create Fig.~\ref{fig:Argo_Float_simu}, we use \pkg{Climatology.jl} to access the OCCA climatology \cite{Forget2010}, and then interpolate $T,S(x,y,z,t)$ via the geospatial tools in \pkg{MeshArrays.jl} providing.
-OCCA is essentially a previously trained model that consists of 12 monthly three-dimensional fields of $T,S$ (one per calendar month).
-Let's note that Figs.~\ref{fig:Argo_Float} and~\ref{fig:Argo_Float_simu} show broadly similar patterns -- this reflects that the predictive model for $T,S$ is skillful and that $T,S$ contrasts see in Fig.~\ref{fig:Argo_Float} largely reflect the $T,S$ sensor moving with the Argo float across the Ocean's geography.
+To create Fig.~\ref{fig:Argo_Float_simu}, we use \pkg{Climatology.jl} to access the OCCA climatology \cite{Forget2010}, and then interpolate $T(x,y,z,t)$, $S(x,y,z,t)$ via geospatial tools from \pkg{MeshArrays.jl}.
+The OCCA climatology is a previously trained model that consists of 12 monthly three-dimensional fields of $T,S$ (one per calendar month).
+The fact that Figs.~\ref{fig:Argo_Float} and~\ref{fig:Argo_Float_simu} show broadly similar patterns reflects that the predictive model is skillful, and that $T,S$ contrasts seen in Fig.~\ref{fig:Argo_Float} largely result from the sensor moving with the Argo float across the Ocean's $T,S$ geography.
 Differences between Figs.~\ref{fig:Argo_Float} and~\ref{fig:Argo_Float_simu} can in turn provide a basis for improving the predictive model, for example by including time variability beyond the seasonal cycle, or through various methods for data assimilation, artificial intelligence, or parameter inference \cite{Forget2010,Forget2015a,FFL15,FP15,Forget2024b}.
@@
 Our second example focuses on the simulation of observing platforms moving with ocean currents.
-This basic simulation of surface drifter pathways uses the geostatistical average of velocities calculated in Fig.~\ref{fig:drifters_ve} as a predictive model for the $U,V(x,y,t)$ velocity fields.
-This gridded data set is simply provided as input to \pkg{Drifters.jl}, which then releases virtual drifters and calculates their trajectories following the flow field (code~\ref{lst:IndDispCode}).
-The combination of these two model elements represents a previously trained model to predict surface drifter trajectories.
-While this simple calculation neglects time variability and small scales in ocean currents altogether, the model is sufficient to capture the mean pathway of sea water through this region -- the well-known loop current feeding the Gulf Stream via Florida Strait (Fig.~\ref{fig:drifters_speed_simu}).
+This basic simulation of surface drifter pathways uses the geostatistical average of velocities calculated in Fig.~\ref{fig:drifters_ve} as a predictive model for the $U(x,y,t)$, $V(x,y,t)$ velocity fields.
+In Code~\ref{lst:IndDispCode}, this gridded data set is provided as input to \pkg{Drifters.jl}, which then releases virtual drifters and calculates their trajectories following the flow field (Fig.~\ref{fig:drifters_speed_simu}).
+While this simple drifter trajectory prediction model neglects stochastic variability and small scales in ocean currents altogether (Fig.~\ref{fig:km_scale}), it is sufficient to capture the main mean pathway of sea water through the Gulf of Mexico region -- the well-known loop current feeding the Gulf Stream via Florida Strait (Fig.~\ref{fig:drifters_speed_simu}).
 
@@
 
-using JLD2, CairoMakie, Drifters, OceanRobots;
+using OceanRobots, Drifters, CairoMakie ;
 P=Drifters.Gulf_of_Mexico_setup();
@@
 I=Individuals(F,P.x0,P.y0);
-[solve!(I,P.T .+P.dT*(n-1)) for n in 1:P.nt]
+[solve!(I,P.T .+P.dT*(n-1)) for n in 1:P.nt];
 \end{lstlisting}

### 2024-11-29 paper/paper.tex
final proofreading and edits (part 2)

@@
 The \pkg{ClimateModels.jl} interface streamlines the use of models implemented in various languages.
-The model hierarchy already includes the models used in this paper, and is easy to extend via pkg{ClimateModels.jl}.
-DTOR can notably simulate observations in the future based on climate model predictions, and \pkg{ClimateModels.jl} provides two options for this kind of applications -- either querying the CMIP6 archive of model output \cite{CMIP6} or using a fast emulator such as Hector \cite{Hector2015} (Fig.~\ref{fig:globalwarming}).
+The model hierarchy already includes models listed in this paper, and is easy to extend via the \pkg{ClimateModels.jl} interface.
+DTOR can also simulate observations in the future based on climate model predictions (Fig.~\ref{fig:globalwarming}), and \pkg{ClimateModels.jl} provides two options for this kind of applications -- either querying the CMIP6 archive of model output \cite{CMIP6} or using a fast emulator such as Hector \cite{Hector2015}.
 
@@
 DTOR can also take advantage of gridded satellite data, incl.
-sea surface temperature and sea level anomalies via \pkg{Climatology.jl}, and it is sometimes possible to use these instead of ocean reanalyses.
+sea surface temperature and sea level anomalies via \pkg{Climatology.jl}, which can sometimes be used instead of ocean reanalyses.
 
@@
 First, we'd like to integrate additional types of ocean observing platforms, starting with those that do not have a data structure listed yet in Tab.~\ref{tab:robots}.
-Observational networks that focus on either the coastal ocean, a specific region, or local field experiments could be supported in the future.
-A top level API to interact with DTOR as a whole through cloud services is also envisioned.
+Observational networks that focus on either the coastal ocean, a specific region, or local field experiments could also be supported in the future.
+In addition, a top level API to interact with DTOR as a whole through cloud services is envisioned and being developed.
 

### 2024-11-29 paper/paper.tex
final proofreading and edits (part 3)

@@
 \centerline{\includegraphics[width=\columnwidth]{figs/20240528_OceanOPS.png}}
-\caption{Locations of ocean robots collecting data on {\it 2024/05/27}. Data source : https://www.ocean-ops.org}
+\caption{Locations of ocean robots collecting data and planned deployments, on {\it 2024/05/27}. Data source : https://www.ocean-ops.org}
 \label{fig:ocean-ops}
@@
 \centerline{\includegraphics[width=\columnwidth]{figs/20240528_drifters_5percent.png}}
-\caption{A few of the ocean drifters (5\% of 19396) that have been deployed to follow near surface ocean currents.}
+\caption{A few of the ocean drifters (5\% of 19396) that have been deployed to follow near surface ocean currents in the past.}
 \label{fig:drifters}
@@
 \begin{table}
-\tbl{Ocean observing platforms targeted by \pkg{OceanRobots.jl}, and associated data structures (or blank if not yet implemented).}{
+\tbl{Ocean observing systems targeted by \pkg{OceanRobots.jl}, and associated data structures (or blank if not yet implemented).}{
 \begin{tabular}{|l||r|}\hline
@@
 ships of opportunity data & \tbd \\
-marine mammals & \tbd \\\hline
+marine mammals data & \tbd \\\hline
 \end{tabular}}
@@
 \centerline{\includegraphics[width=\columnwidth]{figs/20240529_speed_subset_IndDisp.png}}
-\caption{Virtual drifter trajectories predicted using (1) just the climatological mean flow field estimated from drifters (Fig.~\ref{fig:drifters_ve}, and the northward component) and (2) \pkg{Drifters.jl} to calculate trajectories.}
+\caption{Virtual drifter trajectories predicted using (1) just the climatological mean flow field estimated from drifters (Fig.~\ref{fig:drifters_ve}, plus the corresponding northward component) and (2) \pkg{Drifters.jl} to calculate trajectories.}
 \label{fig:drifters_speed_simu}
@@
 \caption{Ensemble of model predictions (black curves) by a simple multi-layer perceptron (from Flux.jl) trained to predict Chlorophyll concentration (present in green algea and marine microbes) from environmental variables (T, S, but also oxygen, optical backscatter, and solar radiation).
-The blue line is the {\it ground truth} that we seek to estimate, and was obtained through proper spatial averaging of the gridded data set from which the training data itself was generated.}
+The blue line is the model {\it ground truth} that we seek to estimate, and was obtained through proper spatial averaging of the gridded data set from which the training data itself was generated.}
 \label{fig:MLP}

### 2024-11-29 paper/paper.tex
final proofreading and edits (part 4/4)

@@
 Through a streamlined workflow, \pkg{ClimateModels.jl} (JuliaCon 2021, 2023) makes it easy to operate these models that can provide a digital environment for the virtual ocean robot fleet to observe and navigate.
-\pkg{Drifters.jl} \cite{Forget2021} can be use to predict pathways of ocean robots that tend to follow ocean currents.
+\pkg{Drifters.jl} \cite{Forget2021} can be used to predict pathways of ocean robots that tend to follow ocean currents.
 \pkg{MeshArrays.jl} adds basic geospatial support for global climate model grids, providing capabilities such as interpolation and geolocation on a grid.
@@
 A fraction of the geospatial data obtained by surface ocean drifters in the past (green dots in Fig.~\ref{fig:ocean-ops}) is depicted in Fig.~\ref{fig:drifters} using \pkg{OceanRobots.jl} and \pkg{Makie.jl}.
-These drifting buoys tend to follow ocean currents at approximately 15 depth.
+These drifting buoys tend to follow ocean currents at approximately 15 meters depth.
 They can measure sea surface temperature and sea level pressure along their trajectory.
@@
 The advent of the Argo array in the early 2000s \cite{Roemmich2019} thus opened up a whole new era of geospatial analysis, state estimation, and parameter inference over the global Ocean  \cite{Forget2007,Forget2010,MFF14,Forget2015a,FFL15,FP15,Forget2024a}.
-On `2024/05/27` for example there were 3837 Argo floats at sea, and a total of 18730 in the Argo data base.
+On {\it 2024/05/27} for example there were 3837 Argo floats at sea, and a total of 18730 in the Argo data base.
 Since the Argo array is such an important observing system, a dedicated package called \pkg{ArgoData.jl} was created that \pkg{OceanRobots.jl} uses under the hood.
@@
 
-Let's define digital twins as agreed upon by the U.S. Committee on Foundational Research Gaps and Future Directions for Digital Twins \cite{DT2024} :
+Digital twins can be defined as per the U.S. Committee on Foundational Research Gaps and Future Directions for Digital Twins \cite{DT2024} :
 

### 2024-11-29 paper/paper.tex
cosmetic improvements (1)

@@
 \centerline{\includegraphics[width=\columnwidth]{figs/20240528_OceanOPS.png}}
-\caption{Locations of ocean robots collecting data and planned deployments, on {\it 2024/05/27}. Data source : https://www.ocean-ops.org}
+\caption{Location of ocean robots that were collecting data on {\it 2024/05/27} for three types of observations (blue, green, and red dots).
+Deployments of Argo profilers that were being planned at the time are also shown (purple dots).
+Data is from https://www.ocean-ops.org and queried via \pkg{OceanRobots.jl}.}
 \label{fig:ocean-ops}
@@
 
+\newpage
+
 \section{Simulating Ocean Robots}
@@
 
+\begin{lstlisting}[
+    language = Julia,
+    label={lst:IndDispCode},
+    caption={Simulate surface drifter pathways in the Gulf of Mexico (Fig.~\ref{fig:drifters_speed}) from flow fields $u,v$ and initial positions $x,y$. 
+    Visualization code is provided in the \pkg{Drifters.jl} documentation.}
+]
+
+using OceanRobots, Drifters, CairoMakie ;
+P=Drifters.Gulf_of_Mexico_setup();
+F=FlowFields(u=P.u,v=P.v,period=P.T);
+I=Individuals(F,P.x0,P.y0);
+[solve!(I,P.T .+P.dT*(n-1)) for n in 1:P.nt];
+\end{lstlisting}
+
 Much more could be done to improve the details and skill of the simple models used here.
@@
 \end{figure}
-
-\begin{lstlisting}[
-    language = Julia,
-    label={lst:IndDispCode},
-    caption={Simulate surface drifter pathways in the Gulf of Mexico (Fig.~\ref{fig:drifters_speed}) from flow fields $u,v$ and initial positions $x,y$. 
-    Visualization code is provided in the \pkg{Drifters.jl} documentation.}
-]
-
-using OceanRobots, Drifters, CairoMakie ;
-P=Drifters.Gulf_of_Mexico_setup();
-F=FlowFields(u=P.u,v=P.v,period=P.T);
-I=Individuals(F,P.x0,P.y0);
-[solve!(I,P.T .+P.dT*(n-1)) for n in 1:P.nt];
-\end{lstlisting}
 

### 2024-11-29 paper/paper.tex
cosmetic improvements (2/2)

--- 2024-11-29 paper/paper.tex
@@
 \begin{figure}[t]
-\centerline{\includegraphics[width=\columnwidth]{figs/20240528_OceanOPS.png}}
-\caption{Locations of ocean robots collecting data and planned deployments, on {\it 2024/05/27}. Data source : https://www.ocean-ops.org}
+\centerline{\includegraphics[width=\columnwidth]{figs/20241129_OceanOPS.png}}
+\caption{Ocean robots that were collecting data on {\it 2024/11/29} for three types of observations (blue, green, and red dots).
+Planned deployments of Argo profilers are also shown (purple dots).
+Data is from https://www.ocean-ops.org and queried via \pkg{OceanRobots.jl}.}
 \label{fig:ocean-ops}

### 2024-11-29 examples/OceanOPS.jl

@@ -130,35 +130,35 @@ begin
 end
 
 # ╔═╡ c5f24071-1c1f-4edf-b7b2-b6194c33b571
-let
+begin
 	function demofigure()
 		lon0=-160
 		proj=Proj.Transformation(MA_preset=2,lon0=lon0)
 	
 		fi0=Figure(size=(900,600),fontsize=24)
-		ax0=Axis(fi0[1,1],backgroundcolor = :gray20,
-			title="Distribution of Ocean Observing Platforms")
+		ax0=Axis(fi0[1,1],title="Distribution of Ocean Observing Platforms")
 		pr_ax=MeshArrays.ProjAxis(ax0; proj=proj,lon0=lon0)
 		lines!(pr_ax,polygons=pol;color=:white, linewidth = 0.5)
 	
 		sc1=scatter!(pr_ax,argo_operational.lon,argo_operational.lat,
-			markersize=6.0,label="Argo (operational)",color=:deepskyblue)
+			markersize=6.0,label="Argo (operational)" => (; markersize = 15),color=:deepskyblue)
 		sc2=scatter!(pr_ax,argo_planned.lon,argo_planned.lat,
-			markersize=6.0,label="Argo (planned)",color=:violet)
+			markersize=6.0,label="Argo (planned)" => (; markersize = 15),color=:violet)
 		sc3=scatter!(pr_ax,drifter_operational.lon,drifter_operational.lat,
-			markersize=8.0,label="Drifter",color=:green1)
+			markersize=8.0,label="Drifter" => (; markersize = 15),color=:green1)
 		sc4=scatter!(pr_ax,more_operational.lon,more_operational.lat,
-			markersize=12.0,label=more_platform_name,color=:red,marker=:star5)
+			markersize=12.0,label=more_platform_name => (; markersize = 15),color=:red,marker=:star5)
 		
 		MeshArrays.grid_lines!(pr_ax;color=:yellow,linewidth=0.5)
 
-		Legend(fi0[2, 1],[sc1,sc2,sc3,sc4],[sc1.label,sc2.label,sc3.label,sc4.label],
[…]

### 2024-11-29 paper/paper.tex
cosmetic improvements (3)

@@
 \tbl{Ocean observing systems targeted by \pkg{OceanRobots.jl}, and associated data structures (or blank if not yet implemented).}{
-\begin{tabular}{|l||r|}\hline
+\begin{tabular}{||l||r||}\hline
 Platform Type & Data Structure\\\hline\hline
@@
 sail drones & \tbd \\
-\hline
+\hline\hline
 research vessel data & \struct{CCHDO} \\

### 2024-11-29 paper/paper.tex
cosmetic improvements (3)

@@
 ]
-
 using OceanRobots, Drifters, CairoMakie ;
